### 2015-09-03 manuscript.tex
initial commit of paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command
\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\usepackage{ieee_packages}

\title{\LARGE \bf
Constrained Attitude Control
}

\author{Shankar Kulumani,Frederick Leve, Taeyoung Lee$^*$
 \thanks{Shankar Kulumani and Taeyoung Lee are with Department of Aerospace Engineering, George Washington University, Washington, DC. Email: {\tt\footnotesize \{skulumani, tylee\}@gwu.edu }}
 }

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

200-300 summary of the paper

general topic area

new developments/contributions of the paper

relation/benefits over previous work

summary of the results and contributions

Awesome abstract

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
introduction to attitude dynamics problem

difficulties of attitude control (topological restriction, nonlinear manifold)

difficulties with attitude representatiion.
Euler angles/MRP have singularities not suitable for large angular rotations
Quaterions have no singularities but double coverage. can exhibit unwinding

\section{PROBLEM FORMULATION}

\section{ATTITUDE STABILIZATION}

\section{EQUILIBRIUM STRUCTURE}

\section{NUMERICAL EXAMPLE}

\section{EXPERIMENT}

\section{CONCLUSIONS}
\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{APPENDIX}

Appendixes should appear before the acknowledgment.

\section*{ACKNOWLEDGMENT}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{library}
\bibliographystyle{IEEEtran}

\end{document}

### 2015-09-18 manuscript.tex
initial outline for ACC paper

@@
 
-\author{Shankar Kulumani,Frederick Leve, Taeyoung Lee$^*$
+\author{Shankar Kulumani and Taeyoung Lee$^*$
  \thanks{Shankar Kulumani and Taeyoung Lee are with Department of Aerospace Engineering, George Washington University, Washington, DC. Email: {\tt\footnotesize \{skulumani, tylee\}@gwu.edu }}
@@
 
+Attitude dynamics evolve on a nonlinear manifold, unique properties not experienced in linear systems
+
 difficulties of attitude control (topological restriction, nonlinear manifold)
 
-difficulties with attitude representatiion.
+difficulties with attitude representations.
+
+Linear vector space used to represent motion on nonlinear manifold.
+
 Euler angles/MRP have singularities not suitable for large angular rotations
-Quaterions have no singularities but double coverage. can exhibit unwinding
+
+Quaterions have no singularities but double coverage as the three sphere double covers the special orthogonal group.
+There are two equivalent quaternions that represent the same attitude.
+
+Discuss attitude control in the presence of constraints. 
+Key technology/capability to allow for autonomous operation of spacecraft and UAVs
+Sensitive optical instruments that require reorientation while avoiding exposure to the sun or bright sources
+
+Removal of constrained regions from the configuration space results in a nonconvex space/region.
+
+Benefits of this approach over previous work ( cite papers).
+Use of artifical potential functions
+Mcinnes looked at reorientation using euler angles. 
+Singularities would become evident for arbitrarily large angular slews
+
+Determine manuever a priori using geometric/kinematic relationships
+
+Computational based approaches.
+Randomized algorithms or direct optimal control
 
@@
 
+Describe attitude dynamics EOMS.
+Explain attitude representation using \SO.
+Hat and vee map properties used in developments
+
+Configuration error function with attractive and repulsive terms
+Define the various attitude error functions and where they are derived from
+summarize some of the properties of the attractive error function from previous papers
+Show the development of the configuration error terms and equilibrium structure
 \section{ATTITUDE STABILIZATION}
 
-\section{EQUILIBRIUM STRUCTURE}
+Derive error dynamics
+Introduce control input function and show that it is stable without any disturbance
+
+Add the disturbance term and introduce adaptive update law
+Mention how for a fixed disturbance this is integral control 
+Go through the various developments of proving the disturbance case is stable for correct choice of gains
 
 \section{NUMERICAL EXAMPLE}
+Parameters used in the simulation
 
+Show stabilization with and without repulsive term
+Show stabilization with and without adaptive update law
+
+Plot of responses
+
+Get the configuration error function mapped onto the attitude sphere
+
+Show rotation animation of spacecraft avoiding constrained regions
 \section{EXPERIMENT}
 
+Discuss experimental setup of the hexrotor on spherical joint
+
+Describe aim of experiment. 
+Demonstrate that hexrotor fixed sensor can stabilize to desired attitude while avoiding an obstacle.
+Mount a sphere at an appropriate distance such that the subtended angle is equal to the cone constraint
+
+Show plots of response with and without avoidance term
+Response should be similar to numerical simulation
+
 \section{CONCLUSIONS}
+
+Discuss how this method allows for on board implementation of attitude avoidance during reorientations
+
+Improves upon previous work by extending to the full nonlinear manifold representation and avoids quaternion ambiguities
+
+Proven stable and validated via hardware experiments
+
 \addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
@@
 
-Appendixes should appear before the acknowledgment.
+Detail on finding bounds of \( \norm{\dot{e_R}} \)
+
+Stability proofs
+
+Further discussion on equilibrium positions and structure of configuration error function
 

### 2015-09-19 manuscript.tex
updating outline

@@
 \section{INTRODUCTION}
+
+Spacecraft are complicated electro mechanical devices and have become critical to national security.
+Spacecraft operations require extensive planning periods and human interaction to perform.
+The ability to robustly and autonomously plan and execute complicated spacecraft maneuvers can drastically improve the performance and duty cycle of assets.
+One key technology to enable spacecraft autonomy is the execution of large angular slews in the presence of constraints.
+For example, many spacecraft missions are equipped with sensitive optical instruments that require targeting while simultaneously avoiding direct exposure to sunlight.
+One of the distinct features of the attitude dynamics of a rigid body is that it evolves on a nonlinear manifold.
+The special orthogonal group, \( \SO \), yields unique properties that are not present in dynamic systems on a linear space. 
+In addition, the removal of constrained zones from the rotational configuration space results in a non-convex and more complicated system.
+The attitude dynamics and control of spacecraft without constraint has been extensively studied in the literature.
+This work builds upon previous results to include attitude constraints on \( \SO \).
+
+In this work an attitude control system is presented to track a desired trajectory while avoiding constrained regions. 
+The control system is formulated directly on the nonlinear manifold \( \SO \) and avoids the issues associated with minimal representations.
+The approach is based on a logarithmic barrier potential function developed directly on \( \SO \). 
+This avoids the singularities associated with Euler angles~\cite{mcinnes1994}.
+Euler angles are not suitable for large angle slew maneuvers as the type of Euler angle sequence should be switched to avoid the singular regions.
+Quaternions do not suffer from singularities but as the three-sphere double covers the special orthogonal group, there exists two antipodal points on the three-sphere which represents an equivalent attitude.
+As a result, control schemes based on quaternions should carefully resolve this ambiguity to avoid unwinding, where a rigid body unnecessarily rotates through a large angle in spite of a small initial error.~\cite{lee2011b}.
+
 introduction to attitude dynamics problem

### 2015-09-19 manuscript.tex
updated packages and included additions from dr. lee

@@
 
+\newcommand{\EditTL}[1]{{\color{red}\protect #1}}
+%\renewcommand{\EditTL}[1]{{\protect #1}}
+
+\newtheorem{definition}{Definition}
+\newtheorem{lem}{Lemma}
+\newtheorem{prop}{Proposition}
+\newtheorem{cor}{Corollary}
+\newtheorem{remark}{Remark}
+
 \title{\LARGE \bf
@@
 
-\author{Shankar Kulumani and Taeyoung Lee$^*$
- \thanks{Shankar Kulumani and Taeyoung Lee are with Department of Aerospace Engineering, George Washington University, Washington, DC. Email: {\tt\footnotesize \{skulumani, tylee\}@gwu.edu }}
+\title{\LARGE \bf
+Geometric Adaptive Control of Attitude Dynamics on $\SO$\\ with State Inequality Constraints}
+
+\author{Shankar Kulumani, Chris Poole, and Taeyoung Lee
+\thanks{Shankar Kulumani, Chris Poole, Taeyoung Lee, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 {\tt \{skulumani,poolec,tylee\}@gwu.edu}}
+\thanks{This research has been supported in part by NSF under the grants CMMI-1243000, CMMI-1335008, and CNS-1337722.}
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
+\section{Introduction}
 
@@
 
-\section{PROBLEM FORMULATION}
+\section{Problem Formulation}
 
@@
 
+\subsection{Attitude Dynamics}
+Consider the attitude dynamics of a rigid body. Define an inertial reference frame and a body-fixed frame. The configuration manifold of the attitude dynamics is the special orthogonal group:
+\begin{align*}
+\SO = \{R\in\Re^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\},
+\end{align*}
+where a rotation matrix $R\in\SO$ represents the transformation of the representation of a vector from the body-fixed frame to the inertial reference frame. The equations of motion are given by
+\begin{gather}
+J\dot\Omega + \Omega\times J\Omega = u+W(R,\Omega)\Delta,\label{eqn:Wdot}\\
+\dot R = R\hat\Omega,\label{eqn:Rdot}
+\end{gather}
+where $J\in\Re^{3\times 3}$ is the inertia matrix, and $\Omega\in\Re^3$ is the angular velocity represented with respect to the body-fixed frame.
+The control moment is denoted by $u\in\Re^3$, and it is expressed with respect to the body-fixed frame.
+It is assumed that the external disturbance is expressed by $W(R,\Omega)\Delta$, where $W(R,\Omega):\SO\times\Re^3\rightarrow \Re^{3\times p}$ is a known function of the attitude and the angular velocity, and $\Delta\in\Re^p$ is an unknown, but fixed uncertain parameter.
+
+At \refeqn{Rdot}, the \textit{hat} map $\wedge :\Re^{3}\rightarrow\so$ represents the transformation of a vector in $\Re^3$ to a $3\times 3$ skew-symmetric matrix such that $\hat x y = x\times y$ for any $x,y\in\Re^3$~\cite{BulLew05}.
+More explicitly,
+\begin{align*}
+\hat x = \begin{bmatrix} 0 & -x_3 & x_2 \\ x_3 & 0 & -x_1 \\ -x_2 & x_1 & 0\end{bmatrix},
+\end{align*}
+for $x=[x_1,x_2,x_3]^T\in\Re^3$. 
+The inverse of the hat map is denoted by the \textit{vee} map $\vee:\so\rightarrow\Re^3$. Several properties of the hat map are summarized as
+\begin{gather}
+%    \hat x y = x\times y = - y\times x = - \hat y x,\\
+    x\cdot \hat y z = y\cdot \hat z x,\quad \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z\label{eqn:STP},\\
+%    \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z,\label{eqn:VTP}\\
+%    C^TC=-C^T\hat e_3^2 C = I_2
+%    \hat x^T \hat x = (x^T x) I - x x^T,\\
+%    \hat x \hat y \hat x=-(y^Tx)\hat x,\\
+%    -\frac{1}{2}\tr{\hat x \hat y} = x^T y,\\
+    \widehat{x\times y} = \hat x \hat y -\hat y \hat x = yx^T-xy^T,\label{eqn:hatxy}\\
+    %\tr{\hat x A}=
+    \tr{A\hat x }=\frac{1}{2}\tr{\hat x (A-A^T)}=-x^T (A-A^T)^\vee,\label{eqn:hat1}\\
+%    \widehat{Ax} = \hat x \parenth{\frac{1}{2}\tr{A}I-A} + \parenth{\frac{1}{2}\tr{A}I-A}^T \hat x,\\
+    \hat x  A+A^T\hat x=(\braces{\tr{A}I_{3\times 3}-A}x)^{\wedge},\label{eqn:xAAx}\\
+R\hat x R^T = (Rx)^\wedge,\quad 
+R(x\times y) = Rx\times Ry\label{eqn:RxR}
+%,\label{eqn:Rxy}
+\end{gather}
+for any $x,y,z\in\Re^3$, $A\in\Re^{3\times 3}$ and $R\in\SO$. Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\Re^n$.
+
+%and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively.
+
+\subsection{Inequality Constraint}
+
+Describe inequality constraints.
+
+Define the desired attitude, and assume that it is sufficiently far from the boundary of the constraint.
+
+Describe the control objective.
+
+\section{Attitude Control on $\SO$ with Inequality Constraints}
+
+\subsection{Attitude Control}
+
 Configuration error function with attractive and repulsive terms
@@
 Show the development of the configuration error terms and equilibrium structure
-\section{ATTITUDE STABILIZATION}
 
@@
 Introduce control input function and show that it is stable without any disturbance
+
+\subsection{Adaptive Control}
 
@@
 
-\section{NUMERICAL EXAMPLE}
+\section{Numerical Examples}
 Parameters used in the simulation
@@
 Show rotation animation of spacecraft avoiding constrained regions
-\section{EXPERIMENT}
+
+\section{Experiments}
 
@@
 
-\section{CONCLUSIONS}
+\section{Conclusions}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{APPENDIX}
+\appendix
+\subsection{Proof of}
 
-Detail on finding bounds of \( \norm{\dot{e_R}} \)
+Detail on finding bounds of \( \norm{\dot{e}_R} \)
 
@@
 Further discussion on equilibrium positions and structure of configuration error function
-
-\section*{ACKNOWLEDGMENT}
 

### 2015-09-19 manuscript.tex
completed introduction section

@@
 \section{Introduction}
+Many researchers have focused on the study of the attitude dynamics of a rigid body~\cite{hughes2004,wertz1978}.
+Rigid body attitude control arises for aerospace vehicles, ground and underwater vehicles, and robotic systems.
+One distinctive feature of the attitude dynamics is that it evolves on a nonlinear manifold.
+The three-dimensional special orthogonal group is the set of \( 3 \times 3 \) orthogonal matrices whose determinant is one.
+This configuration space is not Euclidean and yields unique stability properties which are not observable on a linear space.
+For example, it is impossible to achieve global attitude stabilization using continuous time-invariant feedback~\cite{bhat2000}.
+Attitude control is typically studied using a variety of attitude parameterizations, such as Euler angles or quaternions~\cite{shuster1993}.
 
-Spacecraft are complicated electro mechanical devices and have become critical to national security.
-Spacecraft operations require extensive planning periods and human interaction to perform.
-The ability to robustly and autonomously plan and execute complicated spacecraft maneuvers can drastically improve the performance and duty cycle of assets.
-One key technology to enable spacecraft autonomy is the execution of large angular slews in the presence of constraints.
-For example, many spacecraft missions are equipped with sensitive optical instruments that require targeting while simultaneously avoiding direct exposure to sunlight.
-One of the distinct features of the attitude dynamics of a rigid body is that it evolves on a nonlinear manifold.
-The special orthogonal group, \( \SO \), yields unique properties that are not present in dynamic systems on a linear space. 
-In addition, the removal of constrained zones from the rotational configuration space results in a non-convex and more complicated system.
-The attitude dynamics and control of spacecraft without constraint has been extensively studied in the literature.
-This work builds upon previous results to include attitude constraints on \( \SO \).
+% topological obstruction - smooth control system can only achieve almost global asymptotic stability
 
-In this work an attitude control system is presented to track a desired trajectory while avoiding constrained regions. 
-The control system is formulated directly on the nonlinear manifold \( \SO \) and avoids the issues associated with minimal representations.
-The approach is based on a logarithmic barrier potential function developed directly on \( \SO \). 
-This avoids the singularities associated with Euler angles~\cite{mcinnes1994}.
-Euler angles are not suitable for large angle slew maneuvers as the type of Euler angle sequence should be switched to avoid the singular regions.
-Quaternions do not suffer from singularities but as the three-sphere double covers the special orthogonal group, there exists two antipodal points on the three-sphere which represents an equivalent attitude.
-As a result, control schemes based on quaternions should carefully resolve this ambiguity to avoid unwinding, where a rigid body unnecessarily rotates through a large angle in spite of a small initial error.~\cite{lee2011b}.
+% discuss issues with parameterizations
+All attitude parameterizations fail to represent the nonlinear configuration space both globally and uniquely~\cite{chaturvedi2011a}.
+For example, minimal attitude representations, such as Euler angle sequences or modified Rodriguez parameters, suffer from singularities.
+These attitude representations are not suitable for large angular slews.
+In order to avoid singularities the designer must carefully switch the chosen Euler angle sequence based on the operating region.
+Another option is to artificially limit the operating region of the rigid body.
+This ensures the system operates in a region free from singularities but limits the performance capabilities and ability to perform arbitrarily large angular maneuvers.
+Quaternions do not have singularities but they double cover the special orthogonal group.
+As a result, any physical attitude is represented by a pair of antipodal quaternions on the three-sphere.
+An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternion may not hold for the physical rigid body evolving on the special orthogonal group.
+During implementation, the design must carefully resolve this non-unique representation in quaternion based attitude control system to avoid undesirable unwinding behavior~\cite{bhat2000}.
+For certain initial conditions, where the rigid body starts closed to the desired attitude, the system unnecessarily rotates through a large angle even while the initial error is small.
 
-introduction to attitude dynamics problem
+% introduce concept of state inequality constraints and how it creates a nonconvex region 
+% mention applicability of this for spacecraft maneuvers, spherical air bearing testing, hardware limitations
+Many physical rigid body systems must perform large angular slews in the presence of state constraints.
+For example, autonomous spacecraft or aerial systems are typically equipped with sensitive optical payloads, such as infrared or interferometric sensors.
+These systems require retargeting while avoiding direct exposure to sunlight or other bright objects.
+Determining a satisfactory attitude control maneuver in the presence of state constraints is a challenging task.
+The removal of constrained regions from the rotational configuration space results in a \textit{nonconvex} region.
+The attitude control problem in the absence of constraints has been extensively studied~\cite{sanyal2008,lee2010,lee2011a}.
+However, the attitude control problem in the presence of constraints has received much less attention.
 
-Attitude dynamics evolve on a nonlinear manifold, unique properties not experienced in linear systems
+% discuss how previous papers (mcinnes and lee/meshabi) have short comings
+Several approaches have been developed to treat the attitude control problem in the presence of constraints.
+A geometric approach is used in~\cite{hablani1999} to determine feasible attitude trajectories prior to implementation.
+Typically, an optimal or easily implementable on-board control scheme for attitude maneuvers is considered without state constraints.
+The algorithm then seeks an intermediate point such that the control scheme can be applied for each segment without violation of the constraints.
+While the geometric method is conceptually simple it is difficult to generalize for an arbitrary amount of constraints.
+In addition, this geometric type of approach is only applicable to problems where the selection of intermediate points are computationally feasible
 
-difficulties of attitude control (topological restriction, nonlinear manifold)
+The approach in~\cite{frazzoli2001} involves the use of randomized motion planning algorithms to solve the constrained attitude control problem.
+A graph is generated consisting of vertices from an initial attitude to a desired attitude. 
+A random iterative search is conducted to determine a path through the graph such that a given cost functional is minimized.
+Once an appropriate path is determined an appropriate control is implemented to perform the attitude maneuver.
+The random search approach can only stochastically guarantee attitude convergence as it can be shown that as the number of vertices in the graph grow, the probability of non convergence goes to zero.
+However, the computational demand grows as the size of the graph is increased. 
+As a result, random search approaches are ill-suited to on-board implementation or in scenarios that require agile maneuvers.
 
-difficulties with attitude representations.
-
-Linear vector space used to represent motion on nonlinear manifold.
-
-Euler angles/MRP have singularities not suitable for large angular rotations
-
-Quaterions have no singularities but double coverage as the three sphere double covers the special orthogonal group.
-There are two equivalent quaternions that represent the same attitude.
-
-Discuss attitude control in the presence of constraints. 
-Key technology/capability to allow for autonomous operation of spacecraft and UAVs
-Sensitive optical instruments that require reorientation while avoiding exposure to the sun or bright sources
-
-Removal of constrained regions from the configuration space results in a nonconvex space/region.
-
-Benefits of this approach over previous work ( cite papers).
-Use of artifical potential functions
-Mcinnes looked at reorientation using euler angles. 
-Singularities would become evident for arbitrarily large angular slews
-
-Determine manuever a priori using geometric/kinematic relationships
-
-Computational based approaches.
-Randomized algorithms or direct optimal control
+In this work, we develop a geometric adaptive controller on \SO to reorient a rigid body in the presence of state inequality constraints.
+We apply a potential function based approach developed directly on the nonlinear manifold \SO.
+Geometric control is concerned with the development of control systems for dynamic systems that evolve on nonlinear manifolds.
+Artificial potential functions have previously been applied to the attitude control problem~\cite{lee2011b,mcinnes1994}.
+These approaches have used attitude parameterizations that give rise to singularities and ambiguities.
+By characterizing the intrinsic geometric properties of \SO, we completely avoid issues associated with local parameterizations of the configuration manifold.
+In this paper, a Lyapunov analysis is presented to guarantee stability in the presence of state constraints
+In addition, we formulate an adaptive update law to enable attitude convergence in the presence of disturbances.
+These results are demonstrated via numerical examples and experimental results on a robotic aerial vehicle.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix
@@
 
-\bibliography{library}
+\bibliography{BibMaster,library}
 \bibliographystyle{IEEEtran}

### 2015-09-19 manuscript.tex
added problem formulation section

@@
 
-Describe attitude dynamics EOMS.
-Explain attitude representation using \SO.
-Hat and vee map properties used in developments
-
 \subsection{Attitude Dynamics}
-Consider the attitude dynamics of a rigid body. Define an inertial reference frame and a body-fixed frame. The configuration manifold of the attitude dynamics is the special orthogonal group:
+Consider the attitude dynamics of a rigid body. 
+Define an inertial reference frame and a body-fixed frame. 
+The configuration manifold of the attitude dynamics is the special orthogonal group:
 \begin{align*}
-\SO = \{R\in\Re^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\},
+	\SO = \{R\in\Re^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\} \, ,
 \end{align*}
-where a rotation matrix $R\in\SO$ represents the transformation of the representation of a vector from the body-fixed frame to the inertial reference frame. The equations of motion are given by
+where a rotation matrix $R\in\SO$ represents the transformation of the representation of a vector from the body-fixed frame to the inertial reference frame. 
+The equations of motion are given by
 \begin{gather}
-J\dot\Omega + \Omega\times J\Omega = u+W(R,\Omega)\Delta,\label{eqn:Wdot}\\
-\dot R = R\hat\Omega,\label{eqn:Rdot}
+	J\dot\Omega + \Omega\times J\Omega = u+W(R,\Omega)\Delta \, ,\label{eqn:Wdot}\\
+	\dot R = R\hat\Omega \, ,\label{eqn:Rdot}
 \end{gather}
@@
 \end{gather}
-for any $x,y,z\in\Re^3$, $A\in\Re^{3\times 3}$ and $R\in\SO$. Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\Re^n$.
+for any $x,y,z\in\Re^3$, $A\in\Re^{3\times 3}$ and $R\in\SO$. 
+Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\Re^n$ and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively.
+The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A}_F = \tr{A^T A} \).
+This results in \( \norm{A} \leq \norm{A}_F \leq \sqrt{r}\norm{A} \), where \( r \) is the rank of A.
 
-%and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively.
+\subsection{State Inequality Constraint}
 
-\subsection{Inequality Constraint}
-
-Describe inequality constraints.
-
-Define the desired attitude, and assume that it is sufficiently far from the boundary of the constraint.
-
-Describe the control objective.
+The two-sphere is the manifold of unit-vectors in \( \R^3 \) such that\( \Sph^2 = \brace{ q \in \R^3 | \norm{q} = 1}\).
+We define \( r \in \Sph^2 \) to be a unit vector from the mass center of the rigid body and represented with respect to the body-fixed frame.
+For example, \( r \) may represent the pointing direction of an on board optical sensor.
+We define \( v \in \Sph^2 \) to be a unit vector from the mass center of the rigid body towards an undesired pointing direction and represented in the inertial reference frame.
+For example, \( v \) may represent the inertial direction of a bright celestial object or the incoming direction of particles or other debris
+It is further assumed that optical sensor has a strict non-exposure constraint with respect to the celestial object.
+We formulate this hard constraint as
+\begin{align}
+	r^T R^T v \leq \cos \theta \, , \label{eqn:constraint}
+\end{align}
+where \( \theta \) is the required minimum angular separation between \( r \) and \( R^T v \). 
+The objective is to a determine a control input \( u \) that stabilizes the system from an initial attitude \( R_0 \) to a desired attitude \( R_d \) while ensuring that~\cref{eqn:constraint} is satisfied.
 
 \section{Attitude Control on $\SO$ with Inequality Constraints}
+Constructing configuration error function
 

### 2015-09-20 ACC16.2.tex
removed unneeded files and changed name to follow dr. lee's format

--- 2015-09-19 manuscript.tex
@@
 \newtheorem{remark}{Remark}
-
-\title{\LARGE \bf
-Constrained Attitude Control
-}
 
@@
 \section{Attitude Control on $\SO$ with Inequality Constraints}
+Discuss importance of choosing a configuration error function
+
 Constructing configuration error function
+
+Log barrier for repulsive term
+
+Standard attractive error function
+
+cite bullo and Dr. Lee papers
 
@@
 
-Show stabilization with and without repulsive term
-Show stabilization with and without adaptive update law
+Inertia matrix of hexrotor
+
+control gains
+
+define sensor and constraint axis
+
+Define initial and desired condition
+
+Present three cases
+
+Show stabilization without repulsive term (passes through constraint)
+Show stabilization with avoidance term without disturbance
+Show stabilization with disturbance and adaptive update law
 
 Plot of responses
-
-Get the configuration error function mapped onto the attitude sphere
 

### 2015-09-21 ACC16.2.tex
began the attitude control section

@@
 By characterizing the intrinsic geometric properties of \SO, we completely avoid issues associated with local parameterizations of the configuration manifold.
-In this paper, a Lyapunov analysis is presented to guarantee stability in the presence of state constraints
+In this paper, we present a Lyapunov analysis to guarantee stability in the presence of state constraints.
 In addition, we formulate an adaptive update law to enable attitude convergence in the presence of disturbances.
@@
 The control moment is denoted by $u\in\Re^3$, and it is expressed with respect to the body-fixed frame. 
-It is assumed that the external disturbance is expressed by $W(R,\Omega)\Delta$, where $W(R,\Omega):\SO\times\Re^3\rightarrow \Re^{3\times p}$ is a known function of the attitude and the angular velocity, and $\Delta\in\Re^p$ is an unknown, but fixed uncertain parameter.
+We assume that the external disturbance is expressed by $W(R,\Omega)\Delta$, where $W(R,\Omega):\SO\times\Re^3\rightarrow \Re^{3\times p}$ is a known function of the attitude and the angular velocity, and $\Delta\in\Re^p$ is an unknown, but fixed uncertain parameter.
+In addition, we assume that a bound on \( W(R, \Omega) \) is known and given by
+\begin{equation}
+	\norm{W} \leq B_W \, . \label{eqn:W_bound}
+\end{equation}
 
-At \refeqn{Rdot}, the \textit{hat} map $\wedge :\Re^{3}\rightarrow\so$ represents the transformation of a vector in $\Re^3$ to a $3\times 3$ skew-symmetric matrix such that $\hat x y = x\times y$ for any $x,y\in\Re^3$~\cite{BulLew05}.
+In~\refeqn{Rdot}, the \textit{hat} map $\wedge :\Re^{3}\rightarrow\so$ represents the transformation of a vector in $\Re^3$ to a $3\times 3$ skew-symmetric matrix such that $\hat x y = x\times y$ for any $x,y\in\Re^3$~\cite{BulLew05}.
 More explicitly,
@@
 
-The two-sphere is the manifold of unit-vectors in \( \R^3 \) such that\( \Sph^2 = \brace{ q \in \R^3 | \norm{q} = 1}\).
+The two-sphere is the manifold of unit-vectors in \( \R^3 \) such that \( \Sph^2 = \{ q \in \R^3 \,  \vert \, \norm{q} = 1 \}\).
 We define \( r \in \Sph^2 \) to be a unit vector from the mass center of the rigid body and represented with respect to the body-fixed frame.
@@
 \end{align}
-where \( \theta \) is the required minimum angular separation between \( r \) and \( R^T v \). 
-The objective is to a determine a control input \( u \) that stabilizes the system from an initial attitude \( R_0 \) to a desired attitude \( R_d \) while ensuring that~\cref{eqn:constraint} is satisfied.
+where \( \ang{0} \leq \theta \leq \ang{90}  \) is the required minimum angular separation between \( r \) and \( R^T v \). 
+The objective is to a determine a control input \( u \) that stabilizes the system from an initial attitude \( R_0 \) to a desired attitude \( R_d \) while ensuring that~\refeqn{eqn:constraint} is always satisfied.
 
 \section{Attitude Control on $\SO$ with Inequality Constraints}
-Discuss importance of choosing a configuration error function
+The first step in designing a control system on a nonlinear manifold \( \Q \) is the selection of a proper configuration error function.
+This configuration error function, \( \Psi : \Q \times \Q \to \R \), is a smooth and proper positive definite function that measures the error between the current configuration and a desired configuration.
+Once an appropriate configuration error function is chosen, one can then define a configuration error vector and a velocity error vector in the tangent space \( \mathsf{T}_q \Q \) through use of the derivatives of \( \Psi \)~\cite{bullo2004}.
+With the configuration error function and vectors the remaining procedure is similar to nonlinear control design on Euclidean vector spaces.
+One chooses control inputs as functions of the state through a Lyapunov analysis on \Q.
 
-Constructing configuration error function
+A new configuration error function is proposed for attitude control in the presence of state inequality constraints.
+We extend the form used in~~\cite{bullo2004,lee2011a} for attitude control on \SO with the addition of a logarithmic barrier function.
+\begin{prop}[Attitude Error Function] \label{prop:config_error}
+We assume a desired attitude command \( ( R_d, \Omega_d = 0 ) \), the current attitude and angular velocity \( ( R, \Omega) \), and a state constraint~\refeq{eqn:constraint} are given.
+We define an attitude error function \( \Psi : \SO \times \SO \to \R \), and attitude error vector \( e_R : \SO \times \SO \to \R \), and an angular velocity error vector \( e_\Omega : \R^3 \to \R^3 \) as follows:
+\begin{gather}
+	\Psi(R) = A(R) B(R) \, , \label{eqn:psi} \\
+	e_R = e_{R_A} B + A e_{R_B} \, , \label{eqn:eR} \\
+	e_\Omega = \Omega \, , \label{eqn:eW}
+\end{gather}
+with
+\begin{gather}
+	A(R) = \frac{1}{2} \tr{G \left( I - R_d^T R\right)} \, , \label{eqn:A} \\
+	B(R) = 1 - \frac{1}{\alpha} \ln \left( \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta}\right) \, . \label{eqn:B} \\
+	e_{R_A} = \frac{1}{2} \parenth{G R_d^T R - R^T R_d G} ^ \vee \, , \label{eq:eRA} \\
+	e_{R_B} = \frac{ \left( R^T v\right)^\vee r}{\alpha \left(r^T R^T v - \cos \theta \right)} \, . \label{eq:eRB} 
+\end{gather}	
+where the matrix \( G \in \R^{3 \times 3} \) is defined as a diagonal matrix matrix for distinct, positive constants \( g_1, g_2, g_3 \in \R \).
+Then, the following properties hold
+\begin{enumerate}[(i)]
+	\item \(\Psi\) is locally positive definite about \( R = R_d\)
+	\item The variation of \( \Psi \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
+	\begin{align}
+		\dirDiff{\Psi}{R} &= \dirDiff{A}{R} \,  B(R) + A \,  \dirDiff{B}{R} \, , \\
+		\dirDiff{A}{R} &= \eta \cdot e_{R_A} \, , \\
+		\dirDiff{B_i}{R} &= \eta \cdot e_{R_{B_i}} \, .
+	\end{align}
+	\item The critical points of \( \Psi \),where \( e_R = 0\), are \( \braces{R_d} \bigcup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \) and \( R^T v = \pm r \).
+	\item An upper bound of \( \norm{e_{R_A}} \) is given as:
+	\begin{align}
+		\norm{e_{R_A}}^2 \leq \frac{\Psi}{b_1} \, ,
+	\end{align}
+	where the constant \( b_1 \) is given by \( b_1 = \frac{h_1}{h_2 + h_3} \) for 
+	\begin{align*}
+		h_1 &= \min{g_1 + g_2, g_2 + g_3 , g_3 + g_1} \, ,\\
+		h_2 &= \min{\parenth{g_1 -g_2}^2,\parenth{g_2 -g_3}^2 , \parenth{g_3 -g_1}^2} \, ,\\
+		h_3 &= \min{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} \, ,\\				
+	\end{align*}
+	\item An upper bound of \( \norm{e_{R_B}} \) is given as:
+	\begin{align}
+		\norm{e_{R_B}} \leq \frac{\sin{\frac{\pi}{2} - \theta}}{\alpha \parenth{\beta - \cos \theta}}
+	\end{align}
+\end{enumerate}
+\end{prop}
+
+\begin{proof}
+	See~\Cref{proof:config_error}
+\end{proof}
+
+Discussion of error function
+
+Give some bounds on B?
+
+The attractive error function has been used for attitude control on \SO.
+In order to incorporate the state inequality constraints we apply the logarithmic barrier function.
+The positive constant \( \alpha \) serves to shape the barrier function.
+As \( \alpha \) is increased the impact of \( B(R) \) is reduced.
+
+\Cref{eqn:psi} is composed of an attractive term \( A (R) \) and a repulsive term \( B(R) \) which are given by
+Here we summarize
 
 Log barrier for repulsive term
+Some properties of the log barrier term
 
 Standard attractive error function
+Configuration error function with attractive and repulsive terms
+Define the various attitude error functions and where they are derived from
+summarize some of the properties of the attractive error function from previous papers
 
-cite bullo and Dr. Lee papers
+Show the development of the configuration error terms and equilibrium structure
+
+Derive error dynamics
 
@@
 
-Configuration error function with attractive and repulsive terms
-Define the various attitude error functions and where they are derived from
-summarize some of the properties of the attractive error function from previous papers
-Show the development of the configuration error terms and equilibrium structure
+Introduce control input function and show that it is stable without any disturbance
 
-Derive error dynamics
-Introduce control input function and show that it is stable without any disturbance
+Lyapunov function
+
+\begin{prop}[Error Dynamics]\label{prop:error_dyn}
+Error dynamics (time derivatives of everything)
+\end{prop}
+\begin{proof}
+	Either here or in the appendix
+\end{proof}
 
@@
 Add the disturbance term and introduce adaptive update law
+
 Mention how for a fixed disturbance this is integral control
+
 Go through the various developments of proving the disturbance case is stable for correct choice of gains
+
+Positive semi definite matrix
+
+Get three polynomials (can use cubic or quartic functions to get analytical result)
+
+Define domain of consideration \( \Psi \leq \psi \) and \( r^T R^T v \leq \beta \)
+
+Give example for a simple case
 
@@
 \appendix
-\subsection{Proof of}
+\subsection{Proof of~\Cref{prop:config_error}} \label{proof:config_error}
 
+Positive definite \( \Psi \)
+
+Structure of \( B \)
+
+Critical Points of \( \Psi \)
+
+Bound of \( \norm{e_{R_A}} \)
+
+\subsection{Proof of }
 Detail on finding bounds of \( \norm{\dot{e}_R} \)
 
-Stability proofs
+Lots of intermediate terms
 
-Further discussion on equilibrium positions and structure of configuration error function
+\subsection{Proof of }
+Stability proofs for case with and without disturbance
 

### 2015-09-21 ACC16.2.tex
added custom equation referencing for IEEE. detail on configuration error function

@@
 where \( \ang{0} \leq \theta \leq \ang{90}  \) is the required minimum angular separation between \( r \) and \( R^T v \). 
-The objective is to a determine a control input \( u \) that stabilizes the system from an initial attitude \( R_0 \) to a desired attitude \( R_d \) while ensuring that~\refeqn{eqn:constraint} is always satisfied.
+The objective is to a determine a control input \( u \) that stabilizes the system from an initial attitude \( R_0 \) to a desired attitude \( R_d \) while ensuring that~\cref{eqn:constraint} is always satisfied.
 
@@
 	B(R) = 1 - \frac{1}{\alpha} \ln \left( \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta}\right) \, . \label{eqn:B} \\
-	e_{R_A} = \frac{1}{2} \parenth{G R_d^T R - R^T R_d G} ^ \vee \, , \label{eq:eRA} \\
-	e_{R_B} = \frac{ \left( R^T v\right)^\vee r}{\alpha \left(r^T R^T v - \cos \theta \right)} \, . \label{eq:eRB} 
+	e_{R_A} = \frac{1}{2} \parenth{G R_d^T R - R^T R_d G} ^ \vee \, , \label{eqn:eRA} \\
+	e_{R_B} = \frac{ \left( R^T v\right)^\vee r}{\alpha \left(r^T R^T v - \cos \theta \right)} \, . \label{eqn:eRB} 
 \end{gather}	
@@
 \begin{enumerate}[(i)]
-	\item \(\Psi\) is locally positive definite about \( R = R_d\)
-	\item The variation of \( \Psi \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
+	\item \label{item:prop_psi_psd} \(\Psi\) is locally positive definite about \( R = R_d\)
+	\item \label{item:prop_er} The variation of \( \Psi \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
 	\begin{align}
-		\dirDiff{\Psi}{R} &= \dirDiff{A}{R} \,  B(R) + A \,  \dirDiff{B}{R} \, , \\
-		\dirDiff{A}{R} &= \eta \cdot e_{R_A} \, , \\
+		\dirDiff{\Psi}{R} &= \dirDiff{A}{R} \,  B(R) + A \,  \dirDiff{B}{R} \, . \\
+	\end{align}
+	\item \label{item:prop_era}The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
+	\begin{align}
+		\dirDiff{A}{R} &= \eta \cdot e_{R_A} \, .
+	\end{align}
+	\item \label{item:prop_erb} The variation of \( B(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
+	\begin{align}
 		\dirDiff{B_i}{R} &= \eta \cdot e_{R_{B_i}} \, .
 	\end{align}
-	\item The critical points of \( \Psi \),where \( e_R = 0\), are \( \braces{R_d} \bigcup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \) and \( R^T v = \pm r \).
-	\item An upper bound of \( \norm{e_{R_A}} \) is given as:
+	\item \label{item:prop_crit}The critical points of \( \Psi \),where \( e_R = 0\), are \( \braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \) and \( R^T v = \pm r \).
+	\item \label{item:prop_era_upbound}An upper bound of \( \norm{e_{R_A}} \) is given as:
 	\begin{align}
@@
 	\end{align*}
-	\item An upper bound of \( \norm{e_{R_B}} \) is given as:
-	\begin{align}
-		\norm{e_{R_B}} \leq \frac{\sin{\frac{\pi}{2} - \theta}}{\alpha \parenth{\beta - \cos \theta}}
-	\end{align}
 \end{enumerate}
@@
 
+\begin{enumerate}[(i)]
+	\item An upper bound of \( \norm{e_{R_B}} \) is given as:
+	\begin{align}
+		\norm{e_{R_B}} \leq \frac{\sin{\frac{\pi}{2} - \theta}}{\alpha \parenth{\beta - \cos \theta}}
+	\end{align}
+\end{enumerate}
 Add the disturbance term and introduce adaptive update law
@@
 \subsection{Proof of~\Cref{prop:config_error}} \label{proof:config_error}
+The proof of~\cref{item:prop_era_upbound} is available in~\cite{lee2011a}.
+To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a locally positive definite function about \( R = R_d \)~\cite{bullo2004}.
+The constraint angle is assumed \( \ang{0} \leq \theta \leq \ang{90} \) such that \( 0 \leq \cos \theta \).
+The term \( r^T R^T v \) represents the cosine of the angle between the body fixed vector \( r \) and the inertial vector \( v \). 
+It follows that
+\begin{align*}
+	0 \leq  \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta} \leq 1 \, ,
+\end{align*}
+for all \( R \in SO \). 
+As a result, the negative logarithm is always positive and
+\begin{align*}
+	1 < B \, .
+\end{align*}
+The product~\cref{eqn:psi} is composed of two positive terms and is therefore also positive definite, and has a single critical point at \( R = R_d \).
 
-Positive definite \( \Psi \)
+Next, we consider~\cref{item:prop_era}.
+The variation of~\cref{eqn:A} is taken with respect to \( \delta R = R \hat \eta \) as
+\begin{align*}
+	\dirDiff{A}{R} &= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
+	&= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee \, ,
+\end{align*}
+where we used~\cref{eqn:hat1}.
 
-Structure of \( B \)
+A straightforward application of the chain and product rules of differentiation allows us to show~\cref{item:prop_erb} as
+\begin{align*}
+	\dirDiff{B_i}{R} &= -\frac{1}{\alpha_i} \left[\left(\frac{1+\cos \theta_i}{\cos \theta_i - r^T R^T v_i} \right) \left(\frac{-1}{1+\cos \theta_i} \right) \left(-\eta \cdot \left( R^T v_i\right)^\vee r \right)\right] && x \cdot \hat{y} z = y \cdot \hat{z}x  \\
+	&= \eta \cdot \frac{ - \left( R^T v_i\right)^\vee r}{\alpha_i \left(\cos \theta_i - r^T R^T v_i \right)} \, ,
+\end{align*}
+where the scalar triple product~\cref{eqn:STP} was used.
 
-Critical Points of \( \Psi \)
-
-Bound of \( \norm{e_{R_A}} \)
+To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
+The attitude error between \( R \) and \( R_d \) is defined as \( Q \in SO \) as
+\begin{align*}
+	Q = R_d^T R = 
+	\begin{bmatrix}
+		q_{11} & q_{12} & q_{13} \\
+		q_{21} & q_{22} & q_{23} \\
+		q_{31} & q_{32} & q_{33}
+	\end{bmatrix} \, .
+\end{align*}
+Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
+\begin{subequations}
+\begin{align}
+	g_3 q_{32} &= g_2 q_{23} \, , \\
+	g_1 q_{13} &= g_3 q_{31} \, , \\
+	g_2 q_{21} &= g_1 q_{12} \, .
+\end{align}
+\end{subequations}
+These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
+Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
+\begin{subequations}
+\begin{align}
+	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 \, , \\
+	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, , \\
+	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, .
+\end{align}
+\end{subequations}
+As a result, all the off diagonal terms of \( Q = R_d^T R \), namely \( q_{12}= q_{13} = q_{23} = 0 \).
+Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
+There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180},
+The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
+This condition only occurs if the representation of the inertial constraint vector, \( v \), in the body frame is parallel or anti-parallel to the body vector, \( r \).
 

### 2015-09-21 ACC16.2.tex
start of error dynamics proposition

@@
 
-Discussion of error function
+\Cref{eqn:psi} is composed of an attractive term \( A (R) \) and a repulsive term \( B(R) \).
+The attractive error function has been used for attitude control on \SO.
+In order to incorporate the state inequality constraints we apply a logarithmic barrier function term.
+Barrier functions are typically used in optimal control and motion planning applications.
+As the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
+The logarithmic function is popular as it quickly decays away from the constraint boundary.
+The positive constant \( \alpha \) serves to shape the barrier function.
+As \( \alpha \) is increased the impact of \( B(R) \) is reduced away from the constraint boundary.
 
-Give some bounds on B?
+\begin{prop}[Error Dynamics]\label{prop:error_dyn}
+	The attitude error dynamics for \( \Psi, e_R, e_\Omega \) satisfy
 
-The attractive error function has been used for attitude control on \SO.
-In order to incorporate the state inequality constraints we apply the logarithmic barrier function.
-The positive constant \( \alpha \) serves to shape the barrier function.
-As \( \alpha \) is increased the impact of \( B(R) \) is reduced.
+	Psi dot
 
-\Cref{eqn:psi} is composed of an attractive term \( A (R) \) and a repulsive term \( B(R) \) which are given by
-Here we summarize
+	er dot
 
-Log barrier for repulsive term
-Some properties of the log barrier term
+	er B dot
 
-Standard attractive error function
-Configuration error function with attractive and repulsive terms
-Define the various attitude error functions and where they are derived from
-summarize some of the properties of the attractive error function from previous papers
+	erA dot
 
-Show the development of the configuration error terms and equilibrium structure
+	A dot
 
-Derive error dynamics
+	B dot
+
+	e omega dot
+
+\end{prop}
+
+\begin{proof}
+	See~\Cref{proof:error_dyn}
+\end{proof}
 
@@
 Lyapunov function
-
-\begin{prop}[Error Dynamics]\label{prop:error_dyn}
-Error dynamics (time derivatives of everything)
-\end{prop}
-\begin{proof}
-	Either here or in the appendix
-\end{proof}
 
@@
 
+\subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
+
 \subsection{Proof of }
+Stability proofs for case with and without disturbance
+
 Detail on finding bounds of \( \norm{\dot{e}_R} \)
@@
 Lots of intermediate terms
-
-\subsection{Proof of }
-Stability proofs for case with and without disturbance
 

### 2015-09-21 ACC16.2.tex
finished intro to attitude control section

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{Introduction}\label{sec:intro}
 Many researchers have focused on the study of the attitude dynamics of a rigid body~\cite{hughes2004,wertz1978}.
@@
 These results are demonstrated via numerical examples and experimental results on a robotic aerial vehicle.
-
-\section{Problem Formulation}
-
-\subsection{Attitude Dynamics}
+\section{Problem Formulation}\label{sec:prob_form}
+\subsection{Attitude Dynamics}\label{sec:att_dyn}
 Consider the attitude dynamics of a rigid body. 
@@
 As \( \alpha \) is increased the impact of \( B(R) \) is reduced away from the constraint boundary. 
+In addition, it is possible to incorporate an arbitrary number of state inequality constraints of the form given in~\cref{eqn:constraint}.
+The configuration error function may be reformulated as \( \Psi = A \bracket{1 + \sum B_i} \) where \( B_i = B - 1 \).
+In this manner, one may enforce multiple state inequality constraints on the control system.
 
@@
 	The attitude error dynamics for \( \Psi, e_R, e_\Omega \) satisfy 
-
-	Psi dot
-
-	er dot
-
-	er B dot
-
-	erA dot
-
-	A dot
-
-	B dot
-
-	e omega dot
+	\begin{gather}
+		\diff{}{t} \parenth{\Psi} = e_R \cdot e_\Omega \, , \label{eqn:psi_dot}\\
+		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B + e_{R_A} \dot{B} + \dot{A}e_{R_B} + A \dot{e}_{R_B} \, , \label{eqn:eR_dot}\\
+		\diff{}{t} \parenth{e_{R_A}} = E(R, R_d) e_\Omega \, , \label{eqn:eRA_dot} \\
+		\diff{}{t} \parenth{e_{R_B}} = F(R) e_\Omega \, , \label{eqn:eRB_dot} \\
+		\diff{}{t} \parenth{A} = e_{R_A} \cdot e_\Omega \, , \label{eqn:A_dot} \\
+		\diff{}{t} \parenth{B} = e_{R_B} \cdot e_\Omega \, , \label{eqn:B_dot} \\
+		\diff{}{t} \parenth{e_\Omega} = J^{-1} \parenth{-\Omega \times J \Omega + u + W(R, \Omega) \Delta} \, , \label{eqn:eW_dot}
+	\end{gather}
+	where the matrices \(E(R,R_d), F(R) \in \R^{3\times3} \) are given by
+	\begin{gather}
+		E(R,R_d) = \frac{1}{2} \parenth{\tr{R^T R_d G}I - R^T R_d G} \, , \label{eqn:E} \\
+		F(R) = \frac{1}{\alpha \parenth{r^T R^T v - \cos \theta}} \left[\parenth{v^T R r} I - R^T v r^T + \right. \nonumber \\
+		\left. \frac{R^T \hat{v} R r v^T R \hat{r}}{\parenth{r^T R^T v - \cos \theta}}\right] \, . \label{eqn:F}
+	\end{gather}
 
@@
 
-\subsection{Attitude Control}
+\subsection{Attitude Control without disturbance}
 
@@
 \subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
+From the kinematics~\cref{eqn:Rdot} and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
+\begin{gather*}
+	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega \, .
+\end{gather*}
+Applying this to the time derivative of~\cref{eqn:A} gives
+\begin{gather*}
+	\diff{}{t} A = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} \, .
+\end{gather*}
+Applying~\cref{eqn:hat1} into this shows~\cref{eqn:A_dot}.
+Next, the time derivative of the repulsive error function is given by
+\begin{gather*}
+	\diff{}{t} B = \frac{r_i^T \parenth{\hat{\Omega} R^T} v_i}{\alpha \parenth{r_i^T R^T v_i - \cos \theta}} \, .
+\end{gather*}
+Using the scalar triple product, given by~\cref{eqn:STP}, one can reduce this to~\cref{eqn:B_dot}.
+The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
+\begin{gather*}
+	\diff{}{t} e_{R_A} = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee \, .
+\end{gather*}
+Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eqn:eRA_dot,eqn:E}.
 
+We take the time derivative of the repulsive attitude error vector, \( e_{R_B} \), as
+\begin{gather*}
+	\diff{}{t} e_{R_B} = a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r \, ,
+\end{gather*}
+with \( a \in \R \) and \( b \in \R\) given by 
+\begin{gather*}
+	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} \, ,
+	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} \, .
+\end{gather*}
+Using the scalar triple product from~\cref{eqn:STP} as \( r \cdot \Omega \times \parenth{R^T v} = \parenth{R^T v} \cdot r \times \Omega \) gives~\cref{eqn:eRB_dot,eqn:F}.
+
+We show the time derivative of the configuration error function as
+\begin{gather*}
+	\diff{}{t} \Psi = \dot{A} B + A \dot{B} \, .
+\end{gather*}
+A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and appplying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
+
+The time-derivative of the angular velocity error, \( e_\Omega \), is given by
+\begin{align*}
+	\diff{}{t} e_\Omega &= \dot{\Omega} \\
+	&= J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } \, ,
+\end{align*}
+where we have used the dynamic equations of motion from~\cref{eqn:Wdot}. 
 \subsection{Proof of }

### 2015-09-21 ACC16.2.tex
starting on attitude control without disturbance

@@
 We extend the form used in~~\cite{bullo2004,lee2011a} for attitude control on \SO with the addition of a logarithmic barrier function.
+We use the configuration error function to develop a nonlinear geometric attitude controller for the stabilization of a general rigid body. 
+A smooth control system is first developed for the no disturbance case and then extended to include an adaptive update law for stabilization in the presence of unknown disturbances.
+
 \begin{prop}[Attitude Error Function] \label{prop:config_error}
@@
 \subsection{Attitude Control without disturbance}
+We introduce a nonlinear geometric controller for the attitude stabilization of a rigid body.
+We assume that there is no disturbance, i.e., \( \Delta = 0 \).
+\begin{prop}[Attitude Control]\label{prop:att_control}
 
+\end{prop}
 Introduce control input function and show that it is stable without any disturbance
@@
 
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{align*}
-	\dirDiff{B_i}{R} &= -\frac{1}{\alpha_i} \left[\left(\frac{1+\cos \theta_i}{\cos \theta_i - r^T R^T v_i} \right) \left(\frac{-1}{1+\cos \theta_i} \right) \left(-\eta \cdot \left( R^T v_i\right)^\vee r \right)\right] && x \cdot \hat{y} z = y \cdot \hat{z}x  \\
-	&= \eta \cdot \frac{ - \left( R^T v_i\right)^\vee r}{\alpha_i \left(\cos \theta_i - r^T R^T v_i \right)} \, ,
+	\dirDiff{B}{R} &= -\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta_i} \right) \right]  \\
+	&= \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} \, ,
 \end{align*}
@@
 The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
-This condition only occurs if the representation of the inertial constraint vector, \( v \), in the body frame is parallel or anti-parallel to the body vector, \( r \).
+This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \).
 
@@
 
+\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
+                                  % on the last page of the document manually. It shortens
+                                  % the textheight of the last page by a suitable amount.
+                                  % This command does not take effect until the next page
+                                  % so it should come on the page before the last. Make
+                                  % sure that you do not shorten the textheight too much.
+
 \bibliography{BibMaster,library}

### 2015-09-22 ACC16.2.tex
completed attitude control without disturbance

@@
 	\end{gather}
-
 \end{prop}
@@
 \begin{prop}[Attitude Control]\label{prop:att_control}
+	Given a desired attitude command \( \parenth{R_d, \Omega_d = 0} \) and positive constants \( k_R, k_\Omega \in \R \) we define a control input \( u \in \R^3 \) as follows
+	\begin{gather}
+		u = -k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega \, . \label{eqn:nodist_control}
+	\end{gather}
+	Then the zero equilibrium of the attitude errors \( \parenth{e_R, e_\Omega} \) is asymptotically stable, i.e., \(e_R, e_\Omega \to 0 \) as \( t \to \infty \).
+\end{prop}
 
-\end{prop}
-Introduce control input function and show that it is stable without any disturbance
+\begin{proof}\label{proof:att_control}
+	Consider the following Lyapunov function:
+	\begin{gather}
+		V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d) \, . \label{eqn:v_nodist}
+	\end{gather}
+	From~\cref{item:prop_psi_psd}, we obtain
+	\begin{gather*}
+		V \geq 0 \, .
+	\end{gather*}
+	Using~\cref{eqn:eW_dot,eqn:psi_dot} with \( \Delta = 0 \), the time derivative of \( V \) is given by
+	\begin{align}
+		\dot{V} &= e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
+		&= -k_\Omega \norm{e_\Omega}^2 \, . \label{eqn:vdot_nodist}
+	\end{align}
+	Since \( V \) is positive definite and \( \dot{V} \) is negative definite this implies that the zero equilibrium point \( e_R, e_\Omega \) is asymptotically stable.
+\end{proof}
 
-Lyapunov function
+This proposition only guarantees that the attitude error vector \( e_R \) asymptotically converges to zero.
+However, this does not necessarily show that \( R \to R_d \) as \( t \to \infty \). 
+There are three additional critical points of \( \Psi \) where \( e_R = 0 \).
+At an undesired equilibrium \( R = \exp{\pi \hat{e}_i} R_d \) and \( e_\Omega =0 \). 
+This results in \( A \) having a value of \( g_1 + g_2, g_2 + g_3 \) or \( g_3 + g_1 \).
+At any of these undesired equilibria we have \( V = k \). 
+We define an augmented Lyapunov function as
+\begin{align*}
+	W = k - V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R (\frac{k}{k_R}+ \Psi(R,R_d)) \, .
+\end{align*}
+We can choose an attitude \( R \) arbitrarily close to the equilibrium point \( \exp{ \pi \hat{e}_i} R_d \) such that the \( k_r \parenth{\frac{k}{k_R}+\Psi }> 0 \).
+This is due to the fact that \( \Psi \) is positive definite about \( R = R_d \) as shown in~\cref{item:prop_psi_psd}.
+If \( e_\Omega \) is sufficiently small this results in \( W > 0 \) and \( \dot{W} = -\dot{V} > 0\) from~\cref{eqn:vdot_nodist}.
+According to Chateav's theorem the undesired equilibria are unstable~\cite{khalil1996}.
+As a result, we can claim that the desired equilibrium \( R = R_d \text{ and } e_\Omega = 0 \) is almost globally asymptotically stable.
 
@@
 Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
-There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180},
+There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180}.
 The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
-This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \).
-
+This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \) .
+The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
 \subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}

### 2015-09-22 ACC16.2.tex
starting adaptive control law section

@@
 \subsection{Adaptive Control}
+We extend the results of the previous section with the addition of a fixed but unknown disturbance \( \Delta \).
+This scenario is typical of many mechanical systems and represents unmodeled dynamics or external moments acting on the system.
+For example, Earth orbiting spacecraft typically experience both a torque due to a gravitational gradient as well as external torques to due solar radiation pressure.
+Aerial vehicles will similarly experience external torques due to air currents or turbulence.
+A smooth control system is introduced to asymptotically stabilize the system to a desired attitude while ensuring that state constraints are satisfied.
+
+\begin{prop}[Bound on \( \dot{e}_R \)]\label{prop:eR_dot_bound}
+Consider a domain \( D \) about the desired attitude defined as
+\begin{align}
+	D = \braces{R \in \SO \vert \Psi < \psi < h1, r^T R^T v < \beta < \cos \theta} \, . \label{eqn:domain}
+\end{align}
+An upper bound of \( \dot{e_R} \) is given by
+
+equation for H
+
+list the bounds on each of the terms
+
+Proof of the derivation of them
+
+Lyapunov analysis which shows that it's stable
+
+Adaptive update law and control input
 
@@
 \end{enumerate}
+\end{prop}
 Add the disturbance term and introduce adaptive update law
@@
 Positive semi definite matrix
-
-Get three polynomials (can use cubic or quartic functions to get analytical result)
-
-Define domain of consideration \( \Psi \leq \psi \) and \( r^T R^T v \leq \beta \)
 
@@
 
-Improves upon previous work by extending to the full nonlinear manifold representation and avoids quaternion ambiguities
+Improves upon previous work by extending to the full nonlinear manifold representation and avoids quaternion ambiguities/singularities
 

### 2015-09-22 ACC16.2.tex
working on \dot{e}_R bounds proof

@@
 \end{align}
-An upper bound of \( \dot{e_R} \) is given by
+Then the following statements hold:
+\begin{enumerate}[(i)]
+	\item \label{item:prop_eR_dot_bound_AB} Upper bounds of \( A(R) \) and \( B(R) \) are given by
+	\begin{gather}
+		\norm{A} < \psi \, , \label{eqn:A_bound}\\
+		\norm{B} < \psi \, . \label{eqn:B_bound}
+	\end{gather}
+	\item \label{item:prop_eR_dot_bound_EF} Upper bounds of \( E(R,R_d) \) and \( F(R) \) are given by
+	\begin{gather}
+		\norm{E} \leq \frac{1}{\sqrt{2}} \tr{G} \, , \label{eqn:E_bound} \\
+		\norm{F} \leq \frac{\beta\parenth{\beta - \cos \theta} + \beta \cos \theta}{\alpha \parenth{\beta - \cos \theta}^2} \, . \label{eqn:F_bound}
+	\end{gather}
+	\item Upper bounds of the attitude error vectors \( e_{R_A} \) and \( e_{R_B} \) are given by
+	\begin{gather}
+		\norm{e_{R_A}} \leq \sqrt{\frac{\psi}{b_1}} \, , \label{eqn:eRA_bound} \\
+		\norm{e_{R_B}} \leq \frac{\sin{\frac{\pi}{2} - \theta}}{\alpha \parenth{\beta - \cos \theta}} \, . \label{eqn:eRB_bound}
+	\end{gather}
+\end{enumerate}
+These results are combined to yield a maximum upper bound of the time derivative of the attitude error vector \( \dot{e}_R \) as
+\begin{gather}
+	\norm{\dot{e}_R} \leq H \norm{e_\Omega} \, ,\label{eqn:eR_bound}
+\end{gather}
+where  \( H \in \R \) is defined as
+\begin{gather}
+	H = \frac{\psi}{\sqrt{2}} \tr{G} + 2 \sqrt{\frac{\psi}{b_1}}\frac{\sin{\frac{\pi}{2} - \theta}}{\alpha \parenth{\beta - \cos \theta}} + \psi \frac{\beta\parenth{\beta - \cos \theta} + \beta \cos \theta}{\alpha \parenth{\beta - \cos \theta}^2} \, .
+\label{eqn:H}
+\end{gather}
+\end{prop}
 
-equation for H
+\begin{proof}[Proof of~\Cref{prop:eR_dot_bound}]\label{proof:eR_dot_bound}
+	We first show~\cref{item:prop_eR_dot_bound_AB} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
+	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
+	However, this would be in contradiction with~\cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
+	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
+	We know that \( B \to \infty \) as the constraint is neared. 
+	We assume that \( B > \psi \) which implies that \( A < 1 \).
+	As \( \psi \) is increased this means that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
+	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
+	This shows~\cref{item:prop_eR_dot_bound_AB}.
 
-list the bounds on each of the terms
+	Next, we show~\cref{item:prop_eR_dot_bound_EF} using the Frobenius norm.
 
+\end{proof}
 Proof of the derivation of them
@@
 
-\begin{enumerate}[(i)]
-	\item An upper bound of \( \norm{e_{R_B}} \) is given as:
-	\begin{align}
-		\norm{e_{R_B}} \leq \frac{\sin{\frac{\pi}{2} - \theta}}{\alpha \parenth{\beta - \cos \theta}}
-	\end{align}
-\end{enumerate}
-\end{prop}
 Add the disturbance term and introduce adaptive update law

### 2015-09-23 ACC16.2.tex
finished \dot{e_{R}} proposition and proof

@@
 	\begin{align}
-		\norm{e_{R_A}}^2 \leq \frac{\Psi}{b_1} \, ,
+		\norm{e_{R_A}}^2 \leq \frac{\Psi}{b_1} \, , \label{eqn:psi_lower_bound}
 	\end{align}
@@
 		\norm{E} \leq \frac{1}{\sqrt{2}} \tr{G} \, , \label{eqn:E_bound} \\
-		\norm{F} \leq \frac{\beta\parenth{\beta - \cos \theta} + \beta \cos \theta}{\alpha \parenth{\beta - \cos \theta}^2} \, . \label{eqn:F_bound}
+		\norm{F} \leq \frac{\parenth{\beta^2 + 1}\parenth{\beta - \cos \theta}^2 + 1 + \beta^2 \parenth{\beta^2-2}}{\alpha^2 \parenth{\beta-\cos \theta}^4} \, . \label{eqn:F_bound}
 	\end{gather}
@@
 		\norm{e_{R_A}} \leq \sqrt{\frac{\psi}{b_1}} \, , \label{eqn:eRA_bound} \\
-		\norm{e_{R_B}} \leq \frac{\sin{\frac{\pi}{2} - \theta}}{\alpha \parenth{\beta - \cos \theta}} \, . \label{eqn:eRB_bound}
+		\norm{e_{R_B}} \leq \frac{\sin\theta}{\alpha \parenth{\beta - \cos \theta}} \, . \label{eqn:eRB_bound}
 	\end{gather}
@@
 \begin{gather}
-	H = \frac{\psi}{\sqrt{2}} \tr{G} + 2 \sqrt{\frac{\psi}{b_1}}\frac{\sin{\frac{\pi}{2} - \theta}}{\alpha \parenth{\beta - \cos \theta}} + \psi \frac{\beta\parenth{\beta - \cos \theta} + \beta \cos \theta}{\alpha \parenth{\beta - \cos \theta}^2} \, .
-\label{eqn:H}
+	H = \norm{B} \norm{E} + 2 \norm{e_{R_A}} \norm{e_{R_B}} + \norm{A}\norm{F}\, . \label{eqn:H}
 \end{gather}
@@
 	Next, we show~\cref{item:prop_eR_dot_bound_EF} using the Frobenius norm.
+	The Frobenius norm \( \norm{E}_F \) is given in~\cite{lee2011a} as
+	\begin{gather*}
+		\norm{E}_F = \sqrt{\tr{E^T E}} = \frac{1}{2} \sqrt{\tr{G^2} + \tr{R^T R_d G}^2} \, .
+	\end{gather*}
+	Applying Rodrigues' formula and the Matlab symbolic toolbox this is simplified to
+	\begin{gather*}
+		\norm{E}^2_F \leq \frac{1}{4} \parenth{\tr{G^2} + \tr{G}^2} \leq \frac{1}{2} \tr{G}^2 \, ,
+	\end{gather*}
+	which shows~\cref{eqn:E_bound}, since \( \norm{E} \leq \norm{E}_F \).
 
+	To show~\cref{eqn:F_bound}, we apply the Frobenius norm \( \norm{F}_F \):
+	\begin{align*}
+		\norm{F}_F =& \sqrt{\tr{F^T F}} \\
+		=& \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} \right.\\
+		& \left.- 2 \tr{a^T b} + 2 \tr{a^T c } + \tr{b^T b} \right. \\
+		&\left. - 2 \tr{b^T c} + \tr{c^T c}\right] \, .
+	\end{align*}
+	where the terms \( a, b, \text{ and } c \) are given by
+	\begin{gather*}
+		a = r^T R r I \, ,\\
+		b = R^T v r^T \, ,\\
+		c = \frac{R^T \hat{v} R r v^T R \hat{r}}{r^T R^T v - \cos \theta}\, .
+	\end{gather*}
+	A straight forward computation of \( a^T a \) shows that
+	\begin{gather*}
+		\tr{a^T a} = \parenth{v^T R r}^2 \tr{I} \leq 3 \beta^2 \, ,
+	\end{gather*}
+	where we used the fact that \( v^T R r = r^T R^T v < \beta \) from our given domain.
+	Similarly, one can show that \( \tr{a^T b} \) is equivalent to
+	\begin{gather*}
+		\tr{a^T b} = v^T R r \tr{R^T v r^T} = \parenth{v^T R r}^2 \leq \beta^2 \, ,
+	\end{gather*} 
+	where we used the fact that \( \tr{x y^T} = x^T y \).
+	The product \( \tr{a^T c} \) is given by
+	\begin{gather*}
+		\tr{a^T c} = \frac{v^T R r}{r^T R^T v - \cos \theta} \tr{\parenth{R^T v}^\vee \parenth{r v^T R} \hat{r} } \, ,
+	\end{gather*}
+	where we used the hat map property~\cref{eqn:RxR}.
+	One can show that \(\tr{a^T c} \leq 0 \) over the range \( -1 \leq v^T R r \leq \cos \theta \). 
+	Next, \( \tr{b^T b}\) is equivalent to
+	\begin{gather*}
+		\tr{b^T b} = \tr{r v^T R R^T v r^T} = 1 \, ,
+	\end{gather*}
+	since \( r,v \in \Sph\).
+	Finally, \( \tr{c^T c} \) is reduced to
+	\begin{gather*}
+		\tr{c^T c} = \tr{\hat{r} R^T v r^T \bracket{-I + R^T v v^T R} r v^T R \hat{r}} \, ,
+	\end{gather*}
+	where we used the fact that \( \hat{x}^2 = - \norm{x}^2 I + x x^T\).
+	Expanding and collecting like terms gives
+	\begin{gather*}
+		\tr{c^T c } = \frac{1 - 2\parenth{v^T R r}^2 + \parenth{v^T R r}^4}{\parenth{r^T R^T v - \cos \theta}^2} \, . 
+	\end{gather*}
+	Using the the given domain \( r^T R^T v \leq \beta \) gives the upper bound~\cref{eqn:F_bound}.
+
+	The bound on \( e_{R_A} \) is given in~\cref{eqn:psi_lower_bound} while \( e_{R_B} \) arises from the definition of the cross product \( \norm{a \times b} = \norm{a} \norm{b} \sin \theta \).
 \end{proof}
-Proof of the derivation of them
 

### 2015-09-23 ACC16.2.tex
starting on adaptive control proof

@@
 
+\begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control]
+Given  a desired attitude command \( R_d, \Omega_d = 0 \) and positive constants \( k_R, k_\Omega, k_\Delta, c \in \R \), we define a control input \( u \in \R^3\) and an adaptive update law for \( \bar{\Delta} \) as follows:
+\begin{align}
+	u &= - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - W \bar{\Delta} \, , \label{eqn:adaptive_control} \\
+	\dot{\bar{\Delta}} &= k_\Delta W^T \parenth{e_\Omega + c e_R} \, . \label{eqn:delta_dot}
+\end{align}
+If \( c \) is sufficiently small the zero equilibrium of the error vectors \( e_R, e_\Omega\) are asymptotically stable.
+\end{prop}
+\begin{proof}[Proof of~\cref{prop:adaptive_control}]\label{proof:adaptive_control}
+	Use same domain
+
+	Lyapunov equation
+
+	Algebra
+
+	Take norm bounds
+
+	Get quadratic product
+
+	Show bound on c for negative semi-definite
+\end{proof}
 Lyapunov analysis which shows that it's stable

### 2015-09-23 ACC16.2.tex
finished proof of adaptive control

--- 2015-09-23 ACC16.2.tex
@@
 \begin{align*}
-	W = k - V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R (\frac{k}{k_R}+ \Psi(R,R_d)) \, .
+	W = k - V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \parenth{\frac{k}{k_R}+ \Psi(R,R_d)} \, .
 \end{align*}
@@
 
-Lyapunov analysis which shows that it's stable
+\begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control}
+Given  a desired attitude command \( R_d, \Omega_d = 0 \) and positive constants \( k_R, k_\Omega, k_\Delta, c \in \R \), we define a control input \( u \in \R^3\) and an adaptive update law for \( \bar{\Delta} \) as follows:
+\begin{align}
+	u &= - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - W \bar{\Delta} \, , \label{eqn:adaptive_control} \\
+	\dot{\bar{\Delta}} &= k_\Delta W^T \parenth{e_\Omega + c e_R} \, . \label{eqn:delta_dot}
+\end{align}
+If \( c \) is chosen such that
+\begin{gather}
+	0 < c < \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k-R \lambda_M H} \, , \label{eqn:c_bound}
+\end{gather}
+  the zero equilibrium of the error vectors \( e_R, e_\Omega\) are asymptotically stable.
+\end{prop}
+\begin{proof}[Proof of~\cref{prop:adaptive_control}]\label{proof:adaptive_control}
+	Consider the Lyapunov function \( V \) given by
+	\begin{gather}
+		V = \frac{1}{2} e_\Omega J e_\Omega + k_R \Psi + c J e_\Omega^T e_R + \frac{1}{2 k_\Delta} e_\Delta^T e_\Delta \, , \label{eqn:v_adapt}
+	\end{gather}
+	over the domain \( D \) in~\cref{eqn:domain}.
+	From~\cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
+	\begin{gather}
+		V \leq z^T W z \, , \label{eqn:v_upper_bound}
+	\end{gather}
+	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = \begin{bmatrix}{ccc}e_R & e_\Omega & e_\Delta\end{bmatrix} \) and the matrix \(W \in \R^{3 \times 3}\) is given by
+	\begin{gather*}
+		W = \begin{bmatrix}{ccc}
+			k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
+			\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
+			0 & 0 & \frac{1}{2 k_\Delta}
+		\end{bmatrix} \, .
+	\end{gather*}
+	The time derivative of with the control inputs~\cref{eqn:adaptive_control} is defined as
+	\begin{align}
+		\dot{V} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
+		&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} \, , \label{eqn:vdot}
+	\end{align}
+	where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
+	The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
+	\begin{align*}
+		 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 \, . 
+	\end{align*}
+	Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{V} \) is written as
+	\begin{gather*}
+		\dot{V} \leq -z^T M z \, ,
+	\end{gather*}
+	where the matrix \( M \in \R^{2 \times 2} \) is 
+	\begin{gather}
+		M = \begin{bmatrix}{cc}
+			k_R c & \frac{k_\Omega c}{2} \\
+			\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
+		\end{bmatrix} \, .
+	\end{gather}
+	If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
+	This implies that the zero equilibrium \( e_R, e_\Omega\) is asymptotically stable. 
+\end{proof}
 
-Adaptive update law and control input
+Local asymptotic stability
 
-Add the disturbance term and introduce adaptive update law
+Domain avoids undesired equilibria
 

### 2015-09-23 ACC16.2.tex
starting on simulation section

@@
 
-\begin{proof}
-	See~\Cref{proof:config_error}
+\begin{proof}[Proof of~\Cref{prop:config_error}]\label{proof:config_error}
+The proof of~\cref{item:prop_era_upbound} is available in~\cite{lee2011a}.
+To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a locally positive definite function about \( R = R_d \)~\cite{bullo2004}.
+The constraint angle is assumed \( \ang{0} \leq \theta \leq \ang{90} \) such that \( 0 \leq \cos \theta \).
+The term \( r^T R^T v \) represents the cosine of the angle between the body fixed vector \( r \) and the inertial vector \( v \). 
+It follows that
+\begin{align*}
+	0 \leq  \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta} \leq 1 \, ,
+\end{align*}
+for all \( R \in SO \). 
+As a result, the negative logarithm is always positive and
+\begin{align*}
+	1 < B \, .
+\end{align*}
+The product~\cref{eqn:psi} is composed of two positive terms and is therefore also positive definite, and has a single critical point at \( R = R_d \).
+
+Next, we consider~\cref{item:prop_era}.
+The variation of~\cref{eqn:A} is taken with respect to \( \delta R = R \hat \eta \) as
+\begin{align*}
+	\dirDiff{A}{R} &= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
+	&= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee \, ,
+\end{align*}
+where we used~\cref{eqn:hat1}.
+
+A straightforward application of the chain and product rules of differentiation allows us to show~\cref{item:prop_erb} as
+\begin{align*}
+	\dirDiff{B}{R} &= -\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta_i} \right) \right]  \\
+	&= \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} \, ,
+\end{align*}
+where the scalar triple product~\cref{eqn:STP} was used.
+
+To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
+The attitude error between \( R \) and \( R_d \) is defined as \( Q \in SO \) as
+\begin{align*}
+	Q = R_d^T R = 
+	\begin{bmatrix}
+		q_{11} & q_{12} & q_{13} \\
+		q_{21} & q_{22} & q_{23} \\
+		q_{31} & q_{32} & q_{33}
+	\end{bmatrix} \, .
+\end{align*}
+Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
+\begin{subequations}
+\begin{align}
+	g_3 q_{32} &= g_2 q_{23} \, , \\
+	g_1 q_{13} &= g_3 q_{31} \, , \\
+	g_2 q_{21} &= g_1 q_{12} \, .
+\end{align}
+\end{subequations}
+These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
+Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
+\begin{subequations}
+\begin{align}
+	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 \, , \\
+	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, , \\
+	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, .
+\end{align}
+\end{subequations}
+As a result, all the off diagonal terms of \( Q = R_d^T R \), namely \( q_{12}= q_{13} = q_{23} = 0 \).
+Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
+There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180}.
+The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
+This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \) .
+The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
 \end{proof}
@@
 
-\begin{proof}
-	See~\Cref{proof:error_dyn}
+\begin{proof}[Proof of~\Cref{prop:error_dyn}]\label{proof:error_dyn}
+From the kinematics~\cref{eqn:Rdot} and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
+\begin{gather*}
+	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega \, .
+\end{gather*}
+Applying this to the time derivative of~\cref{eqn:A} gives
+\begin{gather*}
+	\diff{}{t} A = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} \, .
+\end{gather*}
+Applying~\cref{eqn:hat1} into this shows~\cref{eqn:A_dot}.
+Next, the time derivative of the repulsive error function is given by
+\begin{gather*}
+	\diff{}{t} B = \frac{r_i^T \parenth{\hat{\Omega} R^T} v_i}{\alpha \parenth{r_i^T R^T v_i - \cos \theta}} \, .
+\end{gather*}
+Using the scalar triple product, given by~\cref{eqn:STP}, one can reduce this to~\cref{eqn:B_dot}.
+The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
+\begin{gather*}
+	\diff{}{t} e_{R_A} = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee \, .
+\end{gather*}
+Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eqn:eRA_dot,eqn:E}.
+
+We take the time derivative of the repulsive attitude error vector, \( e_{R_B} \), as
+\begin{gather*}
+	\diff{}{t} e_{R_B} = a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r \, ,
+\end{gather*}
+with \( a \in \R \) and \( b \in \R\) given by 
+\begin{gather*}
+	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} \, ,
+	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} \, .
+\end{gather*}
+Using the scalar triple product from~\cref{eqn:STP} as \( r \cdot \Omega \times \parenth{R^T v} = \parenth{R^T v} \cdot r \times \Omega \) gives~\cref{eqn:eRB_dot,eqn:F}.
+
+We show the time derivative of the configuration error function as
+\begin{gather*}
+	\diff{}{t} \Psi = \dot{A} B + A \dot{B} \, .
+\end{gather*}
+A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and appplying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
+
+The time-derivative of the angular velocity error, \( e_\Omega \), is given by
+\begin{align*}
+	\diff{}{t} e_\Omega &= \dot{\Omega} \\
+	&= J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } \, ,
+\end{align*}
+where we have used the dynamic equations of motion from~\cref{eqn:Wdot}. 
 \end{proof}
@@
 
-\begin{proof}\label{proof:att_control}
+\begin{proof}[Proof of~\Cref{prop:att_control}]\label{proof:att_control}
 	Consider the following Lyapunov function:
@@
 	\end{gather}
-	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = \begin{bmatrix}{ccc}e_R & e_\Omega & e_\Delta\end{bmatrix} \) and the matrix \(W \in \R^{3 \times 3}\) is given by
+	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = \begin{bmatrix}e_R & e_\Omega & e_\Delta\end{bmatrix} \) and the matrix \(W \in \R^{3 \times 3}\) is given by
 	\begin{gather*}
-		W = \begin{bmatrix}{ccc}
+		W = \begin{bmatrix}
 			k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
@@
 	\begin{gather}
-		M = \begin{bmatrix}{cc}
+		M = \begin{bmatrix}
 			k_R c & \frac{k_\Omega c}{2} \\
@@
 	This implies that the zero equilibrium \( e_R, e_\Omega\) is asymptotically stable. 
+	The domain \( D \) does that include the undesired equilibria and ensures that as \( e_R \to 0 \) the attitude also converges \( R \to R_d \).
 \end{proof}
-
-Local asymptotic stability
-
-Domain avoids undesired equilibria
-
-Mention how for a fixed disturbance this is integral control
-
-Go through the various developments of proving the disturbance case is stable for correct choice of gains
-
-Positive semi definite matrix
-
-Give example for a simple case
+Nonlinear adaptive controllers have been developed for attitude stabilization in terms of modified Rodriguez parameters and quaternions, as well as attitude tracking in terms of Euler angles. 
+The proposed control system is developed on \(\SO\) and avoids the singularities of Euler angles and Rodriguez parameters while incorporating state inequality constraints. 
+In addition, the unwinding and double coverage ambiguity of quaternions are also completely avoided.
 
 \section{Numerical Examples}
-Parameters used in the simulation
+We demonstrate the performance of the proposed control system via numerical simulation.
+The inertia tensor of a rigid body is given as
+\begin{gather*}
+	J = \begin{bmatrix}
+	\num{5.571e-3} & \num{6.177e-5} & \num{-2.503e-5} \\
+	\num{6.177e-5} & \num{5.571e-3} & \num{1.001e-5} \\
+	\num{-2.503e-5} & \num{1.007e-5} & \num{1.051e-2}
+	\end{bmatrix} \, .
+\end{gather*} 
+The control system parameters are chosen as
+\begin{gather*}
+	G = \text{diag} \parenth{0.9,1.1,1.0}\, , \quad k_R = 0.4 \, , \quad	k_\Omega = 0.296 \, ,\\
+	c = 1.0 \, , \quad k_\Delta = 0.5 \, , \quad \alpha = 10 \, .
+\end{gather*}
+A body fixed sensor is defined as
+\begin{gather*}
+	r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix} \, ,
+\end{gather*}
+while multiple inequality constraints are defined in~\cref{tab:constraints}.
 
-Inertia matrix of hexrotor
-
-control gains
-
-define sensor and constraint axis
-
-Define initial and desired condition
+The initial and desired states are defined using Euler angles as~\cite{shuster1993},
+\begin{gather*}
+	R(0) = I \, , \quad \Omega(0) = 0 \, ,\\
+	R_d = ROT3(\ang{90}) \, , \quad \Omega_d = 0 \, .
+\end{gather*}
 
@@
 \appendix
-\subsection{Proof of~\Cref{prop:config_error}} \label{proof:config_error}
-The proof of~\cref{item:prop_era_upbound} is available in~\cite{lee2011a}.
-To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a locally positive definite function about \( R = R_d \)~\cite{bullo2004}.
-The constraint angle is assumed \( \ang{0} \leq \theta \leq \ang{90} \) such that \( 0 \leq \cos \theta \).
-The term \( r^T R^T v \) represents the cosine of the angle between the body fixed vector \( r \) and the inertial vector \( v \). 
-It follows that
-\begin{align*}
-	0 \leq  \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta} \leq 1 \, ,
-\end{align*}
-for all \( R \in SO \). 
-As a result, the negative logarithm is always positive and
-\begin{align*}
-	1 < B \, .
-\end{align*}
-The product~\cref{eqn:psi} is composed of two positive terms and is therefore also positive definite, and has a single critical point at \( R = R_d \).
 
-Next, we consider~\cref{item:prop_era}.
-The variation of~\cref{eqn:A} is taken with respect to \( \delta R = R \hat \eta \) as
-\begin{align*}
-	\dirDiff{A}{R} &= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
-	&= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee \, ,
-\end{align*}
-where we used~\cref{eqn:hat1}.
-
-A straightforward application of the chain and product rules of differentiation allows us to show~\cref{item:prop_erb} as
-\begin{align*}
-	\dirDiff{B}{R} &= -\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta_i} \right) \right]  \\
-	&= \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} \, ,
-\end{align*}
-where the scalar triple product~\cref{eqn:STP} was used.
-
-To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
-The attitude error between \( R \) and \( R_d \) is defined as \( Q \in SO \) as
-\begin{align*}
-	Q = R_d^T R = 
-	\begin{bmatrix}
-		q_{11} & q_{12} & q_{13} \\
-		q_{21} & q_{22} & q_{23} \\
-		q_{31} & q_{32} & q_{33}
-	\end{bmatrix} \, .
-\end{align*}
-Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
-\begin{subequations}
-\begin{align}
-	g_3 q_{32} &= g_2 q_{23} \, , \\
-	g_1 q_{13} &= g_3 q_{31} \, , \\
-	g_2 q_{21} &= g_1 q_{12} \, .
-\end{align}
-\end{subequations}
-These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
-Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
-\begin{subequations}
-\begin{align}
-	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 \, , \\
-	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, , \\
-	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, .
-\end{align}
-\end{subequations}
-As a result, all the off diagonal terms of \( Q = R_d^T R \), namely \( q_{12}= q_{13} = q_{23} = 0 \).
-Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
-There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180}.
-The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
-This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \) .
-The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
-\subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
-From the kinematics~\cref{eqn:Rdot} and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
-\begin{gather*}
-	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega \, .
-\end{gather*}
-Applying this to the time derivative of~\cref{eqn:A} gives
-\begin{gather*}
-	\diff{}{t} A = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} \, .
-\end{gather*}
-Applying~\cref{eqn:hat1} into this shows~\cref{eqn:A_dot}.
-Next, the time derivative of the repulsive error function is given by
-\begin{gather*}
-	\diff{}{t} B = \frac{r_i^T \parenth{\hat{\Omega} R^T} v_i}{\alpha \parenth{r_i^T R^T v_i - \cos \theta}} \, .
-\end{gather*}
-Using the scalar triple product, given by~\cref{eqn:STP}, one can reduce this to~\cref{eqn:B_dot}.
-The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
-\begin{gather*}
-	\diff{}{t} e_{R_A} = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee \, .
-\end{gather*}
-Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eqn:eRA_dot,eqn:E}.
-
-We take the time derivative of the repulsive attitude error vector, \( e_{R_B} \), as
-\begin{gather*}
-	\diff{}{t} e_{R_B} = a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r \, ,
-\end{gather*}
-with \( a \in \R \) and \( b \in \R\) given by 
-\begin{gather*}
-	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} \, ,
-	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} \, .
-\end{gather*}
-Using the scalar triple product from~\cref{eqn:STP} as \( r \cdot \Omega \times \parenth{R^T v} = \parenth{R^T v} \cdot r \times \Omega \) gives~\cref{eqn:eRB_dot,eqn:F}.
-
-We show the time derivative of the configuration error function as
-\begin{gather*}
-	\diff{}{t} \Psi = \dot{A} B + A \dot{B} \, .
-\end{gather*}
-A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and appplying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
-
-The time-derivative of the angular velocity error, \( e_\Omega \), is given by
-\begin{align*}
-	\diff{}{t} e_\Omega &= \dot{\Omega} \\
-	&= J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } \, ,
-\end{align*}
-where we have used the dynamic equations of motion from~\cref{eqn:Wdot}. 
 \subsection{Proof of }

### 2015-09-23 ACC16.2.tex
working on simulation section

@@
 	G = \text{diag} \parenth{0.9,1.1,1.0}\, , \quad k_R = 0.4 \, , \quad	k_\Omega = 0.296 \, ,\\
-	c = 1.0 \, , \quad k_\Delta = 0.5 \, , \quad \alpha = 10 \, .
+	c = 1.0 \, , \quad k_\Delta = 0.5 \, , \quad \alpha = 15 \, .
 \end{gather*}
@@
 while multiple inequality constraints are defined in~\cref{tab:constraints}.
-
+The simulation parameters are chosen to emulate those found in~\cite{lee2011b}.
+\begin{table}[htbp]
+\begin{center}\begin{tabular}{lc}
+Constraint Vector & Angle \\ \hline \hline 
+\(\begin{bmatrix} 0.174 &-0.934 & -0.034 \end{bmatrix}\) & \ang{40} \\ \hline 
+\(\begin{bmatrix} 0 & 0.7071 & 0.7071 \end{bmatrix}\) & \ang{40} \\ \hline 
+\(\begin{bmatrix} -0.853 & 0.436 & -0.286 \end{bmatrix}\) & \ang{40} \\ \hline 
+\(\begin{bmatrix} -0.122 -0.140 -0.983 \end{bmatrix}\) & \ang{20}\end{tabular} 
+\caption{Simulation Parameters}
+\end{center}
+\label{tab:constraints}
+\end{table}
 The initial and desired states are defined using Euler angles as~\cite{shuster1993},
@@
 	R(0) = I \, , \quad \Omega(0) = 0 \, ,\\
-	R_d = ROT3(\ang{90}) \, , \quad \Omega_d = 0 \, .
+	R_d = ROT3(\ang{225}) \, , \quad \Omega_d = 0 \, .
 \end{gather*}
 
+We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}
+We assume a fixed disturbance of 
+\begin{gather*}
+	\Delta = \begin{bmatrix} 0.06 & 0.06 & 0.09 \end{bmatrix}^T \, ,
+\end{gather*}
+with the function \( W(R,\Omega) = I \).
+This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
 Present three cases

### 2015-09-24 ACC16.2.tex
added figures and simulation plots. starting on experimental section

@@
 This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
-Present three cases
+\begin{figure}
+	\includegraphics[width=\columnwidth]{cad}
+	\caption{Trajectory in inertial frame\label{fig:cad}}
+\end{figure}
+\begin{figure} 
+	\centering 
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{eR_con} 
+		\caption{Attitude error vector \(e_R\) } \label{fig:eR_con} 
+	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{eW_con} 
+		\caption{Angular velocity error} \label{fig:eW_con} 
+	\end{subfigure}
 
-Show stabilization without repulsive term (passes through constraint)
-Show stabilization with avoidance term without disturbance
-Show stabilization with disturbance and adaptive update law
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{Psi_con} 
+		\caption{Configuration error \( \Psi \)} \label{fig:Psi_con} 
+	\end{subfigure}~
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{u_con} 
+		\caption{Control input \( u\)} \label{fig:u_con} 
+	\end{subfigure} 
+	\caption{Attitude stabilization without adaptive update law}
+	\label{fig:con} 
+\end{figure}
 
-Plot of responses
+\begin{figure} 
+	\centering 
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{eR_adapt} 
+		\caption{Attitude error vector \(e_R\) } \label{fig:eR_adapt} 
+	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{eW_adapt} 
+		\caption{Angular velocity error} \label{fig:eW_adapt} 
+	\end{subfigure}
 
-Show rotation animation of spacecraft avoiding constrained regions
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{Psi_adapt} 
+		\caption{Configuration error \( \Psi \)} \label{fig:Psi_adapt} 
+	\end{subfigure}~
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{u_adapt} 
+		\caption{Control input \( u\)} \label{fig:u_adapt} 
+	\end{subfigure}
 
-\section{Experiments}
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{Delta_adapt} 
+		\caption{Disturbance estimate \( \bar{\Delta}\)} \label{fig:Delta_adapt} 
+	\end{subfigure}
+	\caption{Attitude stabilization with adaptive update law}
+	\label{fig:adapt} 
+\end{figure}
 
-Discuss experimental setup of the hexrotor on spherical joint
+Simulation results without the adaptive update law are shown in~\cref{fig:con}.
+Without the update law, the system does not achieve zero steady state error. 
+\Cref{fig:Psi_con} shows that the configuration error function does not converge to zero.
+\Cref{fig:adapt} shows the results with the addition of the adaptive update law.
+
+The path of the body fixed sensor in the inertial frame is illustrated in~\cref{fig:cad}.
+The initial attitude is represented with the green circle while the final attitude is marked with a green \(\times\).
+The control system is able to asymptotically converge to zero attitude error.
+In addition, the estimate of the disturbance converges to the the true value.
+Both control system are able to automatically avoid the constrained regions. 
+In addition, these results show that it is straightforward to incorporate an arbitrary amount of large constraints.
+In spite of this challenging configuration space the proposed control system offers a simple method of avoiding constrained regions.
+These closed-loop feedback results are computed in real time and offer a significant advantage over typical open-loop planning methods.
+These results show that the proposed geometric adaptive approach is critical to attitude stabilization in the presence of state constraints and disturbances.
+
+\section{Experiment on Hexrotor UAV}
+
+A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory(FDCL) at the George Washington University.
+The UAV is composed of three pairs of counter-rotating propellers. 
+Typical quadrotor UAVs are composed of four or more co-planar propellers.
+As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
+For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
+Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
+This allows the hexrotor to impart a force in any direction and a moment about any axis. (cite hexrotor paper)
+
+The hexrotor UAV is composed of the following parts:
+\begin{itemize}
+	\item ODROID processor 
+	\item Wifi connectivity
+	\item VectorNav IMU
+	\item Vicon motion capture sent from command computer
+\end{itemize}
 
 Describe aim of experiment. 
-Demonstrate that hexrotor fixed sensor can stabilize to desired attitude while avoiding an obstacle.
+Demonstrate that hexrotor fixed sensor can stabilize to desired attitude while avoiding an obstacle.s
 Mount a sphere at an appropriate distance such that the subtended angle is equal to the cone constraint
@@
 
-\subsection{Proof of }
-Stability proofs for case with and without disturbance
-
-Detail on finding bounds of \( \norm{\dot{e}_R} \)
-
-Lots of intermediate terms
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-09-24 ACC16.2.tex
finished sim and started experimental section. changed pdf names. run epstopdf rather than letting latex do it.

@@
 	R(0) = I \, , \quad \Omega(0) = 0 \, ,\\
-	R_d = ROT3(\ang{225}) \, , \quad \Omega_d = 0 \, .
+	R_d = \text{ROT3}(\ang{225}) \, , \quad \Omega_d = 0 \, .
 \end{gather*}
@@
 Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
-This allows the hexrotor to impart a force in any direction and a moment about any axis. (cite hexrotor paper)
+This allows the hexrotor to impart a force in any direction and a moment about any axis.
 
-The hexrotor UAV is composed of the following parts:
+The hexrotor UAV is composed of the following hardware:
 \begin{itemize}
 	\item ODROID processor 
-	\item Wifi connectivity
+	\item Wifi connectivity blurb
 	\item VectorNav IMU 
+	\item Brushless DC Motors 
 	\item Vicon motion capture sent from command computer
 \end{itemize}
+In order to constrain the motion and test only the attitude dynamics we attach the hexrotor to a spherical joint.
+The center of rotation is below the center of gravity of the hexrotor.
+As a result, there is a destabilizing gravitational moment and the resulting attitude dynamics is similar to an inverted pendulum model.
+We augment the control input in~\cref{eqn:adaptive_control} with an additional term to negate the effect of the gravitational moment.
 
-Describe aim of experiment. 
-Demonstrate that hexrotor fixed sensor can stabilize to desired attitude while avoiding an obstacle.s
-Mount a sphere at an appropriate distance such that the subtended angle is equal to the cone constraint
+A sensor is defined in the body frame of the hexrotor as \( r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix}^T \).
+We define an obstacle in the inertial frame as \( v = \begin{bmatrix} \frac{1}{\sqrt{2}} & \frac{1}{\sqrt{2}} & 0\end{bmatrix}^T \) with \( \theta = \ang{10} \).
+An inertial and desired attitude are defined in terms of Euler angles as
+\begin{gather}
+	R(0) = \text{ROT3}(\ang{90}) \, , \quad R_d = \text{ROT3}(\ang{0}) \, ,
+\end{gather}                                
+this results in the sensor performing a \ang{90} yaw rotation about the vertical axis of the spherical joint.
 
-Show plots of response with and without avoidance term
-Response should be similar to numerical simulation
+Picture of test set up
+Plots of response and trajectory
+Link to video
 
+The experimental results are shown in FIGURE.
+It shows acceptable attitude stabilization performance.
+The attitude errors asymptotically converge to zero. 
+In addition, as the constraint is neared an out-of-plane moment is used to avoid the constrained region.
+The control system is computed autonomously on-board the UAV.
+This is in constrast to many state constrained attitude control systems which require an a priori attitude trajectory to be calculated. 
 \section{Conclusions}

### 2015-09-24 ACC16.2.tex
started proofreading

@@
 Many researchers have focused on the study of the attitude dynamics of a rigid body~\cite{hughes2004,wertz1978}.
-Rigid body attitude control arises for aerospace vehicles, ground and underwater vehicles, and robotic systems.
-One distinctive feature of the attitude dynamics is that it evolves on a nonlinear manifold.
+Rigid body attitude control is an important problem for aerospace vehicles, ground and underwater vehicles, as well as robotic systems.
+One distinctive feature of the attitude dynamics of rigid bodies is that it evolves on a nonlinear manifold.
 The three-dimensional special orthogonal group is the set of \( 3 \times 3 \) orthogonal matrices whose determinant is one.
@@
 These attitude representations are not suitable for large angular slews.
-In order to avoid singularities the designer must carefully switch the chosen Euler angle sequence based on the operating region.
+In order to avoid singularities, the designer must carefully switch the chosen Euler angle sequence based on the operating region.
 Another option is to artificially limit the operating region of the rigid body.
@@
 As a result, any physical attitude is represented by a pair of antipodal quaternions on the three-sphere.
-An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternion may not hold for the physical rigid body evolving on the special orthogonal group.
+An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
 During implementation, the design must carefully resolve this non-unique representation in quaternion based attitude control system to avoid undesirable unwinding behavior~\cite{bhat2000}.

### 2015-09-24 ACC16.2.tex
finished conclusion and abstract. need to proof read and cut down to 8 pages

@@
 \begin{abstract}
-
-200-300 summary of the paper
-
-general topic area
-
-new developments/contributions of the paper
-
-relation/benefits over previous work
-
-summary of the results and contributions
-
-Awesome abstract
+We present a new geometric adaptive control system with state inequality constraints for the attitude dynamics of a rigid body.
+We globally express the attitude dynamics and control system using the special orthogonal group. 
+This representation is geometrically exact and avoids singularities and ambiguities of other attitude parameterizations, such as Euler angles and quaternions.
+Attitude constraints are incorporated and automatically considered by the control system.
+In addition, we develop an adaptive update law that enables attitude stabilization in the presence of unknown disturbances. 
+We demonstrate the effectiveness of the control system through numerical simulation and experimental results on a hexrotor UAV.
 
@@
 		h_2 &= \min{\parenth{g_1 -g_2}^2,\parenth{g_2 -g_3}^2 , \parenth{g_3 -g_1}^2} \, ,\\
-		h_3 &= \min{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} \, ,\\				
+		h_3 &= \min{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} \, .				
 	\end{align*}
@@
 \end{prop}
-
 \begin{proof}[Proof of~\Cref{prop:config_error}]\label{proof:config_error}
@@
 In this manner, one may enforce multiple state inequality constraints on the control system.
-
 \begin{prop}[Error Dynamics]\label{prop:error_dyn}
@@
 \end{prop}
-
 \begin{proof}[Proof of~\Cref{prop:error_dyn}]\label{proof:error_dyn}
@@
 \end{proof}
-
 \begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control}
@@
 \begin{figure} 
-	\includegraphics[width=\columnwidth]{cad}
-	\caption{Trajectory in inertial frame\label{fig:cad}}
-\end{figure}
-\begin{figure} 
 	\centering 
@@
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{eW_con} 
-		\caption{Angular velocity error} \label{fig:eW_con} 
+		\includegraphics[width=\columnwidth]{Psi_con} 
+		\caption{Configuration error \( \Psi \)} \label{fig:Psi_con} 
 	\end{subfigure}
@@
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{Psi_con} 
-		\caption{Configuration error \( \Psi \)} \label{fig:Psi_con} 
+		\includegraphics[width=\columnwidth]{u_con} 
+		\caption{Control input \( u\)} \label{fig:u_con} 
 	\end{subfigure}~
 	\begin{subfigure}[htbp]{0.5\columnwidth}
-		\includegraphics[width=\columnwidth]{u_con} 
-		\caption{Control input \( u\)} \label{fig:u_con} 
+		\includegraphics[width=\columnwidth]{cad}
+		\caption{Trajectory in inertial frame\label{fig:cad}}
 	\end{subfigure}
@@
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{eW_adapt} 
-		\caption{Angular velocity error} \label{fig:eW_adapt} 
+		\includegraphics[width=\columnwidth]{Psi_adapt} 
+		\caption{Configuration error \( \Psi \)} \label{fig:Psi_adapt} 
 	\end{subfigure}
@@
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{Psi_adapt} 
-		\caption{Configuration error \( \Psi \)} \label{fig:Psi_adapt} 
-	\end{subfigure}~
-	\begin{subfigure}[htbp]{0.5\columnwidth} 
 		\includegraphics[width=\columnwidth]{u_adapt} 
 		\caption{Control input \( u\)} \label{fig:u_adapt} 
-	\end{subfigure}
-
+	\end{subfigure}~	
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
@@
 \begin{itemize}
-	\item ODROID processor 
-	\item Wifi connectivity blurb
-	\item VectorNav IMU 
-	\item Brushless DC Motors 
-	\item Vicon motion capture sent from command computer
+	\item Onboard ODROID XU3 Linux processor.
+	\item VectorNav VN100 IMU operating at over \SI{100}{\hertz} via TTL serial 
+	\item Brushless DC Motors powered by BL-Ctrl-2.0 speed controllers via I2C.
+	\item Position and attitude over WiFi (TCP) communication from Vicon motion capture system via host computer.
+	\item Commands sent over WiFi through the terminal (SSH) to the code running onboard the hexrotor. 
 \end{itemize}
@@
 
-A sensor is defined in the body frame of the hexrotor as \( r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix}^T \).
-We define an obstacle in the inertial frame as \( v = \begin{bmatrix} \frac{1}{\sqrt{2}} & \frac{1}{\sqrt{2}} & 0\end{bmatrix}^T \) with \( \theta = \ang{10} \).
-An inertial and desired attitude are defined in terms of Euler angles as
+\begin{figure}
+	\includegraphics[width = \columnwidth]{hexrotor}
+	\caption{Attitude control testbed~\label{fig:hexrotor}}
+\end{figure}
+A sensor pointing direction is defined in the body frame of the hexrotor as \( r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix}^T \).
+We define an obstacle in the inertial frame as \( v = \begin{bmatrix} \frac{1}{\sqrt{2}} & \frac{1}{\sqrt{2}} & 0\end{bmatrix}^T \) with \( \theta = \ang{12} \).
+An initial and desired attitude are defined in terms of Euler angles as
 \begin{gather}
-	R(0) = \text{ROT3}(\ang{90}) \, , \quad R_d = \text{ROT3}(\ang{0}) \, ,
+	R(0) = \text{ROT3}(\ang{90}) \, , \quad R_d = \text{ROT3}(\ang{0})=I \, .
 \end{gather}                                
-this results in the sensor performing a \ang{90} yaw rotation about the vertical axis of the spherical joint.
+This results in the sensor performing a \ang{90} yaw rotation about the vertical axis of the spherical joint.
+The attitude control system is identical to the one presented in~\cref{prop:adaptive_control} except the addition of a gravity moment term and the following parameters
+\begin{gather*}
+	k_R = 0.4 \, , \quad k_\Omega = 0.7 \, , c = 0.1 \\
+	\alpha = 8 \, , k_\Delta = 0.05 \, .
+\end{gather*}
+\begin{figure} 
+	\centering 
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{eR_exp} 
+		\caption{Attitude error vector \(e_R\) } \label{fig:eR_exp} 
+	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{Psi_exp} 
+		\caption{Configuration error \( \Psi \)} \label{fig:Psi_exp} 
+	\end{subfigure}
 
-Picture of test set up
-Plots of response and trajectory
-Link to video
-
-The experimental results are shown in FIGURE.
-It shows acceptable attitude stabilization performance.
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{u_exp} 
+		\caption{Control input \( u\)} \label{fig:u_exp} 
+	\end{subfigure}~
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{traj_exp} 
+		\caption{Attitude Trajectory} \label{fig:traj_exp} 
+	\end{subfigure}
+	\caption{Constrained Attitude stabilization experiment}
+	\label{fig:exp} 
+\end{figure}
+The experimental results are shown in~\Cref{fig:exp}.
+Overall it behaves as the numerical simulations predicted.
 The attitude errors asymptotically converge to zero. 
 In addition, as the constraint is neared an out-of-plane moment is used to avoid the constrained region.
-The control system is computed autonomously on-board the UAV.
+An increased gain of the adaptive update law would improve the final steady state error performance.
+A video clip showing the attitude manuever is available LINK.
+\section{Conclusion}\label{sec:conclusion}
+We have developed a geometric adaptive control system which incorporates state inequality constraints on \SO.
+The presented control system is developed directly on \SO and avoids singularities and ambiguities that are inherent to attitude parameterizations.
+An adaptive control system is developed to asymptotically converge to a desired attitude while avoiding constraints in the presence of disturbances.
+In addition we have demonstrated the control system via numerical simulation and hardware experiments on a hexrotor UAV.
+A novel feature of this control is that it is computed autonomously on-board the UAV.
 This is in constrast to many state constrained attitude control systems which require an a priori attitude trajectory to be calculated. 
-\section{Conclusions}
-
-Discuss how this method allows for on board implementation of attitude avoidance during reorientations
-
-Improves upon previous work by extending to the full nonlinear manifold representation and avoids quaternion ambiguities/singularities
-
-Proven stable and validated via hardware experiments
+The presented method is simple, efficient and ideal for hardware implementation on embedded systems.
 

### 2015-09-24 ACC16.2.tex
first round of proof reading

@@
 An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
-During implementation, the design must carefully resolve this non-unique representation in quaternion based attitude control system to avoid undesirable unwinding behavior~\cite{bhat2000}.
-For certain initial conditions, where the rigid body starts closed to the desired attitude, the system unnecessarily rotates through a large angle even while the initial error is small.
+During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}.
+Unwinding is where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.
 
@@
 The algorithm then seeks an intermediate point such that the control scheme can be applied for each segment without violation of the constraints.
-While the geometric method is conceptually simple it is difficult to generalize for an arbitrary amount of constraints.
+While the geometric method is conceptually simple it is difficult to generalize for an arbitrary number of constraints.
 In addition, this geometric type of approach is only applicable to problems where the selection of intermediate points are computationally feasible
@@
 
-In this work, we develop a geometric adaptive controller on \SO to reorient a rigid body in the presence of state inequality constraints.
+In this work, we develop a geometric adaptive controller on \(\SO\) to reorient a rigid body in the presence of state inequality constraints.
 We apply a potential function based approach developed directly on the nonlinear manifold \SO.
@@
 In addition, we formulate an adaptive update law to enable attitude convergence in the presence of disturbances.
-These results are demonstrated via numerical examples and experimental results on a robotic aerial vehicle.
+These results are demonstrated via numerical examples and experimental results on a hexrotor aerial vehicle.
 \section{Problem Formulation}\label{sec:prob_form}
@@
 Consider the attitude dynamics of a rigid body. 
-Define an inertial reference frame and a body-fixed frame. 
+We define an inertial reference frame and a body-fixed frame fixed to the center of mass. 
 The configuration manifold of the attitude dynamics is the special orthogonal group:
@@
 \end{gather}
-where $J\in\Re^{3\times 3}$ is the inertia matrix, and $\Omega\in\Re^3$ is the angular velocity represented with respect to the body-fixed frame. 
-The control moment is denoted by $u\in\Re^3$, and it is expressed with respect to the body-fixed frame. 
-We assume that the external disturbance is expressed by $W(R,\Omega)\Delta$, where $W(R,\Omega):\SO\times\Re^3\rightarrow \Re^{3\times p}$ is a known function of the attitude and the angular velocity, and $\Delta\in\Re^p$ is an unknown, but fixed uncertain parameter.
+where $J\in\R^{3\times 3}$ is the inertia matrix, and $\Omega\in\R^{3\times1}$ is the angular velocity represented with respect to the body-fixed frame. 
+The control moment is denoted by $u\in\R^{3\times1}$, and it is expressed with respect to the body-fixed frame. 
+We assume that the external disturbance is expressed by $W(R,\Omega)\Delta$, where $W(R,\Omega):\SO\times\R^{3\times1}\rightarrow \R^{3\times p}$ is a known function of the attitude and the angular velocity.
+The disturbance is represented by $\Delta\in\R^{p\times1}$ is an unknown, but fixed uncertain parameter.
 In addition, we assume that a bound on \( W(R, \Omega) \) is known and given by
@@
 
-In~\refeqn{Rdot}, the \textit{hat} map $\wedge :\Re^{3}\rightarrow\so$ represents the transformation of a vector in $\Re^3$ to a $3\times 3$ skew-symmetric matrix such that $\hat x y = x\times y$ for any $x,y\in\Re^3$~\cite{BulLew05}.
+In~\refeqn{Rdot}, the \textit{hat} map $\wedge :\R^{3\times1}\rightarrow\so$ represents the transformation of a vector in $\R^{3\times1}$ to a $3\times 3$ skew-symmetric matrix such that $\hat x y = x\times y$ for any $x,y\in\R^{3\times1}$~\cite{bullo2004}.
 More explicitly, 
@@
 \end{align*}
-for $x=[x_1,x_2,x_3]^T\in\Re^3$. 
-The inverse of the hat map is denoted by the \textit{vee} map $\vee:\so\rightarrow\Re^3$. Several properties of the hat map are summarized as
+for $x=[x_1,x_2,x_3]^T\in\R^{3\times1}$. 
+The inverse of the hat map is denoted by the \textit{vee} map $\vee:\so\rightarrow\R^{3\times1}$. 
+Several properties of the hat map are summarized as
 \begin{gather}
@@
 \end{gather}
-for any $x,y,z\in\Re^3$, $A\in\Re^{3\times 3}$ and $R\in\SO$. 
-Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\Re^n$ and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively.
+for any $x,y,z\in\R^{3\times1}$, $A\in\R^{3\times 3}$ and $R\in\SO$. 
+Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\R^n$ and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively.
 The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A}_F = \tr{A^T A} \).
@@
 We define \( r \in \Sph^2 \) to be a unit vector from the mass center of the rigid body and represented with respect to the body-fixed frame.
-For example, \( r \) may represent the pointing direction of an on board optical sensor.
+For example, \( r \) may represent the pointing direction of an on-board optical sensor.
 We define \( v \in \Sph^2 \) to be a unit vector from the mass center of the rigid body towards an undesired pointing direction and represented in the inertial reference frame.
-For example, \( v \) may represent the inertial direction of a bright celestial object or the incoming direction of particles or other debris
+For example, \( v \) may represent the inertial direction of a bright celestial object or the incoming direction of particles or other debris.
 It is further assumed that optical sensor has a strict non-exposure constraint with respect to the celestial object.
@@
 Once an appropriate configuration error function is chosen, one can then define a configuration error vector and a velocity error vector in the tangent space \( \mathsf{T}_q \Q \) through use of the derivatives of \( \Psi \)~\cite{bullo2004}.
-With the configuration error function and vectors the remaining procedure is similar to nonlinear control design on Euclidean vector spaces.
+With the configuration error function and vectors the remaining procedure is analogous to nonlinear control design on Euclidean vector spaces.
 One chooses control inputs as functions of the state through a Lyapunov analysis on \Q.
@@
 A new configuration error function is proposed for attitude control in the presence of state inequality constraints.
-We extend the form used in~~\cite{bullo2004,lee2011a} for attitude control on \SO with the addition of a logarithmic barrier function.
+We extend the form used in~\cite{bullo2004,lee2011a} for attitude control on \SO with the addition of a logarithmic barrier function.
 We use the configuration error function to develop a nonlinear geometric attitude controller for the stabilization of a general rigid body. 
@@
 \begin{prop}[Attitude Error Function] \label{prop:config_error}
-We assume a desired attitude command \( ( R_d, \Omega_d = 0 ) \), the current attitude and angular velocity \( ( R, \Omega) \), and a state constraint~\refeq{eqn:constraint} are given.
+We assume a desired attitude command \( ( R_d, \Omega_d = 0 ) \), the current attitude and angular velocity \( ( R, \Omega) \), and a state constraint~\cref{eqn:constraint} are given.
 We define an attitude error function \( \Psi : \SO \times \SO \to \R \), and attitude error vector \( e_R : \SO \times \SO \to \R \), and an angular velocity error vector \( e_\Omega : \R^3 \to \R^3 \) as follows:
@@
 	\begin{align}
-		\dirDiff{B_i}{R} &= \eta \cdot e_{R_{B_i}} \, .
+		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}} \, .
 	\end{align}
@@
 \end{align*}
-for all \( R \in SO \). 
+for all \( R \in \SO \). 
 As a result, the negative logarithm is always positive and
@@
 \begin{align*}
-	\dirDiff{B}{R} &= -\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta_i} \right) \right]  \\
+	\dirDiff{B}{R} &= -\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta} \right) \right]  \\
 	&= \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} \, ,
@@
 To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
-The attitude error between \( R \) and \( R_d \) is defined as \( Q \in SO \) as
+The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
 \begin{align*}
@@
 \end{subequations}
-As a result, all the off diagonal terms of \( Q = R_d^T R \), namely \( q_{12}= q_{13} = q_{23} = 0 \).
+As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
 Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
@@
 \begin{gather*}
-	\diff{}{t} A = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} \, .
+	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} \, .
 \end{gather*}
@@
 \begin{gather*}
-	\diff{}{t} B = \frac{r_i^T \parenth{\hat{\Omega} R^T} v_i}{\alpha \parenth{r_i^T R^T v_i - \cos \theta}} \, .
+	\diff{}{t} (B) = \frac{r_i^T \parenth{\hat{\Omega} R^T} v_i}{\alpha \parenth{r_i^T R^T v_i - \cos \theta}} \, .
 \end{gather*}
@@
 \begin{gather*}
-	\diff{}{t} e_{R_A} = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee \, .
+	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee \, .
 \end{gather*}
@@
 \begin{gather*}
-	\diff{}{t} e_{R_B} = a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r \, ,
+	\diff{}{t}( e_{R_B} )= a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r \, ,
 \end{gather*}
@@
 \begin{gather*}
-	\diff{}{t} \Psi = \dot{A} B + A \dot{B} \, .
+	\diff{}{t} (\Psi) = \dot{A} B + A \dot{B} \, .
 \end{gather*}
@@
 There are three additional critical points of \( \Psi \) where \( e_R = 0 \).
-At an undesired equilibrium \( R = \exp{\pi \hat{e}_i} R_d \) and \( e_\Omega =0 \). 
+At an undesired equilibrium \( R = \exp{ \parenth{\pi \hat{e}_i}} R_d \) and \( e_\Omega =0 \). 
 This results in \( A \) having a value of \( g_1 + g_2, g_2 + g_3 \) or \( g_3 + g_1 \).
@@
 \end{align*}
-We can choose an attitude \( R \) arbitrarily close to the equilibrium point \( \exp{ \pi \hat{e}_i} R_d \) such that the \( k_r \parenth{\frac{k}{k_R}+\Psi }> 0 \).
+We can choose an attitude \( R \) arbitrarily close to the equilibrium point \( \exp{ \parenth{\pi \hat{e}_i}} R_d \) such that the \( k_R \parenth{\frac{k}{k_R}+\Psi }> 0 \).
 This is due to the fact that \( \Psi \) is positive definite about \( R = R_d \) as shown in~\cref{item:prop_psi_psd}.
@@
 \begin{proof}[Proof of~\Cref{prop:eR_dot_bound}]\label{proof:eR_dot_bound}
-	We first show~\cref{item:prop_eR_dot_bound_AB} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
+	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
 	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
@@
 	We assume that \( B > \psi \) which implies that \( A < 1 \).
-	As \( \psi \) is increased this means that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
+	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
 	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
-	This shows~\cref{item:prop_eR_dot_bound_AB}.
+	This shows~\cref{eqn:A_bound,eqn:B_bound}.
 
-	Next, we show~\cref{item:prop_eR_dot_bound_EF} using the Frobenius norm.
+	Next, we show~~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
 	The Frobenius norm \( \norm{E}_F \) is given in~\cite{lee2011a} as
@@
 	\end{gather*}
-	Applying Rodrigues' formula and the Matlab symbolic toolbox this is simplified to
+	Applying Rodrigues' formula and the Matlab symbolic toolbox, this is simplified to
 	\begin{gather*}
@@
 	\end{gather*}
-	A straight forward computation of \( a^T a \) shows that
+	A straightforward computation of \( a^T a \) shows that
 	\begin{gather*}
@@
 	\end{gather*}
-	since \( r,v \in \Sph\).
+	since \( r,v \in \Sph^2\).
 	Finally, \( \tr{c^T c} \) is reduced to
@@
 \begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control}
-Given  a desired attitude command \( R_d, \Omega_d = 0 \) and positive constants \( k_R, k_\Omega, k_\Delta, c \in \R \), we define a control input \( u \in \R^3\) and an adaptive update law for \( \bar{\Delta} \) as follows:
+Given  a desired attitude command \( (R_d, \Omega_d = 0 )\) and positive constants \( k_R, k_\Omega, k_\Delta, c \in \R \), we define a control input \( u \in \R^3\) and an adaptive update law for \( \bar{\Delta} \) as follows:
 \begin{align}
@@
 	over the domain \( D \) in~\cref{eqn:domain}.
-	From~\cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
+	From~\Cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
 	\begin{gather}
@@
 	\end{gather*}
-	The time derivative of with the control inputs~\cref{eqn:adaptive_control} is defined as
+	The time derivative of \( V\) with the control inputs~\cref{eqn:adaptive_control} is defined as
 	\begin{align}
@@
 \end{proof}
+
 Nonlinear adaptive controllers have been developed for attitude stabilization in terms of modified Rodriguez parameters and quaternions, as well as attitude tracking in terms of Euler angles. 
@@
 	J = \begin{bmatrix}
-	\num{5.571e-3} & \num{6.177e-5} & \num{-2.503e-5} \\
-	\num{6.177e-5} & \num{5.571e-3} & \num{1.001e-5} \\
-	\num{-2.503e-5} & \num{1.007e-5} & \num{1.051e-2}
-	\end{bmatrix} \, .
+	\num{5.57e-3} & \num{6.17e-5} & \num{-2.50e-5} \\
+	\num{6.17e-5} & \num{5.57e-3} & \num{1.00e-5} \\
+	\num{-2.50e-5} & \num{1.00e-5} & \num{1.05e-2}
+	\end{bmatrix} \si{\kilo\gram\meter\squared} \, .
 \end{gather*} 
@@
 \end{gather*}
-while multiple inequality constraints are defined in~\cref{tab:constraints}.
+while multiple inequality constraints are defined in~\Cref{tab:constraints}.
 The simulation parameters are chosen to emulate those found in~\cite{lee2011b}.
@@
 \(\begin{bmatrix} -0.122 -0.140 -0.983 \end{bmatrix}\) & \ang{20}\end{tabular} 
-\caption{Simulation Parameters}
+\caption{Simulation Parameters~\label{tab:constraints}}
 \end{center}
-\label{tab:constraints}
 \end{table}
+
 The initial and desired states are defined using Euler angles as~\cite{shuster1993},
 \begin{gather*}
-	R(0) = I \, , \quad \Omega(0) = 0 \, ,\\
-	R_d = \text{ROT3}(\ang{225}) \, , \quad \Omega_d = 0 \, .
+	R_0 = \text{ROT3}(\ang{225}) \, , \quad \Omega_0 = 0 \, ,\\
+	R_d = I \, , \quad \Omega_d = 0 \, .
 \end{gather*}
 
-We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}
+We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}.
 We assume a fixed disturbance of 
@@
 This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
+The first term of~\cref{eqn:delta_dot} has the effect of increasing the proportional gain of the control system, since the time derivative of the attitude error vector, \( \dot{e_{R}} \), is linear with respect to the angular velocity error vector \( e_\Omega\).
 \begin{figure} 
@@
 
-Simulation results without the adaptive update law are shown in~\cref{fig:con}.
+Simulation results without the adaptive update law are shown in~\cref{fig:con,fig:adapt}, respectively.
 Without the update law, the system does not achieve zero steady state error. 
@@
 \Cref{fig:adapt} shows the results with the addition of the adaptive update law.
-
+The addition of the adaptive update law allows the system to converge to the desired attitude in the presence of constraints.
 The path of the body fixed sensor in the inertial frame is illustrated in~\cref{fig:cad}.
@@
 The center of rotation is below the center of gravity of the hexrotor.
-As a result, there is a destabilizing gravitational moment and the resulting attitude dynamics is similar to an inverted pendulum model.
+As a result, there is a destabilizing gravitational moment and the resulting attitude dynamics are similar to an inverted pendulum model.
 We augment the control input in~\cref{eqn:adaptive_control} with an additional term to negate the effect of the gravitational moment.
@@
 This results in the sensor performing a \ang{90} yaw rotation about the vertical axis of the spherical joint.
-The attitude control system is identical to the one presented in~\cref{prop:adaptive_control} except the addition of a gravity moment term and the following parameters
+The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term and the following parameters
 \begin{gather*}
@@
 The experimental results are shown in~\Cref{fig:exp}.
-Overall it behaves as the numerical simulations predicted.
+Overall, it behaves as the numerical simulations predicted.
 The attitude errors asymptotically converge to zero. 
@@
 An increased gain of the adaptive update law would improve the final steady state error performance.
-A video clip showing the attitude manuever is available LINK.
+A video clip showing the attitude manuever is available \url{https://youtu.be/IQLgNXfv_WA}.
 \section{Conclusion}\label{sec:conclusion}

### 2015-09-25 ACC16.2.tex
moved proofs to appendix

@@
 \end{prop}
-\begin{proof}[Proof of~\Cref{prop:config_error}]\label{proof:config_error}
-The proof of~\cref{item:prop_era_upbound} is available in~\cite{lee2011a}.
-To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a locally positive definite function about \( R = R_d \)~\cite{bullo2004}.
-The constraint angle is assumed \( \ang{0} \leq \theta \leq \ang{90} \) such that \( 0 \leq \cos \theta \).
-The term \( r^T R^T v \) represents the cosine of the angle between the body fixed vector \( r \) and the inertial vector \( v \). 
-It follows that
-\begin{align*}
-	0 \leq  \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta} \leq 1 \, ,
-\end{align*}
-for all \( R \in \SO \). 
-As a result, the negative logarithm is always positive and
-\begin{align*}
-	1 < B \, .
-\end{align*}
-The product~\cref{eqn:psi} is composed of two positive terms and is therefore also positive definite, and has a single critical point at \( R = R_d \).
-
-Next, we consider~\cref{item:prop_era}.
-The variation of~\cref{eqn:A} is taken with respect to \( \delta R = R \hat \eta \) as
-\begin{align*}
-	\dirDiff{A}{R} &= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
-	&= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee \, ,
-\end{align*}
-where we used~\cref{eqn:hat1}.
-
-A straightforward application of the chain and product rules of differentiation allows us to show~\cref{item:prop_erb} as
-\begin{align*}
-	\dirDiff{B}{R} &= -\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta} \right) \right]  \\
-	&= \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} \, ,
-\end{align*}
-where the scalar triple product~\cref{eqn:STP} was used.
-
-To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
-The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
-\begin{align*}
-	Q = R_d^T R = 
-	\begin{bmatrix}
-		q_{11} & q_{12} & q_{13} \\
-		q_{21} & q_{22} & q_{23} \\
-		q_{31} & q_{32} & q_{33}
-	\end{bmatrix} \, .
-\end{align*}
-Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
-\begin{subequations}
-\begin{align}
-	g_3 q_{32} &= g_2 q_{23} \, , \\
-	g_1 q_{13} &= g_3 q_{31} \, , \\
-	g_2 q_{21} &= g_1 q_{12} \, .
-\end{align}
-\end{subequations}
-These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
-Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
-\begin{subequations}
-\begin{align}
-	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 \, , \\
-	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, , \\
-	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, .
-\end{align}
-\end{subequations}
-As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
-Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
-There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180}.
-The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
-This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \) .
-The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
+\begin{proof}
+See~\Cref{proof:config_error}
 \end{proof}
@@
 \end{prop}
-\begin{proof}[Proof of~\Cref{prop:error_dyn}]\label{proof:error_dyn}
-From the kinematics~\cref{eqn:Rdot} and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
-\begin{gather*}
-	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega \, .
-\end{gather*}
-Applying this to the time derivative of~\cref{eqn:A} gives
-\begin{gather*}
-	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} \, .
-\end{gather*}
-Applying~\cref{eqn:hat1} into this shows~\cref{eqn:A_dot}.
-Next, the time derivative of the repulsive error function is given by
-\begin{gather*}
-	\diff{}{t} (B) = \frac{r_i^T \parenth{\hat{\Omega} R^T} v_i}{\alpha \parenth{r_i^T R^T v_i - \cos \theta}} \, .
-\end{gather*}
-Using the scalar triple product, given by~\cref{eqn:STP}, one can reduce this to~\cref{eqn:B_dot}.
-The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
-\begin{gather*}
-	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee \, .
-\end{gather*}
-Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eqn:eRA_dot,eqn:E}.
-
-We take the time derivative of the repulsive attitude error vector, \( e_{R_B} \), as
-\begin{gather*}
-	\diff{}{t}( e_{R_B} )= a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r \, ,
-\end{gather*}
-with \( a \in \R \) and \( b \in \R\) given by 
-\begin{gather*}
-	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} \, ,
-	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} \, .
-\end{gather*}
-Using the scalar triple product from~\cref{eqn:STP} as \( r \cdot \Omega \times \parenth{R^T v} = \parenth{R^T v} \cdot r \times \Omega \) gives~\cref{eqn:eRB_dot,eqn:F}.
-
-We show the time derivative of the configuration error function as
-\begin{gather*}
-	\diff{}{t} (\Psi) = \dot{A} B + A \dot{B} \, .
-\end{gather*}
-A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and appplying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
-
-The time-derivative of the angular velocity error, \( e_\Omega \), is given by
-\begin{align*}
-	\diff{}{t} e_\Omega &= \dot{\Omega} \\
-	&= J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } \, ,
-\end{align*}
-where we have used the dynamic equations of motion from~\cref{eqn:Wdot}. 
+\begin{proof}
+See~\Cref{proof:error_dyn}
 \end{proof}
@@
 
-\begin{proof}[Proof of~\Cref{prop:att_control}]\label{proof:att_control}
-	Consider the following Lyapunov function:
-	\begin{gather}
-		V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d) \, . \label{eqn:v_nodist}
-	\end{gather}
-	From~\cref{item:prop_psi_psd}, we obtain
-	\begin{gather*}
-		V \geq 0 \, .
-	\end{gather*}
-	Using~\cref{eqn:eW_dot,eqn:psi_dot} with \( \Delta = 0 \), the time derivative of \( V \) is given by
-	\begin{align}
-		\dot{V} &= e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
-		&= -k_\Omega \norm{e_\Omega}^2 \, . \label{eqn:vdot_nodist}
-	\end{align}
-	Since \( V \) is positive definite and \( \dot{V} \) is negative definite this implies that the zero equilibrium point \( e_R, e_\Omega \) is asymptotically stable.
+\begin{proof}
+See~\Cref{proof:att_control}
 \end{proof}
@@
 
-\begin{proof}[Proof of~\Cref{prop:eR_dot_bound}]\label{proof:eR_dot_bound}
-	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
-	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
-	However, this would be in contradiction with~\cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
-	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
-	We know that \( B \to \infty \) as the constraint is neared. 
-	We assume that \( B > \psi \) which implies that \( A < 1 \).
-	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
-	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
-	This shows~\cref{eqn:A_bound,eqn:B_bound}.
-
-	Next, we show~~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
-	The Frobenius norm \( \norm{E}_F \) is given in~\cite{lee2011a} as
-	\begin{gather*}
-		\norm{E}_F = \sqrt{\tr{E^T E}} = \frac{1}{2} \sqrt{\tr{G^2} + \tr{R^T R_d G}^2} \, .
-	\end{gather*}
-	Applying Rodrigues' formula and the Matlab symbolic toolbox, this is simplified to
-	\begin{gather*}
-		\norm{E}^2_F \leq \frac{1}{4} \parenth{\tr{G^2} + \tr{G}^2} \leq \frac{1}{2} \tr{G}^2 \, ,
-	\end{gather*}
-	which shows~\cref{eqn:E_bound}, since \( \norm{E} \leq \norm{E}_F \).
-
-	To show~\cref{eqn:F_bound}, we apply the Frobenius norm \( \norm{F}_F \):
-	\begin{align*}
-		\norm{F}_F =& \sqrt{\tr{F^T F}} \\
-		=& \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} \right.\\
-		& \left.- 2 \tr{a^T b} + 2 \tr{a^T c } + \tr{b^T b} \right. \\
-		&\left. - 2 \tr{b^T c} + \tr{c^T c}\right] \, .
-	\end{align*}
-	where the terms \( a, b, \text{ and } c \) are given by
-	\begin{gather*}
-		a = r^T R r I \, ,\\
-		b = R^T v r^T \, ,\\
-		c = \frac{R^T \hat{v} R r v^T R \hat{r}}{r^T R^T v - \cos \theta}\, .
-	\end{gather*}
-	A straightforward computation of \( a^T a \) shows that
-	\begin{gather*}
-		\tr{a^T a} = \parenth{v^T R r}^2 \tr{I} \leq 3 \beta^2 \, ,
-	\end{gather*}
-	where we used the fact that \( v^T R r = r^T R^T v < \beta \) from our given domain.
-	Similarly, one can show that \( \tr{a^T b} \) is equivalent to
-	\begin{gather*}
-		\tr{a^T b} = v^T R r \tr{R^T v r^T} = \parenth{v^T R r}^2 \leq \beta^2 \, ,
-	\end{gather*} 
-	where we used the fact that \( \tr{x y^T} = x^T y \).
-	The product \( \tr{a^T c} \) is given by
-	\begin{gather*}
-		\tr{a^T c} = \frac{v^T R r}{r^T R^T v - \cos \theta} \tr{\parenth{R^T v}^\vee \parenth{r v^T R} \hat{r} } \, ,
-	\end{gather*}
-	where we used the hat map property~\cref{eqn:RxR}.
-	One can show that \(\tr{a^T c} \leq 0 \) over the range \( -1 \leq v^T R r \leq \cos \theta \). 
-	Next, \( \tr{b^T b}\) is equivalent to
-	\begin{gather*}
-		\tr{b^T b} = \tr{r v^T R R^T v r^T} = 1 \, ,
-	\end{gather*}
-	since \( r,v \in \Sph^2\).
-	Finally, \( \tr{c^T c} \) is reduced to
-	\begin{gather*}
-		\tr{c^T c} = \tr{\hat{r} R^T v r^T \bracket{-I + R^T v v^T R} r v^T R \hat{r}} \, ,
-	\end{gather*}
-	where we used the fact that \( \hat{x}^2 = - \norm{x}^2 I + x x^T\).
-	Expanding and collecting like terms gives
-	\begin{gather*}
-		\tr{c^T c } = \frac{1 - 2\parenth{v^T R r}^2 + \parenth{v^T R r}^4}{\parenth{r^T R^T v - \cos \theta}^2} \, . 
-	\end{gather*}
-	Using the the given domain \( r^T R^T v \leq \beta \) gives the upper bound~\cref{eqn:F_bound}.
-
-	The bound on \( e_{R_A} \) is given in~\cref{eqn:psi_lower_bound} while \( e_{R_B} \) arises from the definition of the cross product \( \norm{a \times b} = \norm{a} \norm{b} \sin \theta \).
+\begin{proof}
+See~\Cref{proof:eR_dot_bound}
 \end{proof}
@@
 \end{prop}
-\begin{proof}[Proof of~\cref{prop:adaptive_control}]\label{proof:adaptive_control}
-	Consider the Lyapunov function \( V \) given by
-	\begin{gather}
-		V = \frac{1}{2} e_\Omega J e_\Omega + k_R \Psi + c J e_\Omega^T e_R + \frac{1}{2 k_\Delta} e_\Delta^T e_\Delta \, , \label{eqn:v_adapt}
-	\end{gather}
-	over the domain \( D \) in~\cref{eqn:domain}.
-	From~\Cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
-	\begin{gather}
-		V \leq z^T W z \, , \label{eqn:v_upper_bound}
-	\end{gather}
-	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = \begin{bmatrix}e_R & e_\Omega & e_\Delta\end{bmatrix} \) and the matrix \(W \in \R^{3 \times 3}\) is given by
-	\begin{gather*}
-		W = \begin{bmatrix}
-			k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
-			\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
-			0 & 0 & \frac{1}{2 k_\Delta}
-		\end{bmatrix} \, .
-	\end{gather*}
-	The time derivative of \( V\) with the control inputs~\cref{eqn:adaptive_control} is defined as
-	\begin{align}
-		\dot{V} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
-		&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} \, , \label{eqn:vdot}
-	\end{align}
-	where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
-	The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
-	\begin{align*}
-		 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 \, . 
-	\end{align*}
-	Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{V} \) is written as
-	\begin{gather*}
-		\dot{V} \leq -z^T M z \, ,
-	\end{gather*}
-	where the matrix \( M \in \R^{2 \times 2} \) is 
-	\begin{gather}
-		M = \begin{bmatrix}
-			k_R c & \frac{k_\Omega c}{2} \\
-			\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
-		\end{bmatrix} \, .
-	\end{gather}
-	If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
-	This implies that the zero equilibrium \( e_R, e_\Omega\) is asymptotically stable. 
-	The domain \( D \) does that include the undesired equilibria and ensures that as \( e_R \to 0 \) the attitude also converges \( R \to R_d \).
+\begin{proof}
+See~\Cref{proof:adaptive_control}
 \end{proof}
@@
 \begin{table}[htbp]
+\caption{Simulation Parameters~\label{tab:constraints}}
 \begin{center}\begin{tabular}{lc}
@@
 \(\begin{bmatrix} -0.122 -0.140 -0.983 \end{bmatrix}\) & \ang{20}\end{tabular} 
-\caption{Simulation Parameters~\label{tab:constraints}}
 \end{center}
@@
 \appendix
+\subsection{Proof of~\Cref{prop:config_error}}\label{proof:config_error}
+The proof of~\cref{item:prop_era_upbound} is available in~\cite{lee2011a}.
+To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a locally positive definite function about \( R = R_d \)~\cite{bullo2004}.
+The constraint angle is assumed \( \ang{0} \leq \theta \leq \ang{90} \) such that \( 0 \leq \cos \theta \).
+The term \( r^T R^T v \) represents the cosine of the angle between the body fixed vector \( r \) and the inertial vector \( v \). 
+It follows that
+\begin{align*}
+	0 \leq  \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta} \leq 1 \, ,
+\end{align*}
+for all \( R \in \SO \). 
+As a result, the negative logarithm is always positive and
+\begin{align*}
+	1 < B \, .
+\end{align*}
+The product~\cref{eqn:psi} is composed of two positive terms and is therefore also positive definite, and has a single critical point at \( R = R_d \).
+
+Next, we consider~\cref{item:prop_era}.
+The variation of~\cref{eqn:A} is taken with respect to \( \delta R = R \hat \eta \) as
+\begin{align*}
+	\dirDiff{A}{R} &= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
+	&= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee \, ,
+\end{align*}
+where we used~\cref{eqn:hat1}.
+
+A straightforward application of the chain and product rules of differentiation allows us to show~\cref{item:prop_erb} as
+\begin{align*}
+	\dirDiff{B}{R} &= -\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta} \right) \right]  \\
+	&= \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} \, ,
+\end{align*}
+where the scalar triple product~\cref{eqn:STP} was used.
+
+To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
+The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
+\begin{align*}
+	Q = R_d^T R = 
+	\begin{bmatrix}
+		q_{11} & q_{12} & q_{13} \\
+		q_{21} & q_{22} & q_{23} \\
+		q_{31} & q_{32} & q_{33}
+	\end{bmatrix} \, .
+\end{align*}
+Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
+\begin{subequations}
+\begin{align}
+	g_3 q_{32} &= g_2 q_{23} \, , \\
+	g_1 q_{13} &= g_3 q_{31} \, , \\
+	g_2 q_{21} &= g_1 q_{12} \, .
+\end{align}
+\end{subequations}
+These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
+Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
+\begin{subequations}
+\begin{align}
+	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 \, , \\
+	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, , \\
+	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, .
+\end{align}
+\end{subequations}
+As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
+Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
+There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180}.
+The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
+This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \) .
+The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
+
+\subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
+From the kinematics~\cref{eqn:Rdot} and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
+\begin{gather*}
+	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega \, .
+\end{gather*}
+Applying this to the time derivative of~\cref{eqn:A} gives
+\begin{gather*}
+	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} \, .
+\end{gather*}
+Applying~\cref{eqn:hat1} into this shows~\cref{eqn:A_dot}.
+Next, the time derivative of the repulsive error function is given by
+\begin{gather*}
+	\diff{}{t} (B) = \frac{r_i^T \parenth{\hat{\Omega} R^T} v_i}{\alpha \parenth{r_i^T R^T v_i - \cos \theta}} \, .
+\end{gather*}
+Using the scalar triple product, given by~\cref{eqn:STP}, one can reduce this to~\cref{eqn:B_dot}.
+The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
+\begin{gather*}
+	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee \, .
+\end{gather*}
+Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eqn:eRA_dot,eqn:E}.
+
+We take the time derivative of the repulsive attitude error vector, \( e_{R_B} \), as
+\begin{gather*}
+	\diff{}{t}( e_{R_B} )= a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r \, ,
+\end{gather*}
+with \( a \in \R \) and \( b \in \R\) given by 
+\begin{gather*}
+	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} \, ,
+	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} \, .
+\end{gather*}
+Using the scalar triple product from~\cref{eqn:STP} as \( r \cdot \Omega \times \parenth{R^T v} = \parenth{R^T v} \cdot r \times \Omega \) gives~\cref{eqn:eRB_dot,eqn:F}.
+
+We show the time derivative of the configuration error function as
+\begin{gather*}
+	\diff{}{t} (\Psi) = \dot{A} B + A \dot{B} \, .
+\end{gather*}
+A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and appplying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
+
+The time-derivative of the angular velocity error, \( e_\Omega \), is given by
+\begin{align*}
+	\diff{}{t} e_\Omega &= \dot{\Omega} \\
+	&= J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } \, ,
+\end{align*}
+where we have used the dynamic equations of motion from~\cref{eqn:Wdot}. 
+\subsection{Proof of~\Cref{prop:att_control}}\label{proof:att_control}
+	Consider the following Lyapunov function:
+	\begin{gather}
+		V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d) \, . \label{eqn:v_nodist}
+	\end{gather}
+	From~\cref{item:prop_psi_psd}, we obtain
+	\begin{gather*}
+		V \geq 0 \, .
+	\end{gather*}
+	Using~\cref{eqn:eW_dot,eqn:psi_dot} with \( \Delta = 0 \), the time derivative of \( V \) is given by
+	\begin{align}
+		\dot{V} &= e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
+		&= -k_\Omega \norm{e_\Omega}^2 \, . \label{eqn:vdot_nodist}
+	\end{align}
+	Since \( V \) is positive definite and \( \dot{V} \) is negative definite this implies that the zero equilibrium point \( e_R, e_\Omega \) is asymptotically stable.
+
+\subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
+	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
+	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
+	However, this would be in contradiction with~\cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
+	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
+	We know that \( B \to \infty \) as the constraint is neared. 
+	We assume that \( B > \psi \) which implies that \( A < 1 \).
+	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
+	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
+	This shows~\cref{eqn:A_bound,eqn:B_bound}.
+
+	Next, we show~~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
+	The Frobenius norm \( \norm{E}_F \) is given in~\cite{lee2011a} as
+	\begin{gather*}
+		\norm{E}_F = \sqrt{\tr{E^T E}} = \frac{1}{2} \sqrt{\tr{G^2} + \tr{R^T R_d G}^2} \, .
+	\end{gather*}
+	Applying Rodrigues' formula and the Matlab symbolic toolbox, this is simplified to
+	\begin{gather*}
+		\norm{E}^2_F \leq \frac{1}{4} \parenth{\tr{G^2} + \tr{G}^2} \leq \frac{1}{2} \tr{G}^2 \, ,
+	\end{gather*}
+	which shows~\cref{eqn:E_bound}, since \( \norm{E} \leq \norm{E}_F \).
+
+	To show~\cref{eqn:F_bound}, we apply the Frobenius norm \( \norm{F}_F \):
+	\begin{align*}
+		\norm{F}_F =& \sqrt{\tr{F^T F}} \\
+		=& \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} \right.\\
+		& \left.- 2 \tr{a^T b} + 2 \tr{a^T c } + \tr{b^T b} \right. \\
+		&\left. - 2 \tr{b^T c} + \tr{c^T c}\right] \, .
+	\end{align*}
+	where the terms \( a, b, \text{ and } c \) are given by
+	\begin{gather*}
+		a = r^T R r I \, ,\\
+		b = R^T v r^T \, ,\\
+		c = \frac{R^T \hat{v} R r v^T R \hat{r}}{r^T R^T v - \cos \theta}\, .
+	\end{gather*}
+	A straightforward computation of \( a^T a \) shows that
+	\begin{gather*}
+		\tr{a^T a} = \parenth{v^T R r}^2 \tr{I} \leq 3 \beta^2 \, ,
+	\end{gather*}
+	where we used the fact that \( v^T R r = r^T R^T v < \beta \) from our given domain.
+	Similarly, one can show that \( \tr{a^T b} \) is equivalent to
+	\begin{gather*}
+		\tr{a^T b} = v^T R r \tr{R^T v r^T} = \parenth{v^T R r}^2 \leq \beta^2 \, ,
+	\end{gather*} 
+	where we used the fact that \( \tr{x y^T} = x^T y \).
+	The product \( \tr{a^T c} \) is given by
+	\begin{gather*}
+		\tr{a^T c} = \frac{v^T R r}{r^T R^T v - \cos \theta} \tr{\parenth{R^T v}^\vee \parenth{r v^T R} \hat{r} } \, ,
+	\end{gather*}
+	where we used the hat map property~\cref{eqn:RxR}.
+	One can show that \(\tr{a^T c} \leq 0 \) over the range \( -1 \leq v^T R r \leq \cos \theta \). 
+	Next, \( \tr{b^T b}\) is equivalent to
+	\begin{gather*}
+		\tr{b^T b} = \tr{r v^T R R^T v r^T} = 1 \, ,
+	\end{gather*}
+	since \( r,v \in \Sph^2\).
+	Finally, \( \tr{c^T c} \) is reduced to
+	\begin{gather*}
+		\tr{c^T c} = \tr{\hat{r} R^T v r^T \bracket{-I + R^T v v^T R} r v^T R \hat{r}} \, ,
+	\end{gather*}
+	where we used the fact that \( \hat{x}^2 = - \norm{x}^2 I + x x^T\).
+	Expanding and collecting like terms gives
+	\begin{gather*}
+		\tr{c^T c } = \frac{1 - 2\parenth{v^T R r}^2 + \parenth{v^T R r}^4}{\parenth{r^T R^T v - \cos \theta}^2} \, . 
+	\end{gather*}
+	Using the the given domain \( r^T R^T v \leq \beta \) gives the upper bound~\cref{eqn:F_bound}.
+
+	The bound on \( e_{R_A} \) is given in~\cref{eqn:psi_lower_bound} while \( e_{R_B} \) arises from the definition of the cross product \( \norm{a \times b} = \norm{a} \norm{b} \sin \theta \).
+
+\subsection{Proof of~\cref{prop:adaptive_control}}\label{proof:adaptive_control}
+	Consider the Lyapunov function \( V \) given by
+	\begin{gather}
+		V = \frac{1}{2} e_\Omega J e_\Omega + k_R \Psi + c J e_\Omega^T e_R + \frac{1}{2 k_\Delta} e_\Delta^T e_\Delta \, , \label{eqn:v_adapt}
+	\end{gather}
+	over the domain \( D \) in~\cref{eqn:domain}.
+	From~\Cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
+	\begin{gather}
+		V \leq z^T W z \, , \label{eqn:v_upper_bound}
+	\end{gather}
+	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = \begin{bmatrix}e_R & e_\Omega & e_\Delta\end{bmatrix} \) and the matrix \(W \in \R^{3 \times 3}\) is given by
+	\begin{gather*}
+		W = \begin{bmatrix}
+			k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
+			\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
+			0 & 0 & \frac{1}{2 k_\Delta}
+		\end{bmatrix} \, .
+	\end{gather*}
+	The time derivative of \( V\) with the control inputs~\cref{eqn:adaptive_control} is defined as
+	\begin{align}
+		\dot{V} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
+		&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} \, , \label{eqn:vdot}
+	\end{align}
+	where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
+	The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
+	\begin{align*}
+		 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 \, . 
+	\end{align*}
+	Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{V} \) is written as
+	\begin{gather*}
+		\dot{V} \leq -z^T M z \, ,
+	\end{gather*}
+	where the matrix \( M \in \R^{2 \times 2} \) is 
+	\begin{gather}
+		M = \begin{bmatrix}
+			k_R c & \frac{k_\Omega c}{2} \\
+			\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
+		\end{bmatrix} \, .
+	\end{gather}
+	If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
+	This implies that the zero equilibrium \( e_R, e_\Omega\) is asymptotically stable. 
+	The domain \( D \) does that include the undesired equilibria and ensures that as \( e_R \to 0 \) the attitude also converges \( R \to R_d \).
 

### 2015-09-25 ACC16.2.tex
down to 8 pages and corrected some errors

@@
 
-\author{Shankar Kulumani, Chris Poole, and Taeyoung Lee
-\thanks{Shankar Kulumani, Chris Poole, Taeyoung Lee, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 {\tt \{skulumani,poolec,tylee\}@gwu.edu}}
+\author{Shankar Kulumani, Christopher Poole, and Taeyoung Lee
+\thanks{Shankar Kulumani, Christopher Poole, Taeyoung Lee, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 {\tt \{skulumani,poolec,tylee\}@gwu.edu}}
 \thanks{This research has been supported in part by NSF under the grants CMMI-1243000, CMMI-1335008, and CNS-1337722.}
@@
 The three-dimensional special orthogonal group is the set of \( 3 \times 3 \) orthogonal matrices whose determinant is one.
-This configuration space is not Euclidean and yields unique stability properties which are not observable on a linear space.
+This configuration space is non-Euclidean and yields unique stability properties which are not observable on a linear space.
 For example, it is impossible to achieve global attitude stabilization using continuous time-invariant feedback~\cite{bhat2000}.
@@
 An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
-During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}.
-Unwinding is where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.
+During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}, where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.
 
@@
 \begin{align*}
-	\SO = \{R\in\Re^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\} \, ,
+	\SO = \{R\in\R^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\} \, ,
 \end{align*}
@@
 \end{gather}
-where $J\in\R^{3\times 3}$ is the inertia matrix, and $\Omega\in\R^{3\times1}$ is the angular velocity represented with respect to the body-fixed frame. 
-The control moment is denoted by $u\in\R^{3\times1}$, and it is expressed with respect to the body-fixed frame. 
-We assume that the external disturbance is expressed by $W(R,\Omega)\Delta$, where $W(R,\Omega):\SO\times\R^{3\times1}\rightarrow \R^{3\times p}$ is a known function of the attitude and the angular velocity.
-The disturbance is represented by $\Delta\in\R^{p\times1}$ is an unknown, but fixed uncertain parameter.
-In addition, we assume that a bound on \( W(R, \Omega) \) is known and given by
+where $J\in\R^{3\times 3}$ is the inertia matrix, and $\Omega\in\R^{3}$ is the angular velocity represented with respect to the body-fixed frame. 
+The control moment is denoted by $u\in\R^{3}$, and it is expressed with respect to the body-fixed frame. 
+We assume that the external disturbance is expressed by $W(R,\Omega)\Delta$, where $W(R,\Omega):\SO\times\R^{3}\rightarrow \R^{3\times p}$ is a known function of the attitude and the angular velocity.
+The disturbance is represented by $\Delta\in\R^{p}$ is an unknown, but fixed uncertain parameter.
+In addition, we assume that a bound on \( W(R, \Omega) \text{ and } \Delta \) is known and given by
 \begin{equation}
-	\norm{W} \leq B_W \, . \label{eqn:W_bound}
+	\norm{W} \leq B_W \, , \quad \norm{\Delta} \leq B_\Delta \,. \label{eqn:W_bound}
 \end{equation}
 
-In~\refeqn{Rdot}, the \textit{hat} map $\wedge :\R^{3\times1}\rightarrow\so$ represents the transformation of a vector in $\R^{3\times1}$ to a $3\times 3$ skew-symmetric matrix such that $\hat x y = x\times y$ for any $x,y\in\R^{3\times1}$~\cite{bullo2004}.
+In~\refeqn{Rdot}, the \textit{hat} map $\wedge :\R^{3}\rightarrow\so$ represents the transformation of a vector in $\R^{3}$ to a $3\times 3$ skew-symmetric matrix such that $\hat x y = x\times y$ for any $x,y\in\R^{3}$~\cite{bullo2004}.
 More explicitly, 
@@
 \end{align*}
-for $x=[x_1,x_2,x_3]^T\in\R^{3\times1}$. 
-The inverse of the hat map is denoted by the \textit{vee} map $\vee:\so\rightarrow\R^{3\times1}$. 
+for $x=[x_1,x_2,x_3]^T\in\R^{3}$. 
+The inverse of the hat map is denoted by the \textit{vee} map $\vee:\so\rightarrow\R^{3}$. 
 Several properties of the hat map are summarized as
@@
 \end{gather}
-for any $x,y,z\in\R^{3\times1}$, $A\in\R^{3\times 3}$ and $R\in\SO$. 
+for any $x,y,z\in\R^{3}$, $A\in\R^{3\times 3}$ and $R\in\SO$. 
 Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\R^n$ and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively.
-The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A}_F = \tr{A^T A} \).
+The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A}_F = \sqrt{\tr{A^T A}} \).
 This results in \( \norm{A} \leq \norm{A}_F \leq \sqrt{r}\norm{A} \), where \( r \) is the rank of A.
@@
 	\begin{align}
-		\dirDiff{\Psi}{R} &= \dirDiff{A}{R} \,  B(R) + A \,  \dirDiff{B}{R} \, . \\
+		\dirDiff{\Psi}{R} &= \dirDiff{A}{R} \,  B(R) + A \,  \dirDiff{B}{R} \, .
 	\end{align}
@@
 	\begin{align*}
-		h_1 &= \min{g_1 + g_2, g_2 + g_3 , g_3 + g_1} \, ,\\
-		h_2 &= \min{\parenth{g_1 -g_2}^2,\parenth{g_2 -g_3}^2 , \parenth{g_3 -g_1}^2} \, ,\\
-		h_3 &= \min{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} \, .				
+		h_1 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} \, ,\\
+		h_2 &= \min\braces{\parenth{g_1 -g_2}^2,\parenth{g_2 -g_3}^2 , \parenth{g_3 -g_1}^2} \, ,\\
+		h_3 &= \min\braces{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} \, .				
 	\end{align*}
@@
 The attractive error function has been used for attitude control on \SO.
-In order to incorporate the state inequality constraints we apply a logarithmic barrier function term.
+In order to incorporate the state inequality constraints we apply a logarithmic barrier term.
 Barrier functions are typically used in optimal control and motion planning applications.
@@
 If \( e_\Omega \) is sufficiently small this results in \( W > 0 \) and \( \dot{W} = -\dot{V} > 0\) from~\cref{eqn:vdot_nodist}.
-According to Chateav's theorem the undesired equilibria are unstable~\cite{khalil1996}.
+According to Chateav's theorem, the undesired equilibria are unstable~\cite{khalil1996}.
 As a result, we can claim that the desired equilibrium \( R = R_d \text{ and } e_\Omega = 0 \) is almost globally asymptotically stable.
@@
 \end{table}
-
 The initial and desired states are defined using Euler angles as~\cite{shuster1993},
 \begin{gather*}
-	R_0 = \text{ROT3}(\ang{225}) \, , \quad \Omega_0 = 0 \, ,\\
-	R_d = I \, , \quad \Omega_d = 0 \, .
+	R_0 = \text{ROT3}(\ang{225}) \, , \quad \Omega_0 = 0 \, ,\quad	R_d = I \, , \quad \Omega_d = 0 \, .
 \end{gather*}
@@
 
-Simulation results without the adaptive update law are shown in~\cref{fig:con,fig:adapt}, respectively.
+Simulation results without the adaptive update law are shown in~\cref{fig:con}.
 Without the update law, the system does not achieve zero steady state error. 
@@
 \begin{gather*}
-	k_R = 0.4 \, , \quad k_\Omega = 0.7 \, , c = 0.1 \\
-	\alpha = 8 \, , k_\Delta = 0.05 \, .
+	k_R = 0.4 \, , \quad k_\Omega = 0.7 \, , \quad c = 0.1 \, ,\quad \alpha = 8 \, , \quad k_\Delta = 0.05 \, .
 \end{gather*}
@@
 An increased gain of the adaptive update law would improve the final steady state error performance.
-A video clip showing the attitude manuever is available \url{https://youtu.be/IQLgNXfv_WA}.
+A video clip showing the attitude manuever is available \url{https://youtu.be/dsmAbwQram4}.
 \section{Conclusion}\label{sec:conclusion}
@@
 for all \( R \in \SO \). 
-As a result, the negative logarithm is always positive and
-\begin{align*}
-	1 < B \, .
-\end{align*}
+As a result, the negative logarithm is always positive, \(1 < B\)
 The product~\cref{eqn:psi} is composed of two positive terms and is therefore also positive definite, and has a single critical point at \( R = R_d \).
@@
 \begin{align*}
-	\dirDiff{A}{R} &= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
-	&= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee \, ,
+	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee \, ,
+%	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
 \end{align*}
@@
 \begin{align*}
-	\dirDiff{B}{R} &= -\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta} \right) \right]  \\
-	&= \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} \, ,
+	\dirDiff{B}{R} &=  \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} \, ,
+%	-\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta} \right) \right]
 \end{align*}
@@
 
-To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
-The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
-\begin{align*}
-	Q = R_d^T R = 
-	\begin{bmatrix}
-		q_{11} & q_{12} & q_{13} \\
-		q_{21} & q_{22} & q_{23} \\
-		q_{31} & q_{32} & q_{33}
-	\end{bmatrix} \, .
-\end{align*}
-Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
-\begin{subequations}
-\begin{align}
-	g_3 q_{32} &= g_2 q_{23} \, , \\
-	g_1 q_{13} &= g_3 q_{31} \, , \\
-	g_2 q_{21} &= g_1 q_{12} \, .
-\end{align}
-\end{subequations}
-These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
-Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
-\begin{subequations}
-\begin{align}
-	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 \, , \\
-	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, , \\
-	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, .
-\end{align}
-\end{subequations}
-As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
-Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
+%To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
+%The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
+%\begin{align*}
+%	Q = R_d^T R = 
+%	\begin{bmatrix}
+%		q_{11} & q_{12} & q_{13} \\
+%		q_{21} & q_{22} & q_{23} \\
+%		q_{31} & q_{32} & q_{33}
+%	\end{bmatrix} \, .
+%\end{align*}
+%Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
+%\begin{subequations}
+%\begin{align}
+%	g_3 q_{32} &= g_2 q_{23} \, , \\
+%	g_1 q_{13} &= g_3 q_{31} \, , \\
+%	g_2 q_{21} &= g_1 q_{12} \, .
+%\end{align}
+%\end{subequations}
+%These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
+%Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
+%\begin{subequations}
+%\begin{align}
+%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 \, , \\
+%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, , \\
+%	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, .
+%\end{align}
+%\end{subequations}
+%As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
+%Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
+The critical points of \( e_{R_A} \) are derived in~\cite{bullo2004}.
 There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180}.
@@
 \begin{gather*}
-	\diff{}{t} (B) = \frac{r_i^T \parenth{\hat{\Omega} R^T} v_i}{\alpha \parenth{r_i^T R^T v_i - \cos \theta}} \, .
+	\diff{}{t} (B) = \frac{r^T \parenth{\hat{\Omega} R^T} v}{\alpha \parenth{r^T R^T v - \cos \theta}} \, .
 \end{gather*}
@@
 
-The time-derivative of the angular velocity error, \( e_\Omega \), is given by
+The time-derivative of the angular velocity error, \( e_\Omega \), is rearranged from~\cref{eqn:Wdot} as 
 \begin{align*}
-	\diff{}{t} e_\Omega &= \dot{\Omega} \\
-	&= J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } \, ,
+	\diff{}{t} e_\Omega = \dot{\Omega} = J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } \, .
 \end{align*}
-where we have used the dynamic equations of motion from~\cref{eqn:Wdot}. 
 \subsection{Proof of~\Cref{prop:att_control}}\label{proof:att_control}
@@
 	\begin{align}
-		\dot{V} &= e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
-		&= -k_\Omega \norm{e_\Omega}^2 \, . \label{eqn:vdot_nodist}
+		\dot{V} &= -k_\Omega \norm{e_\Omega}^2 \, . \label{eqn:vdot_nodist}
+%		e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
 	\end{align}
@@
 	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
-	However, this would be in contradiction with~\cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
+	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
 	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
@@
 	To show~\cref{eqn:F_bound}, we apply the Frobenius norm \( \norm{F}_F \):
-	\begin{align*}
-		\norm{F}_F =& \sqrt{\tr{F^T F}} \\
-		=& \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} \right.\\
-		& \left.- 2 \tr{a^T b} + 2 \tr{a^T c } + \tr{b^T b} \right. \\
-		&\left. - 2 \tr{b^T c} + \tr{c^T c}\right] \, .
-	\end{align*}
+	\begin{gather*}
+		\norm{F}_F = \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} - 2 \tr{a^T b} \right. \\
+		\left.+ 2 \tr{a^T c } + \tr{b^T b}  - 2 \tr{b^T c} + \tr{c^T c}\right] \, .
+	\end{gather*}
 	where the terms \( a, b, \text{ and } c \) are given by
 	\begin{gather*}
-		a = r^T R r I \, ,\\
-		b = R^T v r^T \, ,\\
-		c = \frac{R^T \hat{v} R r v^T R \hat{r}}{r^T R^T v - \cos \theta}\, .
+		a = r^T R r I \, , \quad	b = R^T v r^T \, , \quad c = \frac{R^T \hat{v} R r v^T R \hat{r}}{r^T R^T v - \cos \theta}\, .
 	\end{gather*}
@@
 	Using the the given domain \( r^T R^T v \leq \beta \) gives the upper bound~\cref{eqn:F_bound}.
-
 	The bound on \( e_{R_A} \) is given in~\cref{eqn:psi_lower_bound} while \( e_{R_B} \) arises from the definition of the cross product \( \norm{a \times b} = \norm{a} \norm{b} \sin \theta \).
@@
 	\begin{gather}
-		V = \frac{1}{2} e_\Omega J e_\Omega + k_R \Psi + c J e_\Omega^T e_R + \frac{1}{2 k_\Delta} e_\Delta^T e_\Delta \, , \label{eqn:v_adapt}
+		V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta \, , \label{eqn:v_adapt}
 	\end{gather}
@@
 	\end{gather}
-	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = \begin{bmatrix}e_R & e_\Omega & e_\Delta\end{bmatrix} \) and the matrix \(W \in \R^{3 \times 3}\) is given by
+	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = \begin{bmatrix}e_R & e_\Omega & e_\Delta\end{bmatrix}^T \) and the matrix \(W \in \R^{3 \times 3}\) is given by
 	\begin{gather*}

### 2015-09-25 ACC16.2.tex
added Dr. Lee bib file. changed some references
corrections from dr. lee

@@
 This representation is geometrically exact and avoids singularities and ambiguities of other attitude parameterizations, such as Euler angles and quaternions.
-Attitude constraints are incorporated and automatically considered by the control system.
+The control system is designed such that the desired attitude is asymptotically stabilized, while the controlled attitude trajectory avoids undesired regions defined by an inequality constraint.
 In addition, we develop an adaptive update law that enables attitude stabilization in the presence of unknown disturbances. 
@@
 One distinctive feature of the attitude dynamics of rigid bodies is that it evolves on a nonlinear manifold.
-The three-dimensional special orthogonal group is the set of \( 3 \times 3 \) orthogonal matrices whose determinant is one.
+The three-dimensional special orthogonal group, namely \( \SO \), is the set of \( 3 \times 3 \) orthogonal matrices whose determinant is one.
 This configuration space is non-Euclidean and yields unique stability properties which are not observable on a linear space.
@@
 The removal of constrained regions from the rotational configuration space results in a \textit{nonconvex} region.
-The attitude control problem in the absence of constraints has been extensively studied~\cite{sanyal2008,lee2010,lee2011a}.
+The attitude control problem in the absence of constraints has been extensively studied~\cite{bullo2004,MayTeePaCC11,LEEITAC15}.
 However, the attitude control problem in the presence of constraints has received much less attention.
@@
 
-In this work, we develop a geometric adaptive controller on \(\SO\) to reorient a rigid body in the presence of state inequality constraints.
+% MORE DETAIL ON CONTRIBUTIONS 
+% EXPLICITLY STATE - first time for constraints to be incorportated on SO(3) with barrier function
+% Consider adaptive control which allows for stabilization in the presence of uncertain terms
+% Benefits over previous approach -
+% Developed on SO(3) - avoids issues of singularities and ambiguities of quaternion approach
+% Geometric approach - requires a priori calculation of trajectory. not robust to uncertainties or changes in configuraiton
+% Random/Graph approach -computationally expensive. requires a priori calculation of trajectory
+
+% Previous potential function approach - developed using att parameterizations - singularities/ambiguities
+Artifical potential functions are commonly used to handle kinematic constraints for a wide range of problems in robotics.
+The goal is the design of an attractive function which parameterizes the distance to the desired state.
+Similarly, a repulsive function is constructed such that the system is directed outward from the constraints. 
+The superposition of the these functions allows one to apply standard feedback control schemes for stabilization and tracking.
+Artificial potential functions have previously been applied to the attitude control problem in~\cite{lee2011b,mcinnes1994}.
+These approaches were developed using attitude parameterizations, namely Euler angles and quaternions.
+By characterizing the attitude both globally and uniquely \SO, we completely avoid issues associated with local parameterizations of the configuration manifold.
+
+In short, the main contribution of this paper is developing an adaptive attitude control scheme in the presence of attitude inequality constraint on \SO.
 We apply a potential function based approach developed directly on the nonlinear manifold \SO.
-Geometric control is concerned with the development of control systems for dynamic systems that evolve on nonlinear manifolds.
-Artificial potential functions have previously been applied to the attitude control problem~\cite{lee2011b,mcinnes1994}.
-These approaches have used attitude parameterizations that give rise to singularities and ambiguities.
-By characterizing the intrinsic geometric properties of \SO, we completely avoid issues associated with local parameterizations of the configuration manifold.
-In this paper, we present a Lyapunov analysis to guarantee stability in the presence of state constraints.
-In addition, we formulate an adaptive update law to enable attitude convergence in the presence of disturbances.
-These results are demonstrated via numerical examples and experimental results on a hexrotor aerial vehicle.
+Our approach avoids the issues of attitude parameterizations, such as kinematic singularities and ambiguities, and is geometrically exact.
+Our approach is also computationally efficient and able to handle uncertain disturbances. 
+Instead of calculating a priori trajectories, as in the geometric and randomized approaches, our approach results in a closed-loop attitude control system.
+This makes it ideal for on-board implentation on UAV or spacecraft systems.
+In addition, unlike previous approaches our control system can handle an arbitrary number of constrained regions without modification. 
+Finally, a rigous Lyapunov analysis guarantees the stability of the proposed control system, rather than probablistic convergence properties of the randomized approach.
+
+We develope a new configuration error function on \SO with a logarithmic barrier function to avoid constrained regions.
+We present a mathematically rigorous analysis to guarantee stability of the proposed control system.
+In addition, we formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances.
+We demonstrate the effectiveness of this new approach via numerical simulation and experimental results on a hexrotor aerial vehicle.
+%In this work, we develop a geometric adaptive controller on \(\SO\) to reorient a rigid body in the presence of state inequality constraints.
+
+%Geometric control is concerned with the development of control systems for dynamic systems that evolve on nonlinear manifolds.
+
 \section{Problem Formulation}\label{sec:prob_form}
@@
 The two-sphere is the manifold of unit-vectors in \( \R^3 \) such that \( \Sph^2 = \{ q \in \R^3 \,  \vert \, \norm{q} = 1 \}\).
-We define \( r \in \Sph^2 \) to be a unit vector from the mass center of the rigid body and represented with respect to the body-fixed frame.
+We define \( r \in \Sph^2 \) to be a unit vector from the mass center of the rigid body along a certain direction and it is represented with respect to the body-fixed frame.
 For example, \( r \) may represent the pointing direction of an on-board optical sensor.
@@
 \end{align}
-where \( \ang{0} \leq \theta \leq \ang{90}  \) is the required minimum angular separation between \( r \) and \( R^T v \). 
+where we assume \( \ang{0} \leq \theta \leq \ang{90}  \) is the required minimum angular separation between \( r \) and \( R^T v \). 
 The objective is to a determine a control input \( u \) that stabilizes the system from an initial attitude \( R_0 \) to a desired attitude \( R_d \) while ensuring that~\cref{eqn:constraint} is always satisfied.
@@
 A new configuration error function is proposed for attitude control in the presence of state inequality constraints.
-We extend the form used in~\cite{bullo2004,lee2011a} for attitude control on \SO with the addition of a logarithmic barrier function.
+We extend the form used in~\cite{bullo2004,lee2011a} for attitude control on \(\SO\) with the addition of a logarithmic barrier function.
 We use the configuration error function to develop a nonlinear geometric attitude controller for the stabilization of a general rigid body. 
@@
 We assume a desired attitude command \( ( R_d, \Omega_d = 0 ) \), the current attitude and angular velocity \( ( R, \Omega) \), and a state constraint~\cref{eqn:constraint} are given.
-We define an attitude error function \( \Psi : \SO \times \SO \to \R \), and attitude error vector \( e_R : \SO \times \SO \to \R \), and an angular velocity error vector \( e_\Omega : \R^3 \to \R^3 \) as follows:
+We define an attitude error function \( \Psi : \SO \times \SO \to \R \), and attitude error vector \( e_R \in \R^3 \), and an angular velocity error vector \( e_\Omega \in \R^3 \) as follows:
 \begin{gather}
@@
 \end{gather}	
-where the matrix \( G \in \R^{3 \times 3} \) is defined as a diagonal matrix matrix for distinct, positive constants \( g_1, g_2, g_3 \in \R \).
+where \( \alpha \in \R \) is defined as a positive constant and the matrix \( G \in \R^{3 \times 3} \) is defined as a diagonal matrix matrix for distinct, positive constants \( g_1, g_2, g_3 \in \R \).
 Then, the following properties hold
@@
 	\item \label{item:prop_psi_psd} \(\Psi\) is locally positive definite about \( R = R_d\)
-	\item \label{item:prop_er} The variation of \( \Psi \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
-	\begin{align}
-		\dirDiff{\Psi}{R} &= \dirDiff{A}{R} \,  B(R) + A \,  \dirDiff{B}{R} \, .
-	\end{align}
 	\item \label{item:prop_era}The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
@@
 	\end{align}
-	\item \label{item:prop_crit}The critical points of \( \Psi \),where \( e_R = 0\), are \( \braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \) and \( R^T v = \pm r \).
+	\item \label{item:prop_crit}The critical points of \( \Psi \), where \( e_R = 0\), are \( \braces{R_d} \cup \braces{R = R_d \exp(\pi \hat{s})  \text{ for } s \in \braces{e_1, e_2, e_3} \vert R^T v = \pm r }\).
 	\item \label{item:prop_era_upbound}An upper bound of \( \norm{e_{R_A}} \) is given as:
@@
 \begin{proof}
-See~\Cref{proof:config_error}
+See~\Cref{proof:config_error}.
 \end{proof}
 
-\Cref{eqn:psi} is composed of an attractive term \( A (R) \) and a repulsive term \( B(R) \).
+\Cref{eqn:psi} is composed of an attractive term \( A (R) \) toward the desired attitude and a repulsive term \( B(R) \) away from the undesired direction \( R^T v \).
 The attractive error function has been used for attitude control on \SO.
+The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}.
+The desired attitude lies at the minimum of \( A(R) \).
+
 In order to incorporate the state inequality constraints we apply a logarithmic barrier term.
 Barrier functions are typically used in optimal control and motion planning applications.
-As the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
+A visualization of the configuration error function is presented in~\cref{fig:config_error}.
+\Cref{fig:avoid_errro} illustrated that as the boundary of the constraint in is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
+We use the scale factor~\(\frac{1}{1+\cos \theta} \) to ensure that \( \Psi \) remains positive definite.
 The logarithmic function is popular as it quickly decays away from the constraint boundary.
@@
 As \( \alpha \) is increased the impact of \( B(R) \) is reduced away from the constraint boundary. 
-In addition, it is possible to incorporate an arbitrary number of state inequality constraints of the form given in~\cref{eqn:constraint}.
-The configuration error function may be reformulated as \( \Psi = A \bracket{1 + \sum B_i} \) where \( B_i = B - 1 \).
+The super position of the attractive and repulsive functions is shown in~\cref{fig:combined_error}.
+The control system follows the direction of the gradient of \( \Psi \) towards the minimum at \( R = R_d \) while avoiding any constrained regions.
+\begin{figure} 
+	\centering 
+	\begin{subfigure}[htbp]{0.3\columnwidth} 
+		\includegraphics[width=\columnwidth]{attract_error} 
+		\caption{Attractive \( A(R) \) } \label{fig:attract_error} 
+	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+	\begin{subfigure}[htbp]{0.3\columnwidth} 
+		\includegraphics[width=\columnwidth]{avoid_error} 
+		\caption{Repulsive \( B(R) \)} \label{fig:avoid_error} 
+	\end{subfigure}~
+	\begin{subfigure}[htbp]{0.3\columnwidth} 
+		\includegraphics[width=\columnwidth]{combined_error} 
+		\caption{Configuration \( \Psi \)} \label{fig:combined_error} 
+	\end{subfigure}
+	\caption{Configuration error function visualization}
+	\label{fig:config_error} 
+\end{figure}
+
+While\cref{eqn:B} represents a single inequality constraint given as~\cref{eqn:constraint}, it is readily generalized to multiple constraints of an arbitrary form. 
+For example, the configuration error function for multiple constraints can be formulated as $\Psi=A[1+\sum_i C_i]$, where $C_i$ has the form of $C_i=B-1$ for the $i$-th constraint. 
 In this manner, one may enforce multiple state inequality constraints on the control system.
+
 \begin{prop}[Error Dynamics]\label{prop:error_dyn}
@@
 \begin{proof}
-See~\Cref{proof:error_dyn}
+See~\Cref{proof:error_dyn}.
 \end{proof}
@@
 We introduce a nonlinear geometric controller for the attitude stabilization of a rigid body.
-We assume that there is no disturbance, i.e., \( \Delta = 0 \).
+We first assume that there is no disturbance, i.e., \( \Delta = 0 \).
 \begin{prop}[Attitude Control]\label{prop:att_control}
@@
 \begin{proof}
-See~\Cref{proof:att_control}
+See~\Cref{proof:att_control}.
 \end{proof}
@@
 This proposition only guarantees that the attitude error vector \( e_R \) asymptotically converges to zero.
-However, this does not necessarily show that \( R \to R_d \) as \( t \to \infty \). 
-There are three additional critical points of \( \Psi \) where \( e_R = 0 \).
+However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are three additional critical points of \( \Psi \) where \( e_R = 0 \).
 At an undesired equilibrium \( R = \exp{ \parenth{\pi \hat{e}_i}} R_d \) and \( e_\Omega =0 \).
-This results in \( A \) having a value of \( g_1 + g_2, g_2 + g_3 \) or \( g_3 + g_1 \).
-At any of these undesired equilibria we have \( V = k \). 
-We define an augmented Lyapunov function as
-\begin{align*}
-	W = k - V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \parenth{\frac{k}{k_R}+ \Psi(R,R_d)} \, .
-\end{align*}
-We can choose an attitude \( R \) arbitrarily close to the equilibrium point \( \exp{ \parenth{\pi \hat{e}_i}} R_d \) such that the \( k_R \parenth{\frac{k}{k_R}+\Psi }> 0 \).
-This is due to the fact that \( \Psi \) is positive definite about \( R = R_d \) as shown in~\cref{item:prop_psi_psd}.
-If \( e_\Omega \) is sufficiently small this results in \( W > 0 \) and \( \dot{W} = -\dot{V} > 0\) from~\cref{eqn:vdot_nodist}.
-According to Chateav's theorem, the undesired equilibria are unstable~\cite{khalil1996}.
-As a result, we can claim that the desired equilibrium \( R = R_d \text{ and } e_\Omega = 0 \) is almost globally asymptotically stable.
+However, we can show that these undesired equilibrium points are unstable in the sense of Lyapunov~\cite{LeeITCST13}.
+As a result, we can claim that the desired equilibrium \( R = R_d \text{ and } e_\Omega = 0 \) is almost globally asymptotically stable, which means that the set of initial conditions that do not converge to the desired attitude has zero Lebesgue measure.
 
+%This results in \( A \) having a value of \( g_1 + g_2, g_2 + g_3 \) or \( g_3 + g_1 \).
+%At any of these undesired equilibria we have \( V = k \). 
+%We define an augmented Lyapunov function as
+%\begin{align*}
+%	W = k - V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \parenth{\frac{k}{k_R}+ \Psi(R,R_d)} \, .
+%\end{align*}
+%We can choose an attitude \( R \) arbitrarily close to the equilibrium point \( \exp{ \parenth{\pi \hat{e}_i}} R_d \) such that the \( k_R \parenth{\frac{k}{k_R}+\Psi }> 0 \).
+%This is due to the fact that \( \Psi \) is positive definite about \( R = R_d \) as shown in~\cref{item:prop_psi_psd}.
+%If \( e_\Omega \) is sufficiently small this results in \( W > 0 \) and \( \dot{W} = -\dot{V} > 0\) from~\cref{eqn:vdot_nodist}.
+%According to Chateav's theorem, the undesired equilibria are unstable~\cite{khalil1996}.
 \subsection{Adaptive Control}
@@
 Aerial vehicles will similarly experience external torques due to air currents or turbulence.
-A smooth control system is introduced to asymptotically stabilize the system to a desired attitude while ensuring that state constraints are satisfied.
+An adaptive control system is introduced to asymptotically stabilize the system to a desired attitude while ensuring that state constraints are satisfied.
 
@@
 \begin{align}
-	D = \braces{R \in \SO \vert \Psi < \psi < h1, r^T R^T v < \beta < \cos \theta} \, . \label{eqn:domain}
+	D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}. \label{eqn:domain}
 \end{align}
@@
 	\begin{gather}
-		\norm{A} < \psi \, , \label{eqn:A_bound}\\
-		\norm{B} < \psi \, . \label{eqn:B_bound}
+		\norm{A} < c_A \, , \label{eqn:A_bound}\\
+		\norm{B} < c_B \, . \label{eqn:B_bound}
 	\end{gather}
@@
 \begin{proof}
-See~\Cref{proof:adaptive_control}
+See~\Cref{proof:adaptive_control}.
 \end{proof}
@@
 In addition, the unwinding and double coverage ambiguity of quaternions are also completely avoided. 
+The control system handles uncertain disturbances while avoiding constrained regions.
 
+Compared to the previous work on constrained attitude control, we present a geometrically exact control system without parameterizations.
+In addition, we incorporate state inequality constraints for the first time on \( \SO \).
+The presented control system is computed in real-time and offers significant computational advantages over previous iterative methods. 
+In addition, the riguous mathematical proof guarantees stability.
 \section{Numerical Examples}
@@
 while multiple inequality constraints are defined in~\Cref{tab:constraints}.
-The simulation parameters are chosen to emulate those found in~\cite{lee2011b}.
+The simulation parameters are chosen to similar those found in~\cite{lee2011b}.
+We increase the size of the constraint regions to create a more challenging scenario for the control system.
 \begin{table}[htbp]
-\caption{Simulation Parameters~\label{tab:constraints}}
+\caption{Constraint Parameters~\label{tab:constraints}}
 \begin{center}\begin{tabular}{lc}
-Constraint Vector & Angle \\ \hline \hline 
+Constraint Vector (\( v \)) & Angle (\( \theta \)) \\ \hline \hline 
 \(\begin{bmatrix} 0.174 &-0.934 & -0.034 \end{bmatrix}\) & \ang{40} \\ \hline 
@@
 \end{table}
-The initial and desired states are defined using Euler angles as~\cite{shuster1993},
+The initial and desired states are defined as
 \begin{gather*}
-	R_0 = \text{ROT3}(\ang{225}) \, , \quad \Omega_0 = 0 \, ,\quad	R_d = I \, , \quad \Omega_d = 0 \, .
+	R_0 =  \exp(\ang{225} * \frac{\pi}{180} \hat{e}_3)\, , \quad \Omega_0 = 0 \, ,\quad	R_d = I \, , \quad \Omega_d = 0 \, .
 \end{gather*}
@@
 \begin{gather*}
-	\Delta = \begin{bmatrix} 0.06 & 0.06 & 0.09 \end{bmatrix}^T \, ,
+	\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \, ,
 \end{gather*}
@@
 		\caption{Configuration error \( \Psi \)} \label{fig:Psi_con} 
-	\end{subfigure}
-
-	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{u_con} 
-		\caption{Control input \( u\)} \label{fig:u_con} 
-	\end{subfigure}~
-	\begin{subfigure}[htbp]{0.5\columnwidth}
-		\includegraphics[width=\columnwidth]{cad}
-		\caption{Trajectory in inertial frame\label{fig:cad}}
 	\end{subfigure}
@@
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{u_adapt} 
-		\caption{Control input \( u\)} \label{fig:u_adapt} 
+		\includegraphics[width=\columnwidth]{delta_adapt} 
+		\caption{Disturbance estimate \( \bar \Delta \)} \label{fig:delta_adapt} 
 	\end{subfigure}~
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{Delta_adapt} 
-		\caption{Disturbance estimate \( \bar{\Delta}\)} \label{fig:Delta_adapt} 
+		\includegraphics[width=\columnwidth]{cad_adapt} 
+		\caption{Attitude trajectory} \label{fig:cad_adapt} 
 	\end{subfigure}
@@
 Without the update law, the system does not achieve zero steady state error. 
-\Cref{fig:Psi_con} shows that the configuration error function does not converge to zero.
+\Cref{fig:Psi_con} shows that the configuration error function does not converge to zero and there exist steady state errors.
 \Cref{fig:adapt} shows the results with the addition of the adaptive update law.
 The addition of the adaptive update law allows the system to converge to the desired attitude in the presence of constraints.
-The path of the body fixed sensor in the inertial frame is illustrated in~\cref{fig:cad}.
+The path of the body fixed sensor in the inertial frame, namely \( R r \), is illustrated in~\cref{fig:cad_adapt}.
 The initial attitude is represented with the green circle while the final attitude is marked with a green \(\times\).
+The inequality constraints from~\cref{tab:constraints} are depicted as red cones, where the cone half angle is \( \theta \).
 The control system is able to asymptotically converge to zero attitude error.
 In addition, the estimate of the disturbance converges to the the true value.
+
 Both control system are able to automatically avoid the constrained regions. 
@@
 
-A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory(FDCL) at the George Washington University.
+A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory(FDCL) at the George Washington University (CITE EVAN PAPER).
 The UAV is composed of three pairs of counter-rotating propellers. 
@@
 \begin{itemize}
-	\item Onboard ODROID XU3 Linux processor.
+	\item Onboard ODROID XU3 computer module.
 	\item VectorNav VN100 IMU operating at over \SI{100}{\hertz} via TTL serial 
@@
 We define an obstacle in the inertial frame as \( v = \begin{bmatrix} \frac{1}{\sqrt{2}} & \frac{1}{\sqrt{2}} & 0\end{bmatrix}^T \) with \( \theta = \ang{12} \).
-An initial and desired attitude are defined in terms of Euler angles as
+An initial and desired attitude are defined as
 \begin{gather}
-	R(0) = \text{ROT3}(\ang{90}) \, , \quad R_d = \text{ROT3}(\ang{0})=I \, .
+	R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \, , \quad R_d = \text{ROT3}(\ang{0})=I \, .
 \end{gather}                                
-This results in the sensor performing a \ang{90} yaw rotation about the vertical axis of the spherical joint.
-The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term and the following parameters
-\begin{gather*}
-	k_R = 0.4 \, , \quad k_\Omega = 0.7 \, , \quad c = 0.1 \, ,\quad \alpha = 8 \, , \quad k_\Delta = 0.05 \, .
-\end{gather*}
+This results in the UAV performing a \ang{90} yaw rotation about the vertical axis of the spherical joint and the constrained region is on the shortest path connecting $R_0$ and $R_d$. 
+The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term and the following parameters: \(k_R = 0.4, k_\Omega = 0.7 ,c = 0.1 , \alpha = 8 \text{ and } k_\Delta = 0.05\).
+
 \begin{figure} 
@@
 The experimental results are shown in~\Cref{fig:exp}.
-Overall, it behaves as the numerical simulations predicted.
-The attitude errors asymptotically converge to zero. 
-In addition, as the constraint is neared an out-of-plane moment is used to avoid the constrained region.
-An increased gain of the adaptive update law would improve the final steady state error performance.
+The attitude error asymptotically converges to zero. 
+The hexrotor avoids the constrained region illustrated by the circular cone in\cref{fig:traj_exp}, by rotating around the boundary of the constraint. 
+This verifies that the proposed control system exhibits the desired performance in the experimental setting as well. 
 A video clip showing the attitude manuever is available \url{https://youtu.be/dsmAbwQram4}.
-\section{Conclusion}\label{sec:conclusion}
-We have developed a geometric adaptive control system which incorporates state inequality constraints on \SO.
-The presented control system is developed directly on \SO and avoids singularities and ambiguities that are inherent to attitude parameterizations.
-An adaptive control system is developed to asymptotically converge to a desired attitude while avoiding constraints in the presence of disturbances.
+\section{Conclusions}\label{sec:conclusions}
+We have developed a geometric adaptive control system which incorporates state inequality constraints on \(\SO\).
+The presented control system is developed directly on \(\SO\) and it avoids singularities and ambiguities that are inherent to attitude parameterizations.
+The attitude configuration error is augmented with a barrier function to avoid the constrained region, and an adaptive control law is proposed to cancel the effects of uncertainties. 
+The stability of the proposed control system is analyzed mathematically rigorously.
 In addition we have demonstrated the control system via numerical simulation and hardware experiments on a hexrotor UAV.
@@
 \subsection{Proof of~\Cref{prop:config_error}}\label{proof:config_error}
-The proof of~\cref{item:prop_era_upbound} is available in~\cite{lee2011a}.
-To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a locally positive definite function about \( R = R_d \)~\cite{bullo2004}.
+To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a positive definite function about \( R = R_d \)~\cite{bullo2004}.
 The constraint angle is assumed \( \ang{0} \leq \theta \leq \ang{90} \) such that \( 0 \leq \cos \theta \).
@@
 for all \( R \in \SO \). 
-As a result, the negative logarithm is always positive, \(1 < B\)
-The product~\cref{eqn:psi} is composed of two positive terms and is therefore also positive definite, and has a single critical point at \( R = R_d \).
+As a result, its negative logarithm is always positive and from~\cref{eqn:B}, \(1 < B\).
+The error function \( \Psi = A B \) is composed of two positive terms and is therefore also positive definite, and it is minimized at \( R = R_d \).
 
@@
 The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
+The proof \( A(R) \) in of~\cref{item:prop_era_upbound} is available in~\cite{lee2011a}.
 
@@
 \begin{gather*}
-	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} \, ,
+	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} , \,
 	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} \, .
@@
 \end{align*}
+This shows~\cref{eqn:eW_dot}.
 \subsection{Proof of~\Cref{prop:att_control}}\label{proof:att_control}
@@
 	\end{gather}
-	From~\cref{item:prop_psi_psd}, we obtain
-	\begin{gather*}
-		V \geq 0 \, .
-	\end{gather*}
+	From~\cref{item:prop_psi_psd} of~\Cref{prop:config_error}, \(V \geq 0 \).
 	Using~\cref{eqn:eW_dot,eqn:psi_dot} with \( \Delta = 0 \), the time derivative of \( V \) is given by
@@
 	\end{align}
-	Since \( V \) is positive definite and \( \dot{V} \) is negative definite this implies that the zero equilibrium point \( e_R, e_\Omega \) is asymptotically stable.
-
+	Since \( V \) is positive definite and \( \dot{V} \) is negative semi-definite, the zero equilibrium point \( e_R, e_\Omega \) is stable in the sense of Lyapunov.
+	The Lyapunov function is non-increasing, therefore \( \lim_{t\to\infty} \norm{e_\Omega} = 0 \) and \( \norm{e_R} \) is uniformly bounded.
+	One can show that \( \norm{\ddot{e}_\Omega} \) is bounded.
+	From Barbalat's Lemma, it follows \( \lim_{t\to\infty}\norm{\dot{e}_\Omega} = 0 \)~\cite[Lemma 8.2]{khalil1996}.
 \subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
-	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
-	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
-	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
-	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
-	We know that \( B \to \infty \) as the constraint is neared. 
-	We assume that \( B > \psi \) which implies that \( A < 1 \).
-	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
-	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
-	This shows~\cref{eqn:A_bound,eqn:B_bound}.
+%	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
+%	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
+%	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
+%	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
+%	We know that \( B \to \infty \) as the constraint is neared. 
+%	We assume that \( B > \psi \) which implies that \( A < 1 \).
+%	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
+%	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
+	The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
+	This implies that that both \( A(R) \) and \( B(R) \) are also bounded which shows~\cref{eqn:A_bound,eqn:B_bound}.
 
@@
 	If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
-	This implies that the zero equilibrium \( e_R, e_\Omega\) is asymptotically stable. 
+	This implies that the Lyapunov function \( V \) is non-increasing and bounded from below.
+	Furthermore, since \( V \) is nonincreasing the disturbance error \( e_\Delta\) is bounded.
+	Since \( \dot{V} \) is uniformly continuous in time this implies that the zero equilibrium \( e_R, e_\Omega\) is stable in the sense of Lyapunov
 	The domain \( D \) does that include the undesired equilibria and ensures that as \( e_R \to 0 \) the attitude also converges \( R \to R_d \).
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-09-26 ACC16.2.tex
correcting errors and implementing dr. lee suggestions

@@
 In addition, we develop an adaptive update law that enables attitude stabilization in the presence of unknown disturbances. 
-We demonstrate the effectiveness of the control system through numerical simulation and experimental results on a hexrotor UAV.
+We demonstrate the effectiveness of the control system through numerical simulation and experimental results.
 
@@
 One distinctive feature of the attitude dynamics of rigid bodies is that it evolves on a nonlinear manifold.
-The three-dimensional special orthogonal group, namely \( \SO \), is the set of \( 3 \times 3 \) orthogonal matrices whose determinant is one.
+The three-dimensional special orthogonal group, or \( \SO \), is the set of \( 3 \times 3 \) orthogonal matrices whose determinant is one.
 This configuration space is non-Euclidean and yields unique stability properties which are not observable on a linear space.
 For example, it is impossible to achieve global attitude stabilization using continuous time-invariant feedback~\cite{bhat2000}.
-Attitude control is typically studied using a variety of attitude parameterizations, such as Euler angles or quaternions~\cite{shuster1993}.
 
@@
 % discuss issues with parameterizations
+
+Attitude control is typically studied using a variety of attitude parameterizations, such as Euler angles or quaternions~\cite{shuster1993}.
 All attitude parameterizations fail to represent the nonlinear configuration space both globally and uniquely~\cite{chaturvedi2011a}.
@@
 These attitude representations are not suitable for large angular slews.
-In order to avoid singularities, the designer must carefully switch the chosen Euler angle sequence based on the operating region.
-Another option is to artificially limit the operating region of the rigid body.
+%In order to avoid singularities, the designer must carefully switch the chosen Euler angle sequence based on the operating region.
+%Another option is to artificially limit the operating region of the rigid body.
 This ensures the system operates in a region free from singularities but limits the performance capabilities and ability to perform arbitrarily large angular maneuvers.
@@
 As a result, any physical attitude is represented by a pair of antipodal quaternions on the three-sphere.
-An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
+%An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
 During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}, where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.
@@
 % Previous potential function approach - developed using att parameterizations - singularities/ambiguities
-Artifical potential functions are commonly used to handle kinematic constraints for a wide range of problems in robotics.
-The goal is the design of an attractive function which parameterizes the distance to the desired state.
-Similarly, a repulsive function is constructed such that the system is directed outward from the constraints. 
+Artificial potential functions are commonly used to handle kinematic constraints for a wide range of problems in robotics.
+The goal is the design of an attractive function which drives the system towards the desired state.
+Similarly, a repulsive function is constructed such that the system is directed away from the constraints. 
 The superposition of the these functions allows one to apply standard feedback control schemes for stabilization and tracking.
@@
 
-We develope a new configuration error function on \SO with a logarithmic barrier function to avoid constrained regions.
+We develop a new configuration error function on \SO with a logarithmic barrier function to avoid constrained regions.
 We present a mathematically rigorous analysis to guarantee stability of the proposed control system.
@@
 Consider the attitude dynamics of a rigid body. 
-We define an inertial reference frame and a body-fixed frame fixed to the center of mass. 
+We define an inertial reference frame and a body frame whose origin is at the center of mass and aligned with the principle directions of the body. 
 The configuration manifold of the attitude dynamics is the special orthogonal group:
@@
 We assume that the external disturbance is expressed by $W(R,\Omega)\Delta$, where $W(R,\Omega):\SO\times\R^{3}\rightarrow \R^{3\times p}$ is a known function of the attitude and the angular velocity.
-The disturbance is represented by $\Delta\in\R^{p}$ is an unknown, but fixed uncertain parameter.
+The disturbance is represented by $\Delta\in\R^{p}$ and is an unknown, but fixed uncertain parameter.
 In addition, we assume that a bound on \( W(R, \Omega) \text{ and } \Delta \) is known and given by
@@
 Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\R^n$ and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively.
-The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A}_F = \sqrt{\tr{A^T A}} \).
-This results in \( \norm{A} \leq \norm{A}_F \leq \sqrt{r}\norm{A} \), where \( r \) is the rank of A.
+The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A} \leq \norm{A}_F = \sqrt{\tr{A^T A}} \leq \sqrt{r} \norm{A} \).
 
@@
 This configuration error function, \( \Psi : \Q \times \Q \to \R \), is a smooth and proper positive definite function that measures the error between the current configuration and a desired configuration.
-Once an appropriate configuration error function is chosen, one can then define a configuration error vector and a velocity error vector in the tangent space \( \mathsf{T}_q \Q \) through use of the derivatives of \( \Psi \)~\cite{bullo2004}.
+Once an appropriate configuration error function is chosen, one can then define a configuration error vector and a velocity error vector in the tangent space \( \mathsf{T}_q \Q \) through the derivatives of \( \Psi \)~\cite{bullo2004}.
 With the configuration error function and vectors the remaining procedure is analogous to nonlinear control design on Euclidean vector spaces.
@@
 
-\Cref{eqn:psi} is composed of an attractive term \( A (R) \) toward the desired attitude and a repulsive term \( B(R) \) away from the undesired direction \( R^T v \).
+\Cref{eqn:psi} is composed of an attractive term, \( A (R) \), toward the desired attitude and a repulsive term, \( B(R) \), away from the undesired direction \( R^T v \).
 The attractive error function has been used for attitude control on \SO.
@@
 Barrier functions are typically used in optimal control and motion planning applications.
-A visualization of the configuration error function is presented in~\cref{fig:config_error}.
-\Cref{fig:avoid_errro} illustrated that as the boundary of the constraint in is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
+A visualization of the configuration error function is presented in~\cref{fig:config_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
 We use the scale factor~\(\frac{1}{1+\cos \theta} \) to ensure that \( \Psi \) remains positive definite.
@@
 
-While\cref{eqn:B} represents a single inequality constraint given as~\cref{eqn:constraint}, it is readily generalized to multiple constraints of an arbitrary form. 
+While~\cref{eqn:B} represents a single inequality constraint given as~\cref{eqn:constraint}, it is readily generalized to multiple constraints of an arbitrary form. 
 For example, the configuration error function for multiple constraints can be formulated as $\Psi=A[1+\sum_i C_i]$, where $C_i$ has the form of $C_i=B-1$ for the $i$-th constraint. 
@@
 	\end{gather}
-	Then the zero equilibrium of the attitude errors \( \parenth{e_R, e_\Omega} \) is asymptotically stable, i.e., \(e_R, e_\Omega \to 0 \) as \( t \to \infty \).
+	Then the zero equilibrium of the attitude errors \( \parenth{e_R, e_\Omega} \) is stable, i.e., \(e_R, e_\Omega \to 0 \) as \( t \to \infty \).
 \end{prop}
@@
 	\begin{gather}
-		\norm{A} < c_A \, , \label{eqn:A_bound}\\
-		\norm{B} < c_B \, . \label{eqn:B_bound}
+		\norm{A} < c_A \, , \quad \norm{B} < c_B \, . \label{eqn:AB_bound}
 	\end{gather}
@@
 \begin{proof}
-See~\Cref{proof:eR_dot_bound}
+See~\Cref{proof:eR_dot_bound}.
 \end{proof}
@@
 \end{gather*}
-A body fixed sensor is defined as
-\begin{gather*}
-	r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix} \, ,
-\end{gather*}
-while multiple inequality constraints are defined in~\Cref{tab:constraints}.
-The simulation parameters are chosen to similar those found in~\cite{lee2011b}.
-We increase the size of the constraint regions to create a more challenging scenario for the control system.
+A body fixed sensor is defined as \(r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix}\), while multiple inequality constraints are defined in~\Cref{tab:constraints}.
+The simulation parameters are chosen to be similar to those found in~\cite{lee2011b}, howver we increase the size of the constraint regions to create a more challenging scenario for the control system.
+The initial state is defined as \(R_0 =  \exp(\ang{225} \times \frac{\pi}{180} \hat{e}_3), \Omega_0 = 0\). 
+The desired state is \( (R_d = I,\Omega_d = 0)\).
 \begin{table}[htbp]
@@
 \end{table}
-The initial and desired states are defined as
-\begin{gather*}
-	R_0 =  \exp(\ang{225} * \frac{\pi}{180} \hat{e}_3)\, , \quad \Omega_0 = 0 \, ,\quad	R_d = I \, , \quad \Omega_d = 0 \, .
-\end{gather*}
-
 We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}.
-We assume a fixed disturbance of 
-\begin{gather*}
-	\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \, ,
-\end{gather*}
-with the function \( W(R,\Omega) = I \).
+We assume a fixed disturbance of \(\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \), with the function \( W(R,\Omega) = I \).
 This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
@@
 The initial attitude is represented with the green circle while the final attitude is marked with a green \(\times\).
-The inequality constraints from~\cref{tab:constraints} are depicted as red cones, where the cone half angle is \( \theta \).
+The inequality constraints from~\Cref{tab:constraints} are depicted as red cones, where the cone half angle is \( \theta \).
 The control system is able to asymptotically converge to zero attitude error.
@@
 These results show that the proposed geometric adaptive approach is critical to attitude stabilization in the presence of state constraints and disturbances.
-
 \section{Experiment on Hexrotor UAV}
-
-A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory(FDCL) at the George Washington University (CITE EVAN PAPER).
+A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory(FDCL) at the George Washington University~\cite{kaufman2014}.
 The UAV is composed of three pairs of counter-rotating propellers. 
@@
 
-The hexrotor UAV is composed of the following hardware:
+The hexrotor UAV, shown in~\cref{fig:hexrotor}, is composed of the following hardware:
 \begin{itemize}
@@
 \begin{figure}
-	\includegraphics[width = \columnwidth]{hexrotor}
+	\centering
+	\includegraphics[width = 0.7\columnwidth]{hexrotor}
 	\caption{Attitude control testbed~\label{fig:hexrotor}}
@@
 We define an obstacle in the inertial frame as \( v = \begin{bmatrix} \frac{1}{\sqrt{2}} & \frac{1}{\sqrt{2}} & 0\end{bmatrix}^T \) with \( \theta = \ang{12} \).
-An initial and desired attitude are defined as
-\begin{gather}
-	R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \, , \quad R_d = \text{ROT3}(\ang{0})=I \, .
-\end{gather}                                
+An initial state is defined as \(R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \), while the desired state is \(R_d = \text{ROT3}(\ang{0})=I \).
 This results in the UAV performing a \ang{90} yaw rotation about the vertical axis of the spherical joint and the constrained region is on the shortest path connecting $R_0$ and $R_d$. 
 The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term and the following parameters: \(k_R = 0.4, k_\Omega = 0.7 ,c = 0.1 , \alpha = 8 \text{ and } k_\Delta = 0.05\).
-
 \begin{figure} 
@@
 The attitude error asymptotically converges to zero. 
-The hexrotor avoids the constrained region illustrated by the circular cone in\cref{fig:traj_exp}, by rotating around the boundary of the constraint. 
+The hexrotor avoids the constrained region illustrated by the circular cone in~\cref{fig:traj_exp}, by rotating around the boundary of the constraint. 
 This verifies that the proposed control system exhibits the desired performance in the experimental setting as well. 
@@
 The attitude configuration error is augmented with a barrier function to avoid the constrained region, and an adaptive control law is proposed to cancel the effects of uncertainties. 
-The stability of the proposed control system is analyzed mathematically rigorously.
-In addition we have demonstrated the control system via numerical simulation and hardware experiments on a hexrotor UAV.
+We show the stability of the  proposed control system through a rigorous mathematically analysis.
+In addition, we have demonstrated the control system via numerical simulation and hardware experiments on a hexrotor UAV.
 A novel feature of this control is that it is computed autonomously on-board the UAV.
-This is in constrast to many state constrained attitude control systems which require an a priori attitude trajectory to be calculated. 
+This is in contrast to many state constrained attitude control systems which require an a priori attitude trajectory to be calculated. 
 The presented method is simple, efficient and ideal for hardware implementation on embedded systems.
@@
 This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \) .
+Since we assume the system will not operate in violation of the constraints, the addition of the barrier function does not add additional critical points to the control system.
 The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
 The proof \( A(R) \) in of~\cref{item:prop_era_upbound} is available in~\cite{lee2011a}.
-
 \subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
@@
 A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and appplying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
-
-The time-derivative of the angular velocity error, \( e_\Omega \), is rearranged from~\cref{eqn:Wdot} as 
+We show~\cref{eqn:eW_dot} by rearranging~\cref{eqn:Wdot} as 
 \begin{align*}
@@
 \end{align*}
-This shows~\cref{eqn:eW_dot}.
 \subsection{Proof of~\Cref{prop:att_control}}\label{proof:att_control}
@@
 	The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
-	This implies that that both \( A(R) \) and \( B(R) \) are also bounded which shows~\cref{eqn:A_bound,eqn:B_bound}.
+	This implies that that both \( A(R) \) and \( B(R) \) are also bounded which shows~\cref{eqn:AB_bound}.
 
@@
 
-\subsection{Proof of~\cref{prop:adaptive_control}}\label{proof:adaptive_control}
+\subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}
 	Consider the Lyapunov function \( V \) given by

### 2015-09-26 ACC16.2.tex
reduced down to 8 pages

@@
 \usepackage{ieee_packages}
+\newcommand{\squeezeup}{\vspace{-2.5mm}}
 
@@
 %Another option is to artificially limit the operating region of the rigid body.
-This ensures the system operates in a region free from singularities but limits the performance capabilities and ability to perform arbitrarily large angular maneuvers.
+%This ensures the system operates in a region free from singularities but limits the performance capabilities and ability to perform arbitrarily large angular maneuvers.
 Quaternions do not have singularities but they double cover the special orthogonal group.
@@
 %An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
-During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}, where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.
+During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}.
+%, where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.
 
@@
 These systems require retargeting while avoiding direct exposure to sunlight or other bright objects.
-Determining a satisfactory attitude control maneuver in the presence of state constraints is a challenging task.
+%Determining a satisfactory attitude control maneuver in the presence of state constraints is a challenging task.
 The removal of constrained regions from the rotational configuration space results in a \textit{nonconvex} region.
@@
 Artificial potential functions are commonly used to handle kinematic constraints for a wide range of problems in robotics.
-The goal is the design of an attractive function which drives the system towards the desired state.
-Similarly, a repulsive function is constructed such that the system is directed away from the constraints. 
+The goal is the design of attractive and repulsive terms which drive the system toward or away from a certain state, respectively.
+%The goal is the design of an attractive function which drives the system towards the desired state.
+%Similarly, a repulsive function is constructed such that the system is directed away from the constraints. 
 The superposition of the these functions allows one to apply standard feedback control schemes for stabilization and tracking.
@@
 These approaches were developed using attitude parameterizations, namely Euler angles and quaternions.
-By characterizing the attitude both globally and uniquely \SO, we completely avoid issues associated with local parameterizations of the configuration manifold.
+By characterizing the attitude both globally and uniquely \(\SO\), we completely avoid issues associated with local parameterizations of the configuration manifold.
 
-In short, the main contribution of this paper is developing an adaptive attitude control scheme in the presence of attitude inequality constraint on \SO.
-We apply a potential function based approach developed directly on the nonlinear manifold \SO.
+In short, the main contribution of this paper is developing an adaptive attitude control scheme in the presence of attitude inequality constraint on \(\SO\).
+We apply a potential function based approach developed directly on the nonlinear manifold \(\SO\).
 Our approach avoids the issues of attitude parameterizations, such as kinematic singularities and ambiguities, and is geometrically exact.
@@
 Instead of calculating a priori trajectories, as in the geometric and randomized approaches, our approach results in a closed-loop attitude control system.
-This makes it ideal for on-board implentation on UAV or spacecraft systems.
+This makes it ideal for on-board implementation on UAV or spacecraft systems.
 In addition, unlike previous approaches our control system can handle an arbitrary number of constrained regions without modification. 
-Finally, a rigous Lyapunov analysis guarantees the stability of the proposed control system, rather than probablistic convergence properties of the randomized approach.
+Finally, a rigorous Lyapunov analysis guarantees the stability of the proposed control system.
+%rather than probablistic convergence properties of the randomized approach.
 
-We develop a new configuration error function on \SO with a logarithmic barrier function to avoid constrained regions.
+We develop a new configuration error function on \(\SO\) with a logarithmic barrier function to avoid constrained regions.
 We present a mathematically rigorous analysis to guarantee stability of the proposed control system.
@@
 \Cref{eqn:psi} is composed of an attractive term, \( A (R) \), toward the desired attitude and a repulsive term, \( B(R) \), away from the undesired direction \( R^T v \).
-The attractive error function has been used for attitude control on \SO.
+The attractive error function has been used for attitude control on \(\SO\).
 The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}.
@@
 We extend the results of the previous section with the addition of a fixed but unknown disturbance \( \Delta \).
-This scenario is typical of many mechanical systems and represents unmodeled dynamics or external moments acting on the system.
-For example, Earth orbiting spacecraft typically experience both a torque due to a gravitational gradient as well as external torques to due solar radiation pressure.
+This scenario is typical of many mechanical systems and represents unmodelled dynamics or external moments acting on the system.
+For example, Earth orbiting spacecraft typically experience both a torque due to a gravitational gradient.
+% as well as external torques to due solar radiation pressure.
 Aerial vehicles will similarly experience external torques due to air currents or turbulence.
@@
 \end{figure}
-
 \begin{figure} 
@@
 The inequality constraints from~\Cref{tab:constraints} are depicted as red cones, where the cone half angle is \( \theta \).
-The control system is able to asymptotically converge to zero attitude error.
+The control system is able to asymptotically converge to zero attitude error 
 In addition, the estimate of the disturbance converges to the the true value.
@@
 The UAV is composed of three pairs of counter-rotating propellers. 
-Typical quadrotor UAVs are composed of four or more co-planar propellers.
-As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
-For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
-Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
-This allows the hexrotor to impart a force in any direction and a moment about any axis.
+%Typical quadrotor UAVs are composed of four or more co-planar propellers.
+%As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
+%For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
+%Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
+The propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
+%This allows the hexrotor to impart a force in any direction and a moment about any axis.
 
@@
 	\item Onboard ODROID XU3 computer module.
-	\item VectorNav VN100 IMU operating at over \SI{100}{\hertz} via TTL serial 
-	\item Brushless DC Motors powered by BL-Ctrl-2.0 speed controllers via I2C.
-	\item Position and attitude over WiFi (TCP) communication from Vicon motion capture system via host computer.
-	\item Commands sent over WiFi through the terminal (SSH) to the code running onboard the hexrotor. 
+	\item VectorNav VN100 IMU operating via TTL serial %at over \SI{100}{\hertz} 
+	\item BLDC motors with BL-Ctrl-2.0 ESC via I2C.
+	\item Position and attitude over WiFi (TCP) communication from Vicon motion capture system.
+	\item Commands sent over WiFi to  onboard controller. 
 \end{itemize}
@@
 	The bound on \( e_{R_A} \) is given in~\cref{eqn:psi_lower_bound} while \( e_{R_B} \) arises from the definition of the cross product \( \norm{a \times b} = \norm{a} \norm{b} \sin \theta \).
-
 \subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}

### 2015-09-27 ACC16.2.tex
updates from dr. lee

@@
 
-\usepackage{ieee_packages}
+\usepackage{ieee_packages,graphicx}
 \newcommand{\squeezeup}{\vspace{-2.5mm}}
@@
 \begin{document}
+\allowdisplaybreaks
 
@@
 \begin{abstract}
-We present a new geometric adaptive control system with state inequality constraints for the attitude dynamics of a rigid body.
-We globally express the attitude dynamics and control system using the special orthogonal group. 
-This representation is geometrically exact and avoids singularities and ambiguities of other attitude parameterizations, such as Euler angles and quaternions.
+This paper presents a new geometric adaptive control system with state inequality constraints for the attitude dynamics of a rigid body.
 The control system is designed such that the desired attitude is asymptotically stabilized, while the controlled attitude trajectory avoids undesired regions defined by an inequality constraint.
 In addition, we develop an adaptive update law that enables attitude stabilization in the presence of unknown disturbances.
-We demonstrate the effectiveness of the control system through numerical simulation and experimental results.
-
+The attitude dynamics and the proposed control systems developed on the special orthogonal group such that singularities and ambiguities of other attitude parameterizations, such as Euler angles and quaternions are completely avoided.
+The effectiveness of the proposed control system are demonstrated through numerical simulations and experimental results.
 \end{abstract}
@@
 \section{Introduction}\label{sec:intro}
-Many researchers have focused on the study of the attitude dynamics of a rigid body~\cite{hughes2004,wertz1978}.
-Rigid body attitude control is an important problem for aerospace vehicles, ground and underwater vehicles, as well as robotic systems.
+
+Rigid body attitude control is an important problem for aerospace vehicles, ground and underwater vehicles, as well as robotic systems~\cite{hughes2004,wertz1978}.
 One distinctive feature of the attitude dynamics of rigid bodies is that it evolves on a nonlinear manifold.
@@
 The algorithm then seeks an intermediate point such that the control scheme can be applied for each segment without violation of the constraints.
-While the geometric method is conceptually simple it is difficult to generalize for an arbitrary number of constraints.
-In addition, this geometric type of approach is only applicable to problems where the selection of intermediate points are computationally feasible
+While the geometric method is conceptually simple, it is difficult to generalize for an arbitrary number of constraints.
+In addition, this geometric type of approach is only applicable to problems where the selection of intermediate points are computationally feasible.
 
@@
 Artificial potential functions have previously been applied to the attitude control problem in~\cite{lee2011b,mcinnes1994}.
-These approaches were developed using attitude parameterizations, namely Euler angles and quaternions.
-By characterizing the attitude both globally and uniquely \(\SO\), we completely avoid issues associated with local parameterizations of the configuration manifold.
+These approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by the singularities of minimal representations or the ambiguity of quaternions.
 
-In short, the main contribution of this paper is developing an adaptive attitude control scheme in the presence of attitude inequality constraint on \(\SO\).
+%By characterizing the attitude both globally and uniquely \(\SO\), we completely avoid issues associated with local parameterizations of the configuration manifold.
+
+This paper is focused on developing an adaptive attitude control scheme in the presence of attitude inequality constraint on \(\SO\).
 We apply a potential function based approach developed directly on the nonlinear manifold \(\SO\).
-Our approach avoids the issues of attitude parameterizations, such as kinematic singularities and ambiguities, and is geometrically exact.
-Our approach is also computationally efficient and able to handle uncertain disturbances. 
+By characterizing the attitude both globally and uniquely \(\SO\), our approach avoids the issues of attitude parameterizations, such as kinematic singularities and ambiguities, and is geometrically exact.
+A new configuration error function on \(\SO\) with a logarithmic barrier function is proposed to avoid constrained regions.
 Instead of calculating a priori trajectories, as in the geometric and randomized approaches, our approach results in a closed-loop attitude control system.
@@
 In addition, unlike previous approaches our control system can handle an arbitrary number of constrained regions without modification.
-Finally, a rigorous Lyapunov analysis guarantees the stability of the proposed control system.
+
+Furthermore, we formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances.
+The stability of the proposed control systems are verified via mathematically rigorous Lyapunov analysis on $\SO$.
+In short, the proposed attitude control system in the presence of inequality constraints is computationally efficient and able to handle uncertain disturbances.
+The effectiveness of this new approach is illustrated via numerical simulation and experimental results.% on a hexrotor aerial vehicle.
+
+%Our approach 
+%Finally, a rigorous Lyapunov analysis guarantees the stability of the proposed control system.
 %rather than probablistic convergence properties of the randomized approach.
 
-We develop a new configuration error function on \(\SO\) with a logarithmic barrier function to avoid constrained regions.
-We present a mathematically rigorous analysis to guarantee stability of the proposed control system.
-In addition, we formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances.
-We demonstrate the effectiveness of this new approach via numerical simulation and experimental results on a hexrotor aerial vehicle.
+%We present a
+
 %In this work, we develop a geometric adaptive controller on \(\SO\) to reorient a rigid body in the presence of state inequality constraints.
@@
 \begin{align*}
-	\SO = \{R\in\R^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\} \, ,
+	\SO = \{R\in\R^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\} ,
 \end{align*}
@@
 \begin{gather}
-	J\dot\Omega + \Omega\times J\Omega = u+W(R,\Omega)\Delta \, ,\label{eqn:Wdot}\\
-	\dot R = R\hat\Omega \, ,\label{eqn:Rdot}
+	J\dot\Omega + \Omega\times J\Omega = u+W(R,\Omega)\Delta ,\label{eqn:Wdot}\\
+	\dot R = R\hat\Omega ,\label{eqn:Rdot}
 \end{gather}
@@
 \begin{equation}
-	\norm{W} \leq B_W \, , \quad \norm{\Delta} \leq B_\Delta \,. \label{eqn:W_bound}
+	\norm{W} \leq B_W , \quad \norm{\Delta} \leq B_\Delta \,. \label{eqn:W_bound}
 \end{equation}
@@
 \begin{align}
-	r^T R^T v \leq \cos \theta \, , \label{eqn:constraint}
+	r^T R^T v \leq \cos \theta , \label{eqn:constraint}
 \end{align}
 where we assume \( \ang{0} \leq \theta \leq \ang{90}  \) is the required minimum angular separation between \( r \) and \( R^T v \).
+
 The objective is to a determine a control input \( u \) that stabilizes the system from an initial attitude \( R_0 \) to a desired attitude \( R_d \) while ensuring that~\cref{eqn:constraint} is always satisfied.
@@
 \section{Attitude Control on $\SO$ with Inequality Constraints}
+
 The first step in designing a control system on a nonlinear manifold \( \Q \) is the selection of a proper configuration error function.
@@
 
-A new configuration error function is proposed for attitude control in the presence of state inequality constraints.
-We extend the form used in~\cite{bullo2004,lee2011a} for attitude control on \(\SO\) with the addition of a logarithmic barrier function.
-We use the configuration error function to develop a nonlinear geometric attitude controller for the stabilization of a general rigid body. 
-A smooth control system is first developed for the no disturbance case and then extended to include an adaptive update law for stabilization in the presence of unknown disturbances.
+To handle the attitude inequality constraint, we propose a new attitude configuration error function.
+More explicitly, we extend the trace form used in~\cite{bullo2004,LeeITCST13} for attitude control on \(\SO\) with the addition of a logarithmic barrier function.
+Based on the proposed configuration error function,  nonlinear geometric attitude controllers are constructed.
+A smooth control system is first developed assuming that there is  no disturbance,and then it is extended to include an adaptive update law for stabilization in the presence of unknown disturbances.
+The proposed attitude configuration error function and several properties are summarized as follows.
 
 \begin{prop}[Attitude Error Function] \label{prop:config_error}
-We assume a desired attitude command \( ( R_d, \Omega_d = 0 ) \), the current attitude and angular velocity \( ( R, \Omega) \), and a state constraint~\cref{eqn:constraint} are given.
-We define an attitude error function \( \Psi : \SO \times \SO \to \R \), and attitude error vector \( e_R \in \R^3 \), and an angular velocity error vector \( e_\Omega \in \R^3 \) as follows:
+%We assume a desired attitude command \( ( R_d, \Omega_d = 0 ) \), the current attitude and angular velocity \( ( R, \Omega) \), and a state constraint~\cref{eqn:constraint} are given.
+Define an attitude error function \( \Psi : \SO \times \SO \to \R \), and attitude error vector \( e_R \in \R^3 \), and an angular velocity error vector \( e_\Omega \in \R^3 \) as follows:
 \begin{gather}
-	\Psi(R) = A(R) B(R) \, , \label{eqn:psi} \\
-	e_R = e_{R_A} B + A e_{R_B} \, , \label{eqn:eR} \\
-	e_\Omega = \Omega \, , \label{eqn:eW}
+	\Psi(R) = A(R) B(R) , \label{eqn:psi} \\
+	e_R = e_{R_A} B + A e_{R_B} , \label{eqn:eR} \\
+	e_\Omega = \Omega , \label{eqn:eW}
 \end{gather}
@@
 \begin{gather}
-	A(R) = \frac{1}{2} \tr{G \left( I - R_d^T R\right)} \, , \label{eqn:A} \\
-	B(R) = 1 - \frac{1}{\alpha} \ln \left( \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta}\right) \, . \label{eqn:B} \\
-	e_{R_A} = \frac{1}{2} \parenth{G R_d^T R - R^T R_d G} ^ \vee \, , \label{eqn:eRA} \\
-	e_{R_B} = \frac{ \left( R^T v\right)^\vee r}{\alpha \left(r^T R^T v - \cos \theta \right)} \, . \label{eqn:eRB} 
+	A(R) = \frac{1}{2} \tr{G \left( I - R_d^T R\right)} , \label{eqn:A} \\
+	B(R) = 1 - \frac{1}{\alpha} \ln \left( \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta}\right) . \label{eqn:B} \\
+	e_{R_A} = \frac{1}{2} \parenth{G R_d^T R - R^T R_d G} ^ \vee , \label{eqn:eRA} \\
+	e_{R_B} = \frac{ \left( R^T v\right)^\vee r}{\alpha \left(r^T R^T v - \cos \theta \right)} . \label{eqn:eRB} 
 \end{gather}	
@@
 \begin{enumerate}[(i)]
-	\item \label{item:prop_psi_psd} \(\Psi\) is locally positive definite about \( R = R_d\)
+	\item \label{item:prop_psi_psd} \(\Psi\) is positive definite about \( R = R_d\)
 	\item \label{item:prop_era}The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
 	\begin{align}
-		\dirDiff{A}{R} &= \eta \cdot e_{R_A} \, .
+		\dirDiff{A}{R} &= \eta \cdot e_{R_A} .
 	\end{align}
@@
 	\begin{align}
-		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}} \, .
+		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}} .
 	\end{align}
-	\item \label{item:prop_crit}The critical points of \( \Psi \), where \( e_R = 0\), are \( \braces{R_d} \cup \braces{R = R_d \exp(\pi \hat{s})  \text{ for } s \in \braces{e_1, e_2, e_3} \vert R^T v = \pm r }\).
+	\item \label{item:prop_crit}The critical points of \( \Psi \) are $R_d$, and $R_d \exp(\pi \hat{s})$ for $s \in \braces{e_1, e_2, e_3}$ satisfying $R^T v = \pm r$.
 	\item \label{item:prop_era_upbound}An upper bound of \( \norm{e_{R_A}} \) is given as:
 	\begin{align}
-		\norm{e_{R_A}}^2 \leq \frac{\Psi}{b_1} \, , \label{eqn:psi_lower_bound}
+		\norm{e_{R_A}}^2 \leq \frac{\Psi}{b_1} , \label{eqn:psi_lower_bound}
 	\end{align}
@@
 	\begin{align*}
-		h_1 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} \, ,\\
-		h_2 &= \min\braces{\parenth{g_1 -g_2}^2,\parenth{g_2 -g_3}^2 , \parenth{g_3 -g_1}^2} \, ,\\
-		h_3 &= \min\braces{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} \, .				
+		h_1 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
+		h_2 &= \min\braces{\parenth{g_1 -g_2}^2,\parenth{g_2 -g_3}^2 , \parenth{g_3 -g_1}^2} ,\\
+		h_3 &= \min\braces{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2}.		
 	\end{align*}
@@
 
-\Cref{eqn:psi} is composed of an attractive term, \( A (R) \), toward the desired attitude and a repulsive term, \( B(R) \), away from the undesired direction \( R^T v \).
+\Cref{eqn:psi} is composed of an attractive term, \( A (R) \) toward the desired attitude, and a repulsive term, \( B(R) \) from the undesired direction \( R^T v \).
 The attractive error function has been used for attitude control on \(\SO\).
-The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}.
-The desired attitude lies at the minimum of \( A(R) \).
+The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum of \( A(R) \).
 
-In order to incorporate the state inequality constraints we apply a logarithmic barrier term.
+To incorporate the state inequality constraints we apply a logarithmic barrier term.
 Barrier functions are typically used in optimal control and motion planning applications.
@@
 The super position of the attractive and repulsive functions is shown in~\cref{fig:combined_error}.
-The control system follows the direction of the gradient of \( \Psi \) towards the minimum at \( R = R_d \) while avoiding any constrained regions.
+The control system is defined such that the attitude trajectory follows the negative gradient of \( \Psi \) towards the minimum at \( R = R_d \), while avoiding the constrained region.
 \begin{figure} 
 	\centering 
-	\begin{subfigure}[htbp]{0.3\columnwidth} 
+	\begin{subfigure}[htbp]{0.45\columnwidth} 
 		\includegraphics[width=\columnwidth]{attract_error} 
@@
 	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
-	\begin{subfigure}[htbp]{0.3\columnwidth} 
+	\begin{subfigure}[htbp]{0.45\columnwidth} 
 		\includegraphics[width=\columnwidth]{avoid_error} 
 		\caption{Repulsive \( B(R) \)} \label{fig:avoid_error} 
-	\end{subfigure}~
-	\begin{subfigure}[htbp]{0.3\columnwidth} 
+	\end{subfigure}
+	\centering
+	\begin{subfigure}[htbp]{0.45\columnwidth} 
 		\includegraphics[width=\columnwidth]{combined_error} 
@@
 While~\cref{eqn:B} represents a single inequality constraint given as~\cref{eqn:constraint}, it is readily generalized to multiple constraints of an arbitrary form. 
-For example, the configuration error function for multiple constraints can be formulated as $\Psi=A[1+\sum_i C_i]$, where $C_i$ has the form of $C_i=B-1$ for the $i$-th constraint. 
-In this manner, one may enforce multiple state inequality constraints on the control system.
+For example, the configuration error function can be formulated as $\Psi=A[1+\sum_i C_i]$, where $C_i$ has the form of $C_i=B-1$ for the $i$-th constraint. 
+In this manner, one may enforce multiple state inequality constraints, and these are illustrated later at numerical examples.
+
 \begin{prop}[Error Dynamics]\label{prop:error_dyn}
@@
 	\begin{gather}
-		\diff{}{t} \parenth{\Psi} = e_R \cdot e_\Omega \, , \label{eqn:psi_dot}\\
-		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B + e_{R_A} \dot{B} + \dot{A}e_{R_B} + A \dot{e}_{R_B} \, , \label{eqn:eR_dot}\\
-		\diff{}{t} \parenth{e_{R_A}} = E(R, R_d) e_\Omega \, , \label{eqn:eRA_dot} \\
-		\diff{}{t} \parenth{e_{R_B}} = F(R) e_\Omega \, , \label{eqn:eRB_dot} \\
-		\diff{}{t} \parenth{A} = e_{R_A} \cdot e_\Omega \, , \label{eqn:A_dot} \\
-		\diff{}{t} \parenth{B} = e_{R_B} \cdot e_\Omega \, , \label{eqn:B_dot} \\
-		\diff{}{t} \parenth{e_\Omega} = J^{-1} \parenth{-\Omega \times J \Omega + u + W(R, \Omega) \Delta} \, , \label{eqn:eW_dot}
+		\diff{}{t} \parenth{\Psi} = e_R \cdot e_\Omega , \label{eqn:psi_dot}\\
+		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B + e_{R_A} \dot{B} + \dot{A}e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
+		\diff{}{t} \parenth{e_{R_A}} = E(R, R_d) e_\Omega , \label{eqn:eRA_dot} \\
+		\diff{}{t} \parenth{e_{R_B}} = F(R) e_\Omega , \label{eqn:eRB_dot} \\
+		\diff{}{t} \parenth{A} = e_{R_A} \cdot e_\Omega , \label{eqn:A_dot} \\
+		\diff{}{t} \parenth{B} = e_{R_B} \cdot e_\Omega , \label{eqn:B_dot} \\
+		\diff{}{t} \parenth{e_\Omega} = J^{-1} \parenth{-\Omega \times J \Omega + u + W(R, \Omega) \Delta} , \label{eqn:eW_dot}
 	\end{gather}
@@
 	\begin{gather}
-		E(R,R_d) = \frac{1}{2} \parenth{\tr{R^T R_d G}I - R^T R_d G} \, , \label{eqn:E} \\
+		E(R,R_d) = \frac{1}{2} \parenth{\tr{R^T R_d G}I - R^T R_d G} , \label{eqn:E} \\
 		F(R) = \frac{1}{\alpha \parenth{r^T R^T v - \cos \theta}} \left[\parenth{v^T R r} I - R^T v r^T + \right. \nonumber \\
-		\left. \frac{R^T \hat{v} R r v^T R \hat{r}}{\parenth{r^T R^T v - \cos \theta}}\right] \, . \label{eqn:F}
+		\left. \frac{R^T \hat{v} R r v^T R \hat{r}}{\parenth{r^T R^T v - \cos \theta}}\right] . \label{eqn:F}
 	\end{gather}
@@
 	\begin{gather}
-		u = -k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega \, . \label{eqn:nodist_control}
+		u = -k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega . \label{eqn:nodist_control}
 	\end{gather}
-	Then the zero equilibrium of the attitude errors \( \parenth{e_R, e_\Omega} \) is stable, i.e., \(e_R, e_\Omega \to 0 \) as \( t \to \infty \).
+	Then the zero equilibrium of the attitude errors is asymptotically stable, and the inequality constraint is satisfied.
 \end{prop}
@@
 %\begin{align*}
-%	W = k - V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \parenth{\frac{k}{k_R}+ \Psi(R,R_d)} \, .
+%	W = k - V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \parenth{\frac{k}{k_R}+ \Psi(R,R_d)} .
 %\end{align*}
@@
 An adaptive control system is introduced to asymptotically stabilize the system to a desired attitude while ensuring that state constraints are satisfied.
+%We first show several properties of the controlled system.
 
@@
 	\begin{gather}
-		\norm{A} < c_A \, , \quad \norm{B} < c_B \, . \label{eqn:AB_bound}
+		\norm{A} < c_A  , \quad \norm{B} < c_B . \label{eqn:AB_bound}
 	\end{gather}
@@
 	\begin{gather}
-		\norm{E} \leq \frac{1}{\sqrt{2}} \tr{G} \, , \label{eqn:E_bound} \\
-		\norm{F} \leq \frac{\parenth{\beta^2 + 1}\parenth{\beta - \cos \theta}^2 + 1 + \beta^2 \parenth{\beta^2-2}}{\alpha^2 \parenth{\beta-\cos \theta}^4} \, . \label{eqn:F_bound}
+		\norm{E} \leq \frac{1}{\sqrt{2}} \tr{G}  , \label{eqn:E_bound} \\
+		\norm{F} \leq \frac{\parenth{\beta^2 + 1}\parenth{\beta - \cos \theta}^2 + 1 + \beta^2 \parenth{\beta^2-2}}{\alpha^2 \parenth{\beta-\cos \theta}^4} . \label{eqn:F_bound}
 	\end{gather}
@@
 	\begin{gather}
-		\norm{e_{R_A}} \leq \sqrt{\frac{\psi}{b_1}} \, , \label{eqn:eRA_bound} \\
-		\norm{e_{R_B}} \leq \frac{\sin\theta}{\alpha \parenth{\beta - \cos \theta}} \, . \label{eqn:eRB_bound}
+		\norm{e_{R_A}} \leq \sqrt{\frac{\psi}{b_1}}, \label{eqn:eRA_bound} \\
+		\norm{e_{R_B}} \leq \frac{\sin\theta}{\alpha \parenth{\beta - \cos \theta}}. \label{eqn:eRB_bound}
 	\end{gather}
@@
 \begin{gather}
-	\norm{\dot{e}_R} \leq H \norm{e_\Omega} \, ,\label{eqn:eR_bound}
+	\norm{\dot{e}_R} \leq H \norm{e_\Omega} ,\label{eqn:eR_bound}
 \end{gather}
@@
 \begin{gather}
-	H = \norm{B} \norm{E} + 2 \norm{e_{R_A}} \norm{e_{R_B}} + \norm{A}\norm{F}\, . \label{eqn:H}
+	H = \norm{B} \norm{E} + 2 \norm{e_{R_A}} \norm{e_{R_B}} + \norm{A}\norm{F}. \label{eqn:H}
 \end{gather}
@@
 \begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control}
-Given  a desired attitude command \( (R_d, \Omega_d = 0 )\) and positive constants \( k_R, k_\Omega, k_\Delta, c \in \R \), we define a control input \( u \in \R^3\) and an adaptive update law for \( \bar{\Delta} \) as follows:
+Given  a desired attitude command \( (R_d, \Omega_d = 0 )\) and positive constants \( k_R, k_\Omega, k_\Delta, c \in \R \), we define a control input \( u \in \R^3\) and an adaptive update law for the estimated uncertainty \( \bar{\Delta} \) as follows:
 \begin{align}
-	u &= - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - W \bar{\Delta} \, , \label{eqn:adaptive_control} \\
-	\dot{\bar{\Delta}} &= k_\Delta W^T \parenth{e_\Omega + c e_R} \, . \label{eqn:delta_dot}
+	u &= - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - W \bar{\Delta} , \label{eqn:adaptive_control} \\
+	\dot{\bar{\Delta}} &= k_\Delta W^T \parenth{e_\Omega + c e_R} . \label{eqn:delta_dot}
 \end{align}
@@
 \begin{gather}
-	0 < c < \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k-R \lambda_M H} \, , \label{eqn:c_bound}
+	0 < c < \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k-R \lambda_M H} , \label{eqn:c_bound}
 \end{gather}
-  the zero equilibrium of the error vectors \( e_R, e_\Omega\) are asymptotically stable.
+  the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is uniformly bounded.
 \end{prop}
@@
 	\num{-2.50e-5} & \num{1.00e-5} & \num{1.05e-2}
-	\end{bmatrix} \si{\kilo\gram\meter\squared} \, .
+	\end{bmatrix} \si{\kilo\gram\meter\squared} .
 \end{gather*} 
@@
 \begin{gather*}
-	G = \text{diag} \parenth{0.9,1.1,1.0}\, , \quad k_R = 0.4 \, , \quad	k_\Omega = 0.296 \, ,\\
-	c = 1.0 \, , \quad k_\Delta = 0.5 \, , \quad \alpha = 15 \, .
+	G = \text{diag} [0.9,1.1,1.0], \quad k_R = 0.4 , \quad	k_\Omega = 0.296 ,\\
+	c = 1.0 , \quad k_\Delta = 0.5 , \quad \alpha = 15 .
 \end{gather*}
-A body fixed sensor is defined as \(r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix}\), while multiple inequality constraints are defined in~\Cref{tab:constraints}.
+A body fixed sensor is defined as \(r = [1,0,0]\), while multiple inequality constraints are defined in~\Cref{tab:constraints}.
 The simulation parameters are chosen to be similar to those found in~\cite{lee2011b}, howver we increase the size of the constraint regions to create a more challenging scenario for the control system.
+
 The initial state is defined as \(R_0 =  \exp(\ang{225} \times \frac{\pi}{180} \hat{e}_3), \Omega_0 = 0\). 
-The desired state is \( (R_d = I,\Omega_d = 0)\).
-\begin{table}[htbp]
+The desired state is \( R_d = I,\Omega_d = 0\).
+\begin{table}%[htbp]
 \caption{Constraint Parameters~\label{tab:constraints}}
@@
 Constraint Vector (\( v \)) & Angle (\( \theta \)) \\ \hline \hline 
-\(\begin{bmatrix} 0.174 &-0.934 & -0.034 \end{bmatrix}\) & \ang{40} \\ \hline 
-\(\begin{bmatrix} 0 & 0.7071 & 0.7071 \end{bmatrix}\) & \ang{40} \\ \hline 
-\(\begin{bmatrix} -0.853 & 0.436 & -0.286 \end{bmatrix}\) & \ang{40} \\ \hline 
-\(\begin{bmatrix} -0.122 -0.140 -0.983 \end{bmatrix}\) & \ang{20}\end{tabular} 
+\([0.174,\,-0.934,\, -0.034]^T\) & \ang{40} \\ \hline 
+\([0 ,\, 0.7071 ,\, 0.7071]^T\) & \ang{40} \\ \hline 
+\([-0.853 ,\, 0.436 ,\, -0.286]^T\) & \ang{40} \\ \hline 
+\([-0.122 ,\,-0.140,\, -0.983]^T\) & \ang{20}\end{tabular} 
 \end{center}
@@
 This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
-The first term of~\cref{eqn:delta_dot} has the effect of increasing the proportional gain of the control system, since the time derivative of the attitude error vector, \( \dot{e_{R}} \), is linear with respect to the angular velocity error vector \( e_\Omega\).
+The first term of~\cref{eqn:delta_dot} has the effect of increasing the proportional gain of the control system, since the time derivative of the attitude error vector, \( \dot{e}_{R} \), is linear with respect to the angular velocity error vector \( e_\Omega\).
 \begin{figure} 
@@
 
+	\centering
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
@@
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{cad_adapt} 
+		\includegraphics[trim=9cm 2.5cm 0 0,clip,width=1.29\columnwidth]{cad_adapt} 
 		\caption{Attitude trajectory} \label{fig:cad_adapt} 
@@
 \end{figure}
-A sensor pointing direction is defined in the body frame of the hexrotor as \( r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix}^T \).
-We define an obstacle in the inertial frame as \( v = \begin{bmatrix} \frac{1}{\sqrt{2}} & \frac{1}{\sqrt{2}} & 0\end{bmatrix}^T \) with \( \theta = \ang{12} \).
-An initial state is defined as \(R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \), while the desired state is \(R_d = \text{ROT3}(\ang{0})=I \).
+A sensor pointing direction is defined in the body frame of the hexrotor as \( r = [1,0,0]^T \).
+We define an obstacle in the inertial frame as \( v = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}, 0]^T \) with \( \theta = \ang{12} \).
+An initial state is defined as \(R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \), while the desired state is \(R_d =I \).
 This results in the UAV performing a \ang{90} yaw rotation about the vertical axis of the spherical joint and the constrained region is on the shortest path connecting $R_0$ and $R_d$. 
@@
 \end{figure}
+
 The experimental results are shown in~\Cref{fig:exp}.
@@
 \begin{align*}
-	0 \leq  \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta} \leq 1 \, ,
+	0 \leq  \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta} \leq 1 ,
 \end{align*}
@@
 \begin{align*}
-	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee \, ,
+	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee ,
 %	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
@@
 \begin{align*}
-	\dirDiff{B}{R} &=  \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} \, ,
+	\dirDiff{B}{R} &=  \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} ,
 %	-\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta} \right) \right]
@@
 %		q_{31} & q_{32} & q_{33}
-%	\end{bmatrix} \, .
+%	\end{bmatrix} .
 %\end{align*}
@@
 %\begin{align}
-%	g_3 q_{32} &= g_2 q_{23} \, , \\
-%	g_1 q_{13} &= g_3 q_{31} \, , \\
-%	g_2 q_{21} &= g_1 q_{12} \, .
+%	g_3 q_{32} &= g_2 q_{23} , \\
+%	g_1 q_{13} &= g_3 q_{31} , \\
+%	g_2 q_{21} &= g_1 q_{12} .
 %\end{align}
@@
 %\begin{align}
-%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 \, , \\
-%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, , \\
-%	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 \, .
+%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \\
+%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 , \\
+%	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 .
 %\end{align}
@@
 The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
-This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \) .
+This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \).
 Since we assume the system will not operate in violation of the constraints, the addition of the barrier function does not add additional critical points to the control system.
 The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
-The proof \( A(R) \) in of~\cref{item:prop_era_upbound} is available in~\cite{lee2011a}.
+The proof \( A(R) \) in of~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
 \subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
@@
 \begin{gather*}
-	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega \, .
+	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega .
 \end{gather*}
@@
 \begin{gather*}
-	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} \, .
+	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} .
 \end{gather*}
@@
 \begin{gather*}
-	\diff{}{t} (B) = \frac{r^T \parenth{\hat{\Omega} R^T} v}{\alpha \parenth{r^T R^T v - \cos \theta}} \, .
+	\diff{}{t} (B) = \frac{r^T \parenth{\hat{\Omega} R^T} v}{\alpha \parenth{r^T R^T v - \cos \theta}} .
 \end{gather*}
@@
 \begin{gather*}
-	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee \, .
+	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee .
 \end{gather*}
@@
 \begin{gather*}
-	\diff{}{t}( e_{R_B} )= a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r \, ,
+	\diff{}{t}( e_{R_B} )= a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r ,
 \end{gather*}
@@
 	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} , \,
-	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} \, .
+	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} .
 \end{gather*}
@@
 \begin{gather*}
-	\diff{}{t} (\Psi) = \dot{A} B + A \dot{B} \, .
+	\diff{}{t} (\Psi) = \dot{A} B + A \dot{B} .
 \end{gather*}
@@
 \begin{align*}
-	\diff{}{t} e_\Omega = \dot{\Omega} = J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } \, .
+	\diff{}{t} e_\Omega = \dot{\Omega} = J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } .
 \end{align*}
@@
 	\begin{gather}
-		V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d) \, . \label{eqn:v_nodist}
+		\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d) . \label{eqn:v_nodist}
 	\end{gather}
-	From~\cref{item:prop_psi_psd} of~\Cref{prop:config_error}, \(V \geq 0 \).
-	Using~\cref{eqn:eW_dot,eqn:psi_dot} with \( \Delta = 0 \), the time derivative of \( V \) is given by
+	From~\cref{item:prop_psi_psd} of~\Cref{prop:config_error}, \(\mathcal{V} \geq 0 \).
+	Using~\cref{eqn:eW_dot,eqn:psi_dot} with \( \Delta = 0 \), the time derivative of \( \mathcal{V} \) is given by
 	\begin{align}
-		\dot{V} &= -k_\Omega \norm{e_\Omega}^2 \, . \label{eqn:vdot_nodist}
+		\dot{\mathcal{V}} &= -k_\Omega \norm{e_\Omega}^2 . \label{eqn:vdot_nodist}
 %		e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
 	\end{align}
-	Since \( V \) is positive definite and \( \dot{V} \) is negative semi-definite, the zero equilibrium point \( e_R, e_\Omega \) is stable in the sense of Lyapunov.
-	The Lyapunov function is non-increasing, therefore \( \lim_{t\to\infty} \norm{e_\Omega} = 0 \) and \( \norm{e_R} \) is uniformly bounded.
-	One can show that \( \norm{\ddot{e}_\Omega} \) is bounded.
-	From Barbalat's Lemma, it follows \( \lim_{t\to\infty}\norm{\dot{e}_\Omega} = 0 \)~\cite[Lemma 8.2]{khalil1996}.
+	Since \( \mathcal{V} \) is positive definite and \( \dot{\mathcal{V}} \) is negative semi-definite, the zero equilibrium point \( e_R, e_\Omega \) is stable in the sense of Lyapunov.
+This also implies \( \lim_{t\to\infty} \norm{e_\Omega} = 0 \) and \( \norm{e_R} \) is uniformly bounded, as the Lyapunov function is non-increasing.
+From \refeqn{eRA_dot} and \refeqn{eRB_dot}, $\lim_{t\to\infty} \dot e_R =0$.
+	One can show that \( \norm{\ddot{e}_R} \) is bounded.
+	From Barbalat's Lemma, it follows \( \lim_{t\to\infty}\norm{\dot{e}_R} = 0 \)~\cite[Lemma 8.2]{khalil1996}.
+Therefore, the equilibrium is asymptotically stable.
+As the Lyapunov function is uniformly bounded, the inequality constraint is satisfied always.
+
 \subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
@@
 	Next, we show~~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
-	The Frobenius norm \( \norm{E}_F \) is given in~\cite{lee2011a} as
+	The Frobenius norm \( \norm{E}_F \) is given in~\cite{LeeITCST13} as
 	\begin{gather*}
-		\norm{E}_F = \sqrt{\tr{E^T E}} = \frac{1}{2} \sqrt{\tr{G^2} + \tr{R^T R_d G}^2} \, .
+		\norm{E}_F = \sqrt{\tr{E^T E}} = \frac{1}{2} \sqrt{\tr{G^2} + \tr{R^T R_d G}^2} .
 	\end{gather*}
@@
 	\begin{gather*}
-		\norm{E}^2_F \leq \frac{1}{4} \parenth{\tr{G^2} + \tr{G}^2} \leq \frac{1}{2} \tr{G}^2 \, ,
+		\norm{E}^2_F \leq \frac{1}{4} \parenth{\tr{G^2} + \tr{G}^2} \leq \frac{1}{2} \tr{G}^2 ,
 	\end{gather*}
@@
 		\norm{F}_F = \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} - 2 \tr{a^T b} \right. \\
-		\left.+ 2 \tr{a^T c } + \tr{b^T b}  - 2 \tr{b^T c} + \tr{c^T c}\right] \, .
+		\left.+ 2 \tr{a^T c } + \tr{b^T b}  - 2 \tr{b^T c} + \tr{c^T c}\right] .
 	\end{gather*}
@@
 	\begin{gather*}
-		a = r^T R r I \, , \quad	b = R^T v r^T \, , \quad c = \frac{R^T \hat{v} R r v^T R \hat{r}}{r^T R^T v - \cos \theta}\, .
+		a = r^T R r I , \quad	b = R^T v r^T , \quad c = \frac{R^T \hat{v} R r v^T R \hat{r}}{r^T R^T v - \cos \theta}.
 	\end{gather*}
@@
 	\begin{gather*}
-		\tr{a^T a} = \parenth{v^T R r}^2 \tr{I} \leq 3 \beta^2 \, ,
+		\tr{a^T a} = \parenth{v^T R r}^2 \tr{I} \leq 3 \beta^2 ,
 	\end{gather*}
@@
 	\begin{gather*}
-		\tr{a^T b} = v^T R r \tr{R^T v r^T} = \parenth{v^T R r}^2 \leq \beta^2 \, ,
+		\tr{a^T b} = v^T R r \tr{R^T v r^T} = \parenth{v^T R r}^2 \leq \beta^2 ,
 	\end{gather*} 
@@
 	\begin{gather*}
-		\tr{a^T c} = \frac{v^T R r}{r^T R^T v - \cos \theta} \tr{\parenth{R^T v}^\vee \parenth{r v^T R} \hat{r} } \, ,
+		\tr{a^T c} = \frac{v^T R r}{r^T R^T v - \cos \theta} \tr{\parenth{R^T v}^\vee \parenth{r v^T R} \hat{r} } ,
 	\end{gather*}
 	where we used the hat map property~\cref{eqn:RxR}.
-	One can show that \(\tr{a^T c} \leq 0 \) over the range \( -1 \leq v^T R r \leq \cos \theta \). 
+	One can show that \(\mathrm{tr}[a^T c] \leq 0 \) over the range \( -1 \leq v^T R r \leq \cos \theta \). 
 	Next, \( \tr{b^T b}\) is equivalent to
 	\begin{gather*}
-		\tr{b^T b} = \tr{r v^T R R^T v r^T} = 1 \, ,
+		\tr{b^T b} = \tr{r v^T R R^T v r^T} = 1 ,
 	\end{gather*}
@@
 	\begin{gather*}
-		\tr{c^T c} = \tr{\hat{r} R^T v r^T \bracket{-I + R^T v v^T R} r v^T R \hat{r}} \, ,
+		\tr{c^T c} = \tr{\hat{r} R^T v r^T \bracket{-I + R^T v v^T R} r v^T R \hat{r}} ,
 	\end{gather*}
@@
 	\begin{gather*}
-		\tr{c^T c } = \frac{1 - 2\parenth{v^T R r}^2 + \parenth{v^T R r}^4}{\parenth{r^T R^T v - \cos \theta}^2} \, . 
+		\tr{c^T c } = \frac{1 - 2\parenth{v^T R r}^2 + \parenth{v^T R r}^4}{\parenth{r^T R^T v - \cos \theta}^2} . 
 	\end{gather*}
@@
 \subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}
-	Consider the Lyapunov function \( V \) given by
+	Consider the Lyapunov function \( \mathcal{V} \) given by
 	\begin{gather}
-		V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta \, , \label{eqn:v_adapt}
+		\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , \label{eqn:v_adapt}
 	\end{gather}
@@
 	\begin{gather}
-		V \leq z^T W z \, , \label{eqn:v_upper_bound}
+		\mathcal{V} \leq z^T W z , \label{eqn:v_upper_bound}
 	\end{gather}
-	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = \begin{bmatrix}e_R & e_\Omega & e_\Delta\end{bmatrix}^T \) and the matrix \(W \in \R^{3 \times 3}\) is given by
+	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrix \(W \in \R^{3 \times 3}\) is given by
 	\begin{gather*}
@@
 			0 & 0 & \frac{1}{2 k_\Delta}
-		\end{bmatrix} \, .
+		\end{bmatrix} .
 	\end{gather*}
-	The time derivative of \( V\) with the control inputs~\cref{eqn:adaptive_control} is defined as
+	The time derivative of \( \mathcal{V}\) with the control inputs~\cref{eqn:adaptive_control} is given by
 	\begin{align}
-		\dot{V} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
-		&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} \, , \label{eqn:vdot}
+		\dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
+		&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
 	\end{align}
@@
 	\begin{align*}
-		 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 \, . 
+		 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
 	\end{align*}
@@
 	\begin{gather*}
-		\dot{V} \leq -z^T M z \, ,
+		\dot{V} \leq -\zeta^T M \zeta ,
 	\end{gather*}
-	where the matrix \( M \in \R^{2 \times 2} \) is 
+	where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
 	\begin{gather}
@@
 			\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
-		\end{bmatrix} \, .
+		\end{bmatrix} .
 	\end{gather}
 	If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
-	This implies that the Lyapunov function \( V \) is non-increasing and bounded from below.
-	Furthermore, since \( V \) is nonincreasing the disturbance error \( e_\Delta\) is bounded.
-	Since \( \dot{V} \) is uniformly continuous in time this implies that the zero equilibrium \( e_R, e_\Omega\) is stable in the sense of Lyapunov
-	The domain \( D \) does that include the undesired equilibria and ensures that as \( e_R \to 0 \) the attitude also converges \( R \to R_d \).
+	This implies that $\dot{\mathcal{V}}$ is negative semidefinite and $\lim_{t\to\infty} \zeta=0$. As the Lyapunov function is non-increasing $z$ is uniformly bounded. 
+%	
+%	
+%	This implies that the Lyapunov function \( V \) is non-increasing and bounded from below.
+%	Furthermore, since \( V \) is nonincreasing the disturbance error \( e_\Delta\) is bounded.
+%	Since \( \dot{V} \) is uniformly continuous in time this implies that the zero equilibrium \( e_R, e_\Omega\) is stable in the sense of Lyapunov
+%	The domain \( D \) does that include the undesired equilibria and ensures that as \( e_R \to 0 \) the attitude also converges \( R \to R_d \).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
+%\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                   % on the last page of the document manually. It shortens

### 2015-09-27 ACC16.2.tex
added a statement on the proof of proposition 4.

@@
 	Therefore, the equilibrium is asymptotically stable. 
-As the Lyapunov function is uniformly bounded, the inequality constraint is satisfied always.
+	As the Lyapunov function is uniformly bounded, the inequality constraint is always satisfied.
 
@@
 	The bound on \( e_{R_A} \) is given in~\cref{eqn:psi_lower_bound} while \( e_{R_B} \) arises from the definition of the cross product \( \norm{a \times b} = \norm{a} \norm{b} \sin \theta \).
+	Finally, we can find the upper bound~\cref{eqn:eR_dot} as
+	\begin{gather*}
+		\norm{\dot{e}_R} \leq \parenth{\norm{B} \norm{E} + 2 \norm{e_{R_A}} \norm{e_{R_B}} + \norm{A}\norm{F}} \norm{e_\Omega} \, .
+	\end{gather*}
+	Using~\crefrange{eqn:AB_bound}{eqn:eRB_bound} one can define \( H \) in terms of known values.
 \subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}
@@
 	If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
-	This implies that $\dot{\mathcal{V}}$ is negative semidefinite and $\lim_{t\to\infty} \zeta=0$. As the Lyapunov function is non-increasing $z$ is uniformly bounded. 
+	This implies that $\dot{\mathcal{V}}$ is negative semidefinite and $\lim_{t\to\infty} \zeta=0$. 
+	As the Lyapunov function is non-increasing $z$ is uniformly bounded. 
 %	

### 2015-09-28 ACC16.2.tex
corrected some typos and errors. fixed some new line errors

@@
 In addition, we develop an adaptive update law that enables attitude stabilization in the presence of unknown disturbances. 
-The attitude dynamics and the proposed control systems developed on the special orthogonal group such that singularities and ambiguities of other attitude parameterizations, such as Euler angles and quaternions are completely avoided.
-The effectiveness of the proposed control system are demonstrated through numerical simulations and experimental results.
+The attitude dynamics and the proposed control systems are developed on the special orthogonal group such that singularities and ambiguities of other attitude parameterizations, such as Euler angles and quaternions are completely avoided.
+The effectiveness of the proposed control system is demonstrated through numerical simulations and experimental results.
 \end{abstract}
@@
 We apply a potential function based approach developed directly on the nonlinear manifold \(\SO\). 
-By characterizing the attitude both globally and uniquely \(\SO\), our approach avoids the issues of attitude parameterizations, such as kinematic singularities and ambiguities, and is geometrically exact.
+By characterizing the attitude both globally and uniquely on \(\SO\), our approach avoids the issues of attitude parameterizations, such as kinematic singularities and ambiguities, and is geometrically exact.
 A new configuration error function on \(\SO\) with a logarithmic barrier function is proposed to avoid constrained regions. 
@@
 Furthermore, we formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances. 
-The stability of the proposed control systems are verified via mathematically rigorous Lyapunov analysis on $\SO$.
+The stability of the proposed control systems is verified via mathematically rigorous Lyapunov analysis on $\SO$.  
 In short, the proposed attitude control system in the presence of inequality constraints is computationally efficient and able to handle uncertain disturbances. 
@@
 Based on the proposed configuration error function,  nonlinear geometric attitude controllers are constructed. 
-A smooth control system is first developed assuming that there is  no disturbance,and then it is extended to include an adaptive update law for stabilization in the presence of unknown disturbances.
+A smooth control system is first developed assuming that there is  no disturbance, and then it is extended to include an adaptive update law for stabilization in the presence of unknown disturbances. 
 The proposed attitude configuration error function and several properties are summarized as follows.
@@
 %We assume a desired attitude command \( ( R_d, \Omega_d = 0 ) \), the current attitude and angular velocity \( ( R, \Omega) \), and a state constraint~\cref{eqn:constraint} are given.
-Define an attitude error function \( \Psi : \SO \times \SO \to \R \), and attitude error vector \( e_R \in \R^3 \), and an angular velocity error vector \( e_\Omega \in \R^3 \) as follows:
+Define an attitude error function \( \Psi : \SO \times \SO \to \R \), an attitude error vector \( e_R \in \R^3 \), and an angular velocity error vector \( e_\Omega \in \R^3 \) as follows:
 \begin{gather}
@@
 Barrier functions are typically used in optimal control and motion planning applications.
-A visualization of the configuration error function is presented in~\cref{fig:config_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
+A visualization of the configuration error function is presented in~\cref{fig:avoid_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
 We use the scale factor~\(\frac{1}{1+\cos \theta} \) to ensure that \( \Psi \) remains positive definite.
@@
 For example, the configuration error function can be formulated as $\Psi=A[1+\sum_i C_i]$, where $C_i$ has the form of $C_i=B-1$ for the $i$-th constraint. 
-In this manner, one may enforce multiple state inequality constraints, and these are illustrated later at numerical examples.
+In this manner, one may enforce multiple state inequality constraints, and we later demonstrate this through numerical simulation.
 
@@
 	\end{gather}
-	Then the zero equilibrium of the attitude errors is asymptotically stable, and the inequality constraint is satisfied.
+	Then the zero equilibrium of the attitude error is asymptotically stable, and the inequality constraint is satisfied.
 \end{prop}
@@
 This scenario is typical of many mechanical systems and represents unmodelled dynamics or external moments acting on the system.
-For example, Earth orbiting spacecraft typically experience both a torque due to a gravitational gradient.
+For example, Earth orbiting spacecraft typically experience a torque due to a gravitational gradient.
 % as well as external torques to due solar radiation pressure.
@@
 The inequality constraints from~\Cref{tab:constraints} are depicted as red cones, where the cone half angle is \( \theta \).
-The control system is able to asymptotically converge to zero attitude error 
+The control system is able to asymptotically converge to zero attitude error.
 In addition, the estimate of the disturbance converges to the the true value.
@@
 The attitude configuration error is augmented with a barrier function to avoid the constrained region, and an adaptive control law is proposed to cancel the effects of uncertainties. 
-We show the stability of the  proposed control system through a rigorous mathematically analysis.
+We show the stability of the  proposed control system through a rigorous mathematical analysis.
 In addition, we have demonstrated the control system via numerical simulation and hardware experiments on a hexrotor UAV.
@@
 The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
-The proof \( A(R) \) in of~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
+The proof \( A(R) \) of~\cref{item:prop_era_upbound} in~\Cref{prop:config_error} is available in~\cite{LeeITCST13}.
 \subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
@@
 	\end{align*}
-	Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{V} \) is written as
+	Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
 	\begin{gather*}
-		\dot{V} \leq -\zeta^T M \zeta ,
+		\dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
 	\end{gather*}

### 2015-09-28 ACC16.2.tex
final corrections. will submit this version

@@
 Once an appropriate path is determined an appropriate control is implemented to perform the attitude maneuver.
-The random search approach can only stochastically guarantee attitude convergence as it can be shown that as the number of vertices in the graph grow, the probability of non convergence goes to zero.
+The random search approach can only stochastically guarantee attitude convergence as it can be shown that as the number of vertices in the graph grow, the probability of nonconvergence goes to zero.
 However, the computational demand grows as the size of the graph is increased. 
@@
 
-This paper is focused on developing an adaptive attitude control scheme in the presence of attitude inequality constraint on \(\SO\).
+This paper is focused on developing an adaptive attitude control scheme in the presence of attitude inequality constraints on \(\SO\).
 We apply a potential function based approach developed directly on the nonlinear manifold \(\SO\). 
@@
 	\begin{align}
-		\norm{e_{R_A}}^2 \leq \frac{\Psi}{b_1} , \label{eqn:psi_lower_bound}
+		\norm{e_{R_A}}^2 \leq \frac{A(R)}{b_1} , \label{eqn:psi_lower_bound}
 	\end{align}
@@
 
-\Cref{eqn:psi} is composed of an attractive term, \( A (R) \) toward the desired attitude, and a repulsive term, \( B(R) \) from the undesired direction \( R^T v \).
+\Cref{eqn:psi} is composed of an attractive term, \( A (R) \) toward the desired attitude, and a repulsive term, \( B(R) \) away from the undesired direction \( R^T v \).
 The attractive error function has been used for attitude control on \(\SO\).
@@
 The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
-The proof \( A(R) \) of~\cref{item:prop_era_upbound} in~\Cref{prop:config_error} is available in~\cite{LeeITCST13}.
+The proof of \( A(R) \) given by~\cref{item:prop_era_upbound} in~\Cref{prop:config_error} is available in~\cite{LeeITCST13}.
 \subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}

### 2015-10-23 ACC16.2.tex
fixed another error to reduce page length. now this is final. for reals
corrected typo

@@
 A body fixed sensor is defined as \(r = [1,0,0]\), while multiple inequality constraints are defined in~\Cref{tab:constraints}.
-The simulation parameters are chosen to be similar to those found in~\cite{lee2011b}, howver we increase the size of the constraint regions to create a more challenging scenario for the control system.
+The simulation parameters are chosen to be similar to those found in~\cite{lee2011b}, however we increase the size of the constraint regions to create a more challenging scenario for the control system.
 
@@
 The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
-The proof of \( A(R) \) given by~\cref{item:prop_era_upbound} in~\Cref{prop:config_error} is available in~\cite{LeeITCST13}.
+The proof of \( \norm{e_{R_A}} \) given by~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
 \subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}

### 2016-01-31 ACC16.2.tex
added negative to eRB bound
Add matched uncertainty comment
Reviewer 1 comment 1
Add physic based explanantion about disturbance
Reviewer 2 Comment 3

@@
 \end{equation}
+This form of uncertainty enters the system dynamics through the input channel and as a result is referred to as a matched uncertainty. 
+While this form of uncertainty is easier than the unmatched variety many physically realizable disturbances may be modeled in this manner.
+For example, orbital spacecraft are subject to gravity gradient torques caused by the non-spherical distribution of mass of both the spacecraft and central gravitational body.
+This form of disturbance may be represented as a body fixed torque on the vehicle.
+In addition, for typical scenarios, where the spacecraft is significantly smaller than the orbital radius, the disturbance torque may be assumed constant over short time intervals.
 
@@
 		\norm{e_{R_A}} \leq \sqrt{\frac{\psi}{b_1}}, \label{eqn:eRA_bound} \\
-		\norm{e_{R_B}} \leq \frac{\sin\theta}{\alpha \parenth{\beta - \cos \theta}}. \label{eqn:eRB_bound}
+		\norm{e_{R_B}} \leq \frac{\sin\theta}{\alpha \parenth{\cos \theta - \beta}}. \label{eqn:eRB_bound}
 	\end{gather}

### 2016-01-31 ACC16.2.tex
Add A(R) and B(R) to equations
Reviewer 1 comment 2
Add detail on proposition 3
Reviewer 1 Comment 3

@@
 	\Psi(R) = A(R) B(R) , \label{eqn:psi} \\
-	e_R = e_{R_A} B + A e_{R_B} , \label{eqn:eR} \\
+	e_R = e_{R_A} B(R) + A(R) e_{R_B} , \label{eqn:eR} \\
 	e_\Omega = \Omega , \label{eqn:eW}
@@
 		\diff{}{t} \parenth{\Psi} = e_R \cdot e_\Omega , \label{eqn:psi_dot}\\
-		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B + e_{R_A} \dot{B} + \dot{A}e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
+		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B(R) + e_{R_A} \dot{B(R)} + \dot{A(R)}e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
 		\diff{}{t} \parenth{e_{R_A}} = E(R, R_d) e_\Omega , \label{eqn:eRA_dot} \\
 		\diff{}{t} \parenth{e_{R_B}} = F(R) e_\Omega , \label{eqn:eRB_dot} \\
-		\diff{}{t} \parenth{A} = e_{R_A} \cdot e_\Omega , \label{eqn:A_dot} \\
-		\diff{}{t} \parenth{B} = e_{R_B} \cdot e_\Omega , \label{eqn:B_dot} \\
+		\diff{}{t} \parenth{A(R)} = e_{R_A} \cdot e_\Omega , \label{eqn:A_dot} \\
+		\diff{}{t} \parenth{B(R)} = e_{R_B} \cdot e_\Omega , \label{eqn:B_dot} \\
 		\diff{}{t} \parenth{e_\Omega} = J^{-1} \parenth{-\Omega \times J \Omega + u + W(R, \Omega) \Delta} , \label{eqn:eW_dot}
@@
 \begin{prop}[Attitude Control]\label{prop:att_control}
-	Given a desired attitude command \( \parenth{R_d, \Omega_d = 0} \) and positive constants \( k_R, k_\Omega \in \R \) we define a control input \( u \in \R^3 \) as follows
+	Given a desired attitude command \( \parenth{R_d, \Omega_d = 0} \), which satisfies the constraint~\cref{eq:constraint}, and positive constants \( k_R, k_\Omega \in \R \) we define a control input \( u \in \R^3 \) as follows
 	\begin{gather}
@@
 \end{align*}
+
 \subsection{Proof of~\Cref{prop:att_control}}\label{proof:att_control}
@@
 Therefore, the equilibrium is asymptotically stable.
-	As the Lyapunov function is uniformly bounded, the inequality constraint is always satisfied.
+
+Furthermore, since \( \dot{\mathcal{V}} \leq 0 \) the Lyapunov function is uniformly bounded which implies 
+\begin{align*}
+	\Psi(R(t)) \leq \mathcal{V}(t) \leq \mathcal{V}(0) .
+\end{align*}
+In addition, the logarithmic term in~\cref{eqn:B} ensures \( \Psi(R) \to \infty \) as \( r^T R^T v \to \cos \theta \).
+Therefore, the inequality constraint is always satisfied given that the desired equilibrium lies in the feasible set.
 

### 2016-02-03 ACC16.2.tex
Shrink error function surface plots
Added some detail about SO(3) visualization with the surface plots.
Also modified the figures to include larger axis labels.

Reviewer 1 Comment 5
Reviewer 2 Comment 7

@@
 \Cref{eqn:psi} is composed of an attractive term, \( A (R) \) toward the desired attitude, and a repulsive term, \( B(R) \) away from the undesired direction \( R^T v \).
-The attractive error function has been used for attitude control on \(\SO\).
+In order to visualize the attitude error function on \( \SO \) we utilize a spherical coordinate representation.
+Recall that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth,and elevation.
+This coordinate system commonly used to define locations on the Earth in terms of a latitude and longitude.
+Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
+We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
+Using the elementary Euler rotations the rotation matrix is now defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
+We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \).
+Applying this method,~\cref{fig:config_error} allows us to visualize the error function on \( \SO \).
+The attractive error function, given by~\cref{eqn:A}, has been previously used for attitude control on \(\SO\).
 The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum of \( A(R) \).

### 2016-02-03 ACC16.2.tex
Add detail about experimental results
Why experimental trajectory differs from sim and why it doesn't converge

Reviewer 1 Comment 6
Review 2 Comment 10

@@
 The experimental results are shown in~\Cref{fig:exp}.
-The attitude error asymptotically converges to zero. 
+In order to maneuver the system "close" to the constrained zone we utilize several intermediary set points on either side of the obstacle.
+From the initial attitude the hexrotor rotates to the first set point, pauses, and then continues around the obstacle to the second set point before continuing toward the desired attitude.
+As a result this creates the stepped behavior of the configuration error history as shown in~\cref{fig:Psi_exp}.
+
+The brushless motors of the hexrotor allow for large control inputs which are critical to enable aggressive maneuvers. 
+When constrained to the spherical joint the hexrotor is capable of performing responsive attitude changes with high angular velocities.
+In addition, The on-board control and motion capture system operate at a discrete interval of approximately \SI{100}{\hertz}.
+It is possible for the system to violate the constraint between these discrete steps and cause numerical exceptions within the embedded software. 
+As a result, conservative control gains are chosen to ensure the hexrotor operates in a sedate manner and to allow sufficient time for the measurement and control software to operate.
+
+There exist several sources of error in the experimental setup.
+The motion capture system uses a series of optical sensor to determine the relative position of several tracking markers. 
+These markers as well as the cameras must remain fixed to ensure accurate attitude measurement.
+In addition, the spherical joint is not fixed at the center of mass but is instead offset due to the physical structure of the hexrotor.
+As a result a disturbance moment is induced on the resultant motion.
+
+This results in a small steady state error in the vicinity of the desired attitude. 
+Over time~\cref{eqn:delta_dot} will remain non-zero while \( e_R \neq 0 \).
+This will cause an increase in control input until the steady-state error is reduced. 
+Further tuning of the control gains would enable a faster response and a reduced settling time.
+
 The hexrotor avoids the constrained region illustrated by the circular cone in~\cref{fig:traj_exp}, by rotating around the boundary of the constraint. 

### 2016-02-05 ACC16.2.tex
Reword description of attitude avoidance via interior midpoints
Reviewer 2 comment 1

@@
 Several approaches have been developed to treat the attitude control problem in the presence of constraints.
-A geometric approach is used in~\cite{hablani1999} to determine feasible attitude trajectories prior to implementation.
-Typically, an optimal or easily implementable on-board control scheme for attitude maneuvers is considered without state constraints.
-The algorithm then seeks an intermediate point such that the control scheme can be applied for each segment without violation of the constraints.
-While the geometric method is conceptually simple, it is difficult to generalize for an arbitrary number of constraints.
-In addition, this geometric type of approach is only applicable to problems where the selection of intermediate points are computationally feasible.
+A conceptually straightforward approach is used in~\cite{hablani1999} to determine feasible attitude trajectories prior to implementation.
+The algorithm determines an intermediate point such that an unconstrained maneuver can be calculated for each subsegment.
+Typically, an optimal or easily implementable on-board control scheme for attitude maneuvers is applied to maneuver the vehicle along these segments.
+In this manner it is possible to accomplish constraint avoidance by linking several intermediary unconstrained maneuvers.
+While this method is conceptually simple, it is difficult to generalize for an arbitrary number of constraints.
+In addition, this approach is only applicable to problems where the selection of intermediate points are computationally feasible.
 

### 2016-02-05 ACC16.2.tex
Add some changes in discussing artificial potential functions.
Reviewer 2 Comment 2

@@
 % Previous potential function approach - developed using att parameterizations - singularities/ambiguities
-Artificial potential functions are commonly used to handle kinematic constraints for a wide range of problems in robotics.
+Artificial potential functions are commonly used to handle kinematic constraints for a wide range of problems in robotics~\cite{rimon1992}.
 The goal is the design of attractive and repulsive terms which drive the system toward or away from a certain state, respectively.
@@
 The superposition of the these functions allows one to apply standard feedback control schemes for stabilization and tracking.
-Artificial potential functions have previously been applied to the attitude control problem in~\cite{lee2011b,mcinnes1994}.
-These approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by the singularities of minimal representations or the ambiguity of quaternions.
+More specifically, artificial potential functions have previously been applied to the spacecraft attitude control problem in~\cite{lee2011b,mcinnes1994}.
+However, both of these approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by the singularities of minimal representations or the ambiguity of quaternions.
 

### 2016-02-05 ACC16.2.tex
Modify Frobenius norm to avoid use of r
We use r to denote both the rank of a matrix and a body fixed vector.

Reviewer 2 Comment 4

@@
 Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\R^n$ and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively.
-The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A} \leq \norm{A}_F = \sqrt{\tr{A^T A}} \leq \sqrt{r} \norm{A} \).
+The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A} \leq \norm{A}_F = \sqrt{\tr{A^T A}} \leq \sqrt{\text{rank}(A)} \norm{A} \).
 

### 2016-02-05 ACC16.2.tex
Modify Psi to be a function on SO(3) only
Reviewer 2 Comment 5

@@
 %We assume a desired attitude command \( ( R_d, \Omega_d = 0 ) \), the current attitude and angular velocity \( ( R, \Omega) \), and a state constraint~\cref{eqn:constraint} are given.
-Define an attitude error function \( \Psi : \SO \times \SO \to \R \), an attitude error vector \( e_R \in \R^3 \), and an angular velocity error vector \( e_\Omega \in \R^3 \) as follows:
+Define an attitude error function \( \Psi : \SO \to \R \), an attitude error vector \( e_R \in \R^3 \), and an angular velocity error vector \( e_\Omega \in \R^3 \) as follows:
 \begin{gather}

### 2016-02-07 ACC16.2.tex
Add detail on constants for proposition 4
Reviewer 2 Comment 9

@@
 	The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
-	This implies that that both \( A(R) \) and \( B(R) \) are also bounded which shows~\cref{eqn:AB_bound}.
+	This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
+	Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
 

### 2016-02-07 ACC16.2.tex
Reduce length by removing proofs and citing future arxiv paper

--- 2016-02-05 ACC16.2.tex
@@
 A graph is generated consisting of vertices from an initial attitude to a desired attitude. 
-A random iterative search is conducted to determine a path through the graph such that a given cost functional is minimized.
-Once an appropriate path is determined an appropriate control is implemented to perform the attitude maneuver.
+A random iterative search is conducted to determine a path through a directed graph such that a given cost functional is minimized.
 The random search approach can only stochastically guarantee attitude convergence as it can be shown that as the number of vertices in the graph grow, the probability of nonconvergence goes to zero.
@@
 As a result, random search approaches are ill-suited to on-board implementation or in scenarios that require agile maneuvers.
+
+Model predictive control for spacecraft attitude dynamics is studied in~\cite{guiggiani2014,kalabic2014,gupta2015}.
+These methods rely on linear or non-linear state dynamics to repeatedly solve a finite-time optimal control problem.
+As a result, model predictive control methods are also computational expensive and apply direct optimization methods to solve the necessary conditions for optimality.
+Therefore these methods are complicated to implement and not applicable for real-time control applications.
 
@@
 In addition, for typical scenarios, where the spacecraft is significantly smaller than the orbital radius, the disturbance torque may be assumed constant over short time intervals.
-
-In~\refeqn{Rdot}, the \textit{hat} map $\wedge :\R^{3}\rightarrow\so$ represents the transformation of a vector in $\R^{3}$ to a $3\times 3$ skew-symmetric matrix such that $\hat x y = x\times y$ for any $x,y\in\R^{3}$~\cite{bullo2004}.
-More explicitly, 
-\begin{align*}
-\hat x = \begin{bmatrix} 0 & -x_3 & x_2 \\ x_3 & 0 & -x_1 \\ -x_2 & x_1 & 0\end{bmatrix},
-\end{align*}
-for $x=[x_1,x_2,x_3]^T\in\R^{3}$. 
-The inverse of the hat map is denoted by the \textit{vee} map $\vee:\so\rightarrow\R^{3}$. 
-Several properties of the hat map are summarized as
-\begin{gather}
-%    \hat x y = x\times y = - y\times x = - \hat y x,\\
-    x\cdot \hat y z = y\cdot \hat z x,\quad \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z\label{eqn:STP},\\
-%    \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z,\label{eqn:VTP}\\
-%    C^TC=-C^T\hat e_3^2 C = I_2
-%    \hat x^T \hat x = (x^T x) I - x x^T,\\
-%    \hat x \hat y \hat x=-(y^Tx)\hat x,\\
-%    -\frac{1}{2}\tr{\hat x \hat y} = x^T y,\\
-    \widehat{x\times y} = \hat x \hat y -\hat y \hat x = yx^T-xy^T,\label{eqn:hatxy}\\
-    %\tr{\hat x A}=
-    \tr{A\hat x }=\frac{1}{2}\tr{\hat x (A-A^T)}=-x^T (A-A^T)^\vee,\label{eqn:hat1}\\
-%    \widehat{Ax} = \hat x \parenth{\frac{1}{2}\tr{A}I-A} + \parenth{\frac{1}{2}\tr{A}I-A}^T \hat x,\\
-    \hat x  A+A^T\hat x=(\braces{\tr{A}I_{3\times 3}-A}x)^{\wedge},\label{eqn:xAAx}\\
-R\hat x R^T = (Rx)^\wedge,\quad 
-R(x\times y) = Rx\times Ry\label{eqn:RxR}
-%,\label{eqn:Rxy}
-\end{gather}
-for any $x,y,z\in\R^{3}$, $A\in\R^{3\times 3}$ and $R\in\SO$. 
-Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\R^n$ and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively.
-The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A} \leq \norm{A}_F = \sqrt{\tr{A^T A}} \leq \sqrt{\text{rank}(A)} \norm{A} \).
 
@@
 \begin{proof}
-See~\Cref{proof:config_error}.
+For brevity the proof is available in~\cite{kulumani2016b}.
 \end{proof}
@@
 \begin{proof}
-See~\Cref{proof:error_dyn}.
+For brevity the proof is found in~\cite{kulumani2016b}.
 \end{proof}
@@
 \begin{proof}
-See~\Cref{proof:att_control}.
+For brevity the proof is found in~\cite{kulumani2016b}.
 \end{proof}
@@
 \begin{proof}
-See~\Cref{proof:eR_dot_bound}.
+For brevity the proof is found in~\cite{kulumani2016b}.
 \end{proof}
@@
 \begin{proof}
-See~\Cref{proof:adaptive_control}.
+For brevity the proof is found in~\cite{kulumani2016b}.
 \end{proof}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\subsection{Proof of~\Cref{prop:config_error}}\label{proof:config_error}
-To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a positive definite function about \( R = R_d \)~\cite{bullo2004}.
-The constraint angle is assumed \( \ang{0} \leq \theta \leq \ang{90} \) such that \( 0 \leq \cos \theta \).
-The term \( r^T R^T v \) represents the cosine of the angle between the body fixed vector \( r \) and the inertial vector \( v \). 
-It follows that
-\begin{align*}
-	0 \leq  \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta} \leq 1 ,
-\end{align*}
-for all \( R \in \SO \). 
-As a result, its negative logarithm is always positive and from~\cref{eqn:B}, \(1 < B\).
-The error function \( \Psi = A B \) is composed of two positive terms and is therefore also positive definite, and it is minimized at \( R = R_d \).
-
-Next, we consider~\cref{item:prop_era}.
-The variation of~\cref{eqn:A} is taken with respect to \( \delta R = R \hat \eta \) as
-\begin{align*}
-	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee ,
-%	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
-\end{align*}
-where we used~\cref{eqn:hat1}.
-
-A straightforward application of the chain and product rules of differentiation allows us to show~\cref{item:prop_erb} as
-\begin{align*}
-	\dirDiff{B}{R} &=  \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} ,
-%	-\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta} \right) \right]
-\end{align*}
-where the scalar triple product~\cref{eqn:STP} was used.
-
-%To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
-%The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
-%\begin{align*}
-%	Q = R_d^T R = 
-%	\begin{bmatrix}
-%		q_{11} & q_{12} & q_{13} \\
-%		q_{21} & q_{22} & q_{23} \\
-%		q_{31} & q_{32} & q_{33}
-%	\end{bmatrix} .
-%\end{align*}
-%Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
-%\begin{subequations}
-%\begin{align}
-%	g_3 q_{32} &= g_2 q_{23} , \\
-%	g_1 q_{13} &= g_3 q_{31} , \\
-%	g_2 q_{21} &= g_1 q_{12} .
-%\end{align}
-%\end{subequations}
-%These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
-%Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
-%\begin{subequations}
-%\begin{align}
-%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \\
-%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 , \\
-%	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 .
-%\end{align}
-%\end{subequations}
-%As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
-%Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
-The critical points of \( e_{R_A} \) are derived in~\cite{bullo2004}.
-There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180}.
-The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
-This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \).
-Since we assume the system will not operate in violation of the constraints, the addition of the barrier function does not add additional critical points to the control system.
-The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
-The proof of \( \norm{e_{R_A}} \) given by~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
-\subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
-From the kinematics~\cref{eqn:Rdot} and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
-\begin{gather*}
-	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega .
-\end{gather*}
-Applying this to the time derivative of~\cref{eqn:A} gives
-\begin{gather*}
-	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} .
-\end{gather*}
-Applying~\cref{eqn:hat1} into this shows~\cref{eqn:A_dot}.
-Next, the time derivative of the repulsive error function is given by
-\begin{gather*}
-	\diff{}{t} (B) = \frac{r^T \parenth{\hat{\Omega} R^T} v}{\alpha \parenth{r^T R^T v - \cos \theta}} .
-\end{gather*}
-Using the scalar triple product, given by~\cref{eqn:STP}, one can reduce this to~\cref{eqn:B_dot}.
-The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
-\begin{gather*}
-	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee .
-\end{gather*}
-Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eqn:eRA_dot,eqn:E}.
-
-We take the time derivative of the repulsive attitude error vector, \( e_{R_B} \), as
-\begin{gather*}
-	\diff{}{t}( e_{R_B} )= a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r ,
-\end{gather*}
-with \( a \in \R \) and \( b \in \R\) given by 
-\begin{gather*}
-	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} , \,
-	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} .
-\end{gather*}
-Using the scalar triple product from~\cref{eqn:STP} as \( r \cdot \Omega \times \parenth{R^T v} = \parenth{R^T v} \cdot r \times \Omega \) gives~\cref{eqn:eRB_dot,eqn:F}.
-
-We show the time derivative of the configuration error function as
-\begin{gather*}
-	\diff{}{t} (\Psi) = \dot{A} B + A \dot{B} .
-\end{gather*}
-A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and appplying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
-We show~\cref{eqn:eW_dot} by rearranging~\cref{eqn:Wdot} as 
-\begin{align*}
-	\diff{}{t} e_\Omega = \dot{\Omega} = J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } .
-\end{align*}
-
-\subsection{Proof of~\Cref{prop:att_control}}\label{proof:att_control}
-Consider the following Lyapunov function:
-\begin{gather}
-	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d) . \label{eqn:v_nodist}
-\end{gather}
-From~\cref{item:prop_psi_psd} of~\Cref{prop:config_error}, \(\mathcal{V} \geq 0 \).
-Using~\cref{eqn:eW_dot,eqn:psi_dot} with \( \Delta = 0 \), the time derivative of \( \mathcal{V} \) is given by
-\begin{align}
-	\dot{\mathcal{V}} &= -k_\Omega \norm{e_\Omega}^2 . \label{eqn:vdot_nodist}
-%	e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
-\end{align}
-Since \( \mathcal{V} \) is positive definite and \( \dot{\mathcal{V}} \) is negative semi-definite, the zero equilibrium point \( e_R, e_\Omega \) is stable in the sense of Lyapunov. 
-This also implies \( \lim_{t\to\infty} \norm{e_\Omega} = 0 \) and \( \norm{e_R} \) is uniformly bounded, as the Lyapunov function is non-increasing.
-From \refeqn{eRA_dot} and \refeqn{eRB_dot}, $\lim_{t\to\infty} \dot e_R =0$.
-One can show that \( \norm{\ddot{e}_R} \) is bounded.
-From Barbalat's Lemma, it follows \( \lim_{t\to\infty}\norm{\dot{e}_R} = 0 \)~\cite[Lemma 8.2]{khalil1996}. 
-Therefore, the equilibrium is asymptotically stable.
-
-Furthermore, since \( \dot{\mathcal{V}} \leq 0 \) the Lyapunov function is uniformly bounded which implies 
-\begin{align*}
-	\Psi(R(t)) \leq \mathcal{V}(t) \leq \mathcal{V}(0) .
-\end{align*}
-In addition, the logarithmic term in~\cref{eqn:B} ensures \( \Psi(R) \to \infty \) as \( r^T R^T v \to \cos \theta \).
-Therefore, the inequality constraint is always satisfied given that the desired equilibrium lies in the feasible set.
-
-\subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
-%	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
-%	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
-%	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
-%	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
-%	We know that \( B \to \infty \) as the constraint is neared. 
-%	We assume that \( B > \psi \) which implies that \( A < 1 \).
-%	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
-%	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
-	The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
-	This implies that that both \( A(R) \) and \( B(R) \) are also bounded which shows~\cref{eqn:AB_bound}.
-
-	Next, we show~~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
-	The Frobenius norm \( \norm{E}_F \) is given in~\cite{LeeITCST13} as
-	\begin{gather*}
-		\norm{E}_F = \sqrt{\tr{E^T E}} = \frac{1}{2} \sqrt{\tr{G^2} + \tr{R^T R_d G}^2} .
-	\end{gather*}
-	Applying Rodrigues' formula and the Matlab symbolic toolbox, this is simplified to
-	\begin{gather*}
-		\norm{E}^2_F \leq \frac{1}{4} \parenth{\tr{G^2} + \tr{G}^2} \leq \frac{1}{2} \tr{G}^2 ,
-	\end{gather*}
-	which shows~\cref{eqn:E_bound}, since \( \norm{E} \leq \norm{E}_F \).
-
-	To show~\cref{eqn:F_bound}, we apply the Frobenius norm \( \norm{F}_F \):
-	\begin{gather*}
-		\norm{F}_F = \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} - 2 \tr{a^T b} \right. \\
-		\left.+ 2 \tr{a^T c } + \tr{b^T b}  - 2 \tr{b^T c} + \tr{c^T c}\right] .
-	\end{gather*}
-	where the terms \( a, b, \text{ and } c \) are given by
-	\begin{gather*}
-		a = r^T R r I , \quad	b = R^T v r^T , \quad c = \frac{R^T \hat{v} R r v^T R \hat{r}}{r^T R^T v - \cos \theta}.
-	\end{gather*}
-	A straightforward computation of \( a^T a \) shows that
-	\begin{gather*}
-		\tr{a^T a} = \parenth{v^T R r}^2 \tr{I} \leq 3 \beta^2 ,
-	\end{gather*}
-	where we used the fact that \( v^T R r = r^T R^T v < \beta \) from our given domain.
-	Similarly, one can show that \( \tr{a^T b} \) is equivalent to
-	\begin{gather*}
-		\tr{a^T b} = v^T R r \tr{R^T v r^T} = \parenth{v^T R r}^2 \leq \beta^2 ,
-	\end{gather*} 
-	where we used the fact that \( \tr{x y^T} = x^T y \).
-	The product \( \tr{a^T c} \) is given by
-	\begin{gather*}
-		\tr{a^T c} = \frac{v^T R r}{r^T R^T v - \cos \theta} \tr{\parenth{R^T v}^\vee \parenth{r v^T R} \hat{r} } ,
-	\end{gather*}
-	where we used the hat map property~\cref{eqn:RxR}.
-	One can show that \(\mathrm{tr}[a^T c] \leq 0 \) over the range \( -1 \leq v^T R r \leq \cos \theta \). 
-	Next, \( \tr{b^T b}\) is equivalent to
-	\begin{gather*}
-		\tr{b^T b} = \tr{r v^T R R^T v r^T} = 1 ,
-	\end{gather*}
-	since \( r,v \in \Sph^2\).
-	Finally, \( \tr{c^T c} \) is reduced to
-	\begin{gather*}
-		\tr{c^T c} = \tr{\hat{r} R^T v r^T \bracket{-I + R^T v v^T R} r v^T R \hat{r}} ,
-	\end{gather*}
-	where we used the fact that \( \hat{x}^2 = - \norm{x}^2 I + x x^T\).
-	Expanding and collecting like terms gives
-	\begin{gather*}
-		\tr{c^T c } = \frac{1 - 2\parenth{v^T R r}^2 + \parenth{v^T R r}^4}{\parenth{r^T R^T v - \cos \theta}^2} . 
-	\end{gather*}
-	Using the the given domain \( r^T R^T v \leq \beta \) gives the upper bound~\cref{eqn:F_bound}.
-	The bound on \( e_{R_A} \) is given in~\cref{eqn:psi_lower_bound} while \( e_{R_B} \) arises from the definition of the cross product \( \norm{a \times b} = \norm{a} \norm{b} \sin \theta \).
-	Finally, we can find the upper bound~\cref{eqn:eR_dot} as
-	\begin{gather*}
-		\norm{\dot{e}_R} \leq \parenth{\norm{B} \norm{E} + 2 \norm{e_{R_A}} \norm{e_{R_B}} + \norm{A}\norm{F}} \norm{e_\Omega} \, .
-	\end{gather*}
-	Using~\crefrange{eqn:AB_bound}{eqn:eRB_bound} one can define \( H \) in terms of known values.
-\subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}
-	Consider the Lyapunov function \( \mathcal{V} \) given by
-	\begin{gather}
-		\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , \label{eqn:v_adapt}
-	\end{gather}
-	over the domain \( D \) in~\cref{eqn:domain}.
-	From~\Cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
-	\begin{gather}
-		\mathcal{V} \leq z^T W z , \label{eqn:v_upper_bound}
-	\end{gather}
-	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrix \(W \in \R^{3 \times 3}\) is given by
-	\begin{gather*}
-		W = \begin{bmatrix}
-			k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
-			\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
-			0 & 0 & \frac{1}{2 k_\Delta}
-		\end{bmatrix} .
-	\end{gather*}
-	The time derivative of \( \mathcal{V}\) with the control inputs~\cref{eqn:adaptive_control} is given by
-	\begin{align}
-		\dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
-		&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
-	\end{align}
-	where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
-	The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
-	\begin{align*}
-		 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
-	\end{align*}
-	Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
-	\begin{gather*}
-		\dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
-	\end{gather*}
-	where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
-	\begin{gather}
-		M = \begin{bmatrix}
-			k_R c & \frac{k_\Omega c}{2} \\
-			\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
-		\end{bmatrix} .
-	\end{gather}
-	If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
-	This implies that $\dot{\mathcal{V}}$ is negative semidefinite and $\lim_{t\to\infty} \zeta=0$. 
-	As the Lyapunov function is non-increasing $z$ is uniformly bounded. 
-%	
-%	
-%	This implies that the Lyapunov function \( V \) is non-increasing and bounded from below.
-%	Furthermore, since \( V \) is nonincreasing the disturbance error \( e_\Delta\) is bounded.
-%	Since \( \dot{V} \) is uniformly continuous in time this implies that the zero equilibrium \( e_R, e_\Omega\) is stable in the sense of Lyapunov
-%	The domain \( D \) does that include the undesired equilibria and ensures that as \( e_R \to 0 \) the attitude also converges \( R \to R_d \).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2016-02-08 ACC16.2.tex
Cut detail to reduce length to 6 pages

@@
 
-% topological obstruction - smooth control system can only achieve almost global asymptotic stability
-
-% discuss issues with parameterizations
-
-Attitude control is typically studied using a variety of attitude parameterizations, such as Euler angles or quaternions~\cite{shuster1993}.
-All attitude parameterizations fail to represent the nonlinear configuration space both globally and uniquely~\cite{chaturvedi2011a}.
-For example, minimal attitude representations, such as Euler angle sequences or modified Rodriguez parameters, suffer from singularities.
-These attitude representations are not suitable for large angular slews.
-%In order to avoid singularities, the designer must carefully switch the chosen Euler angle sequence based on the operating region.
-%Another option is to artificially limit the operating region of the rigid body.
-%This ensures the system operates in a region free from singularities but limits the performance capabilities and ability to perform arbitrarily large angular maneuvers.
-Quaternions do not have singularities but they double cover the special orthogonal group.
-As a result, any physical attitude is represented by a pair of antipodal quaternions on the three-sphere.
-%An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
-During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}.
-%, where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.
-
 % introduce concept of state inequality constraints and how it creates a nonconvex region 
@@
 A conceptually straightforward approach is used in~\cite{hablani1999} to determine feasible attitude trajectories prior to implementation.
-The algorithm determines an intermediate point such that an unconstrained maneuver can be calculated for each subsegment.
-Typically, an optimal or easily implementable on-board control scheme for attitude maneuvers is applied to maneuver the vehicle along these segments.
+The algorithm determines an intermediate point such that an unconstrained maneuver can be calculated for each sub-interval.
 In this manner it is possible to accomplish constraint avoidance by linking several intermediary unconstrained maneuvers.
 While this method is conceptually simple, it is difficult to generalize for an arbitrary number of constraints.
-In addition, this approach is only applicable to problems where the selection of intermediate points are computationally feasible.
 
 The approach in~\cite{frazzoli2001} involves the use of randomized motion planning algorithms to solve the constrained attitude control problem.
-A graph is generated consisting of vertices from an initial attitude to a desired attitude. 
 A random iterative search is conducted to determine a path through a directed graph such that a given cost functional is minimized.
-The random search approach can only stochastically guarantee attitude convergence as it can be shown that as the number of vertices in the graph grow, the probability of nonconvergence goes to zero.
-However, the computational demand grows as the size of the graph is increased. 
-As a result, random search approaches are ill-suited to on-board implementation or in scenarios that require agile maneuvers.
+However, the random search approach can only stochastically guarantee attitude convergence.
+Typically, very large graphs are required which are ill-suited to on-board implementation or in scenarios that require agile maneuvers.
 
 Model predictive control for spacecraft attitude dynamics is studied in~\cite{guiggiani2014,kalabic2014,gupta2015}.
-These methods rely on linear or non-linear state dynamics to repeatedly solve a finite-time optimal control problem.
-As a result, model predictive control methods are also computational expensive and apply direct optimization methods to solve the necessary conditions for optimality.
-Therefore these methods are complicated to implement and not applicable for real-time control applications.
+This approach relies on linear or non-linear state prediction to repeatedly solve a finite time constrained optimal control problem.
+The necessary conditions for optimality are computed over a receding finite horizon using a direct method. 
+As a result,these methods are also computationally expensive and difficult to implement on-board.
 
@@
 The goal is the design of attractive and repulsive terms which drive the system toward or away from a certain state, respectively.
-%The goal is the design of an attractive function which drives the system towards the desired state.
-%Similarly, a repulsive function is constructed such that the system is directed away from the constraints. 
-The superposition of the these functions allows one to apply standard feedback control schemes for stabilization and tracking.
 More specifically, artificial potential functions have previously been applied to the spacecraft attitude control problem in~\cite{lee2011b,mcinnes1994}.
-However, both of these approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by the singularities of minimal representations or the ambiguity of quaternions.
-
-%By characterizing the attitude both globally and uniquely \(\SO\), we completely avoid issues associated with local parameterizations of the configuration manifold.
+However, both of these approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by the singularities or ambiguities.
 
@@
 We apply a potential function based approach developed directly on the nonlinear manifold \(\SO\). 
-By characterizing the attitude both globally and uniquely on \(\SO\), our approach avoids the issues of attitude parameterizations, such as kinematic singularities and ambiguities, and is geometrically exact.
-A new configuration error function on \(\SO\) with a logarithmic barrier function is proposed to avoid constrained regions. 
-Instead of calculating a priori trajectories, as in the geometric and randomized approaches, our approach results in a closed-loop attitude control system. 
-This makes it ideal for on-board implementation on UAV or spacecraft systems. 
-In addition, unlike previous approaches our control system can handle an arbitrary number of constrained regions without modification.
-
-Furthermore, we formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances. 
+We also formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances.
 The stability of the proposed control systems is verified via mathematically rigorous Lyapunov analysis on $\SO$. 
@@
 The effectiveness of this new approach is illustrated via numerical simulation and experimental results.% on a hexrotor aerial vehicle.
-
-%Our approach 
-%Finally, a rigorous Lyapunov analysis guarantees the stability of the proposed control system.
-%rather than probablistic convergence properties of the randomized approach.
-
-%We present a
-
-%In this work, we develop a geometric adaptive controller on \(\SO\) to reorient a rigid body in the presence of state inequality constraints.
-
-%Geometric control is concerned with the development of control systems for dynamic systems that evolve on nonlinear manifolds.
 
@@
 \end{equation}
-This form of uncertainty enters the system dynamics through the input channel and as a result is referred to as a matched uncertainty. 
-While this form of uncertainty is easier than the unmatched variety many physically realizable disturbances may be modeled in this manner.
-For example, orbital spacecraft are subject to gravity gradient torques caused by the non-spherical distribution of mass of both the spacecraft and central gravitational body.
-This form of disturbance may be represented as a body fixed torque on the vehicle.
-In addition, for typical scenarios, where the spacecraft is significantly smaller than the orbital radius, the disturbance torque may be assumed constant over short time intervals.
+This form of uncertainty enters the system dynamics through the input channel and is referred to as a matched uncertainty. 
+Many physically realizable disturbances may be modeled in this manner such as gravity gradient torques on orbital spacecraft.
 
@@
 In order to visualize the attitude error function on \( \SO \) we utilize a spherical coordinate representation.
-Recall that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth,and elevation.
-This coordinate system commonly used to define locations on the Earth in terms of a latitude and longitude.
-Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
 We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
@@
 We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \).
-Applying this method,~\cref{fig:config_error} allows us to visualize the error function on \( \SO \).
-The attractive error function, given by~\cref{eqn:A}, has been previously used for attitude control on \(\SO\).
+\cref{fig:config_error} allows us to visualize the error function on \( \SO \).
 The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum of \( A(R) \).
@@
 \end{figure}
+
 A sensor pointing direction is defined in the body frame of the hexrotor as \( r = [1,0,0]^T \).
@@
 When constrained to the spherical joint the hexrotor is capable of performing responsive attitude changes with high angular velocities.
-In addition, The on-board control and motion capture system operate at a discrete interval of approximately \SI{100}{\hertz}.
-It is possible for the system to violate the constraint between these discrete steps and cause numerical exceptions within the embedded software. 
-As a result, conservative control gains are chosen to ensure the hexrotor operates in a sedate manner and to allow sufficient time for the measurement and control software to operate.
+In addition, the on-board control and motion capture system operate at a discrete interval of approximately \SI{100}{\hertz}.
+It is possible for the system to violate the constraint between these discrete steps and cause numerical instability.
+We chose conservative control gains to  allow sufficient time for the measurement and control software to function correctly.
 

### 2016-02-09 ACC16.2.tex
Cut redundant sentences and now at exaclty 6 pages

@@
 
-Rigid body attitude control is an important problem for aerospace vehicles, ground and underwater vehicles, as well as robotic systems~\cite{hughes2004,wertz1978}.
+Rigid body attitude control is an important problem for aerospace vehicles, ground and underwater vehicles, as well as robotic systems~\cite{hughes2004}.
 One distinctive feature of the attitude dynamics of rigid bodies is that it evolves on a nonlinear manifold.
@@
 This approach relies on linear or non-linear state prediction to repeatedly solve a finite time constrained optimal control problem.
-The necessary conditions for optimality are computed over a receding finite horizon using a direct method. 
-As a result,these methods are also computationally expensive and difficult to implement on-board.
+The necessary conditions for optimality are continually computed over a receding finite horizon using a direct method. 
+As a result, these methods are also computationally expensive.
 
@@
 More specifically, artificial potential functions have previously been applied to the spacecraft attitude control problem in~\cite{lee2011b,mcinnes1994}.
-However, both of these approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by the singularities or ambiguities.
+However, both of these approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by singularities or ambiguities.
 
 This paper is focused on developing an adaptive attitude control scheme in the presence of attitude inequality constraints on \(\SO\).
-We apply a potential function based approach developed directly on the nonlinear manifold \(\SO\). 
+We apply a potential function based approach directly on the nonlinear manifold \(\SO\). 
 We also formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances.
@@
 We define an inertial reference frame and a body frame whose origin is at the center of mass and aligned with the principle directions of the body. 
-The configuration manifold of the attitude dynamics is the special orthogonal group:
-\begin{align*}
-	\SO = \{R\in\R^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\} ,
-\end{align*}
-where a rotation matrix $R\in\SO$ represents the transformation of the representation of a vector from the body-fixed frame to the inertial reference frame. 
+The configuration manifold of the attitude dynamics is the special orthogonal group: \(\SO = \{R\in\R^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\} \).
+The rotation matrix $R\in\SO$ represents the transformation of the representation of a vector from the body-fixed frame to the inertial reference frame. 
 The equations of motion are given by
@@
 This form of uncertainty enters the system dynamics through the input channel and is referred to as a matched uncertainty. 
-Many physically realizable disturbances may be modeled in this manner such as gravity gradient torques on orbital spacecraft.
+Many physically realizable disturbances may be modeled in this manner such as a gravity gradient torque.
 
 \subsection{State Inequality Constraint}
-
 The two-sphere is the manifold of unit-vectors in \( \R^3 \) such that \( \Sph^2 = \{ q \in \R^3 \,  \vert \, \norm{q} = 1 \}\).
@@
 A smooth control system is first developed assuming that there is  no disturbance, and then it is extended to include an adaptive update law for stabilization in the presence of unknown disturbances.
-The proposed attitude configuration error function and several properties are summarized as follows.
 
@@
 \begin{proof}
-For brevity the proof is available in~\cite{kulumani2016b}.
+For brevity, the proof is available in~\cite{kulumani2016b}.
 \end{proof}
@@
 In order to visualize the attitude error function on \( \SO \) we utilize a spherical coordinate representation.
-We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
-Using the elementary Euler rotations the rotation matrix is now defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
-We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \).
-\cref{fig:config_error} allows us to visualize the error function on \( \SO \).
-The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum of \( A(R) \).
+We parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
+Using the elementary Euler rotations the rotation matrix is defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
+We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \) as shown in~\cref{fig:config_error}.
+\( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum \(\lambda=\beta=\SI{0}{\degree}\).
 
 To incorporate the state inequality constraints we apply a logarithmic barrier term.
-Barrier functions are typically used in optimal control and motion planning applications.
-A visualization of the configuration error function is presented in~\cref{fig:avoid_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
+A visualization of the barrier function is presented in~\cref{fig:avoid_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
 We use the scale factor~\(\frac{1}{1+\cos \theta} \) to ensure that \( \Psi \) remains positive definite.
@@
 As \( \alpha \) is increased the impact of \( B(R) \) is reduced away from the constraint boundary. 
-The super position of the attractive and repulsive functions is shown in~\cref{fig:combined_error}.
-The control system is defined such that the attitude trajectory follows the negative gradient of \( \Psi \) towards the minimum at \( R = R_d \), while avoiding the constrained region.
+The superposition of the attractive and repulsive functions is shown in~\cref{fig:combined_error}.
+The control system allows the attitude trajectory follows the negative gradient of \( \Psi \) towards the minimum at \( R = R_d \), while avoiding the constraints.
 \begin{figure} 
@@
 		\diff{}{t} \parenth{\Psi} = e_R \cdot e_\Omega , \label{eqn:psi_dot}\\
-		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B(R) + e_{R_A} \dot{B(R)} + \dot{A(R)}e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
+		%\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B + e_{R_A} \dot{B} + \dot{A}e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
 		\diff{}{t} \parenth{e_{R_A}} = E(R, R_d) e_\Omega , \label{eqn:eRA_dot} \\
@@
 \begin{prop}[Attitude Control]\label{prop:att_control}
-	Given a desired attitude command \( \parenth{R_d, \Omega_d = 0} \), which satisfies the constraint~\cref{eq:constraint}, and positive constants \( k_R, k_\Omega \in \R \) we define a control input \( u \in \R^3 \) as follows
+	Given a desired attitude command \( \parenth{R_d, \Omega_d = 0} \), which satisfies the constraint~\cref{eqn:constraint}, and positive constants \( k_R, k_\Omega \in \R \) we define a control input \( u \in \R^3 \) as follows
 	\begin{gather}
@@
 \end{prop}
-
 \begin{proof}
-For brevity the proof is found in~\cite{kulumani2016b}.
+For brevity, the proof is found in~\cite{kulumani2016b}.
 \end{proof}
@@
 		\norm{E} \leq \frac{1}{\sqrt{2}} \tr{G}  , \label{eqn:E_bound} \\
-		\norm{F} \leq \frac{\parenth{\beta^2 + 1}\parenth{\beta - \cos \theta}^2 + 1 + \beta^2 \parenth{\beta^2-2}}{\alpha^2 \parenth{\beta-\cos \theta}^4} . \label{eqn:F_bound}
+		\norm{F} \leq \frac{\parenth{\beta^2 + 1}\parenth{\beta - \cos \theta}^2 + 1 + \beta^4-2 \beta^2}{\alpha^2 \parenth{\beta-\cos \theta}^4} . \label{eqn:F_bound}
 	\end{gather}
@@
 \begin{proof}
-For brevity the proof is found in~\cite{kulumani2016b}.
+For brevity, the proof is found in~\cite{kulumani2016b}.
 \end{proof}
@@
 Nonlinear adaptive controllers have been developed for attitude stabilization in terms of modified Rodriguez parameters and quaternions, as well as attitude tracking in terms of Euler angles. 
-The proposed control system is developed on \(\SO\) and avoids the singularities of Euler angles and Rodriguez parameters while incorporating state inequality constraints. 
-In addition, the unwinding and double coverage ambiguity of quaternions are also completely avoided. 
-The control system handles uncertain disturbances while avoiding constrained regions.
+The proposed control system is developed on \(\SO\) and avoids the issues inherent in attitude representations, while incorporating state inequality constraints. 
+In addition, the control system handles uncertain disturbances.
 
 Compared to the previous work on constrained attitude control, we present a geometrically exact control system without parameterizations.
-In addition, we incorporate state inequality constraints for the first time on \( \SO \).
+In addition, we incorporate state inequality constraints on \( \SO \).
 The presented control system is computed in real-time and offers significant computational advantages over previous iterative methods. 
@@
 The desired state is \( R_d = I,\Omega_d = 0\).
-\begin{table}%[htbp]
+\begin{table}[htbp]
 \caption{Constraint Parameters~\label{tab:constraints}}
@@
 Simulation results without the adaptive update law are shown in~\cref{fig:con}.
-Without the update law, the system does not achieve zero steady state error. 
-\Cref{fig:Psi_con} shows that the configuration error function does not converge to zero and there exist steady state errors.
-\Cref{fig:adapt} shows the results with the addition of the adaptive update law.
-The addition of the adaptive update law allows the system to converge to the desired attitude in the presence of constraints.
+Without the update law,~\cref{fig:Psi_con} shows that the configuration error function does not converge to zero and there exist steady state errors.
+\Cref{fig:adapt} shows that the addition of the adaptive update law the system converges to the desired attitude.
 The path of the body fixed sensor in the inertial frame, namely \( R r \), is illustrated in~\cref{fig:cad_adapt}.
@@
 	\item BLDC motors with BL-Ctrl-2.0 ESC via I2C.
-	\item Position and attitude over WiFi (TCP) communication from Vicon motion capture system.
-	\item Commands sent over WiFi to  onboard controller. 
+	\item Vicon motion capture system.
 \end{itemize}
@@
 It is possible for the system to violate the constraint between these discrete steps and cause numerical instability.
-We chose conservative control gains to  allow sufficient time for the measurement and control software to function correctly.
+We choose conservative control gains to  allow sufficient time for the measurement and control software to function correctly.
 
 There exist several sources of error in the experimental setup.
-The motion capture system uses a series of optical sensor to determine the relative position of several tracking markers. 
+The motion capture system uses a series of optical sensors to determine the relative position of several tracking markers. 
 These markers as well as the cameras must remain fixed to ensure accurate attitude measurement.
 In addition, the spherical joint is not fixed at the center of mass but is instead offset due to the physical structure of the hexrotor.
-As a result a disturbance moment is induced on the resultant motion.
+As a result a disturbance moment is induced on the system.
 
@@
 This will cause an increase in control input until the steady-state error is reduced. 
-Further tuning of the control gains would enable a faster response and a reduced settling time.
+Further tuning of the control gains would enable a reduced settling time.
 
@@
 
-%\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
+\addtolength{\textheight}{-12cm}
 

### 2016-02-09 ACC16.2.tex

--- 2016-02-07 ACC16.2.tex
@@
 
+In~\refeqn{Rdot}, the \textit{hat} map $\wedge :\R^{3}\rightarrow\so$ represents the transformation of a vector in $\R^{3}$ to a $3\times 3$ skew-symmetric matrix such that $\hat x y = x\times y$ for any $x,y\in\R^{3}$~\cite{bullo2004}.
+More explicitly, 
+\begin{align*}
+\hat x = \begin{bmatrix} 0 & -x_3 & x_2 \\ x_3 & 0 & -x_1 \\ -x_2 & x_1 & 0\end{bmatrix},
+\end{align*}
+for $x=[x_1,x_2,x_3]^T\in\R^{3}$. 
+The inverse of the hat map is denoted by the \textit{vee} map $\vee:\so\rightarrow\R^{3}$. 
+Several properties of the hat map are summarized as
+\begin{gather}
+%    \hat x y = x\times y = - y\times x = - \hat y x,\\
+    x\cdot \hat y z = y\cdot \hat z x,\quad \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z\label{eqn:STP},\\
+%    \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z,\label{eqn:VTP}\\
+%    C^TC=-C^T\hat e_3^2 C = I_2
+%    \hat x^T \hat x = (x^T x) I - x x^T,\\
+%    \hat x \hat y \hat x=-(y^Tx)\hat x,\\
+%    -\frac{1}{2}\tr{\hat x \hat y} = x^T y,\\
+    \widehat{x\times y} = \hat x \hat y -\hat y \hat x = yx^T-xy^T,\label{eqn:hatxy}\\
+    %\tr{\hat x A}=
+    \tr{A\hat x }=\frac{1}{2}\tr{\hat x (A-A^T)}=-x^T (A-A^T)^\vee,\label{eqn:hat1}\\
+%    \widehat{Ax} = \hat x \parenth{\frac{1}{2}\tr{A}I-A} + \parenth{\frac{1}{2}\tr{A}I-A}^T \hat x,\\
+    \hat x  A+A^T\hat x=(\braces{\tr{A}I_{3\times 3}-A}x)^{\wedge},\label{eqn:xAAx}\\
+R\hat x R^T = (Rx)^\wedge,\quad 
+R(x\times y) = Rx\times Ry\label{eqn:RxR}
+%,\label{eqn:Rxy}
+\end{gather}
+for any $x,y,z\in\R^{3}$, $A\in\R^{3\times 3}$ and $R\in\SO$. 
+Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\R^n$ and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively.
+The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A} \leq \norm{A}_F = \sqrt{\tr{A^T A}} \leq \sqrt{\text{rank}(A)} \norm{A} \).
+
 \subsection{State Inequality Constraint}
@@
 \begin{proof}
-For brevity the proof is available in~\cite{kulumani2016b}.
+See~\Cref{proof:config_error}.
 \end{proof}
@@
 \begin{proof}
-For brevity the proof is found in~\cite{kulumani2016b}.
+See~\Cref{proof:error_dyn}.
 \end{proof}
@@
 \begin{proof}
-For brevity the proof is found in~\cite{kulumani2016b}.
+See~\Cref{proof:att_control}.
 \end{proof}
@@
 \begin{proof}
-For brevity the proof is found in~\cite{kulumani2016b}.
+See~\Cref{proof:eR_dot_bound}.
 \end{proof}
@@
 \begin{proof}
-For brevity the proof is found in~\cite{kulumani2016b}.
+See~\Cref{proof:adaptive_control}.
 \end{proof}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+\subsection{Proof of~\Cref{prop:config_error}}\label{proof:config_error}
+To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a positive definite function about \( R = R_d \)~\cite{bullo2004}.
+The constraint angle is assumed \( \ang{0} \leq \theta \leq \ang{90} \) such that \( 0 \leq \cos \theta \).
+The term \( r^T R^T v \) represents the cosine of the angle between the body fixed vector \( r \) and the inertial vector \( v \). 
+It follows that
+\begin{align*}
+	0 \leq  \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta} \leq 1 ,
+\end{align*}
+for all \( R \in \SO \). 
+As a result, its negative logarithm is always positive and from~\cref{eqn:B}, \(1 < B\).
+The error function \( \Psi = A B \) is composed of two positive terms and is therefore also positive definite, and it is minimized at \( R = R_d \).
+
+Next, we consider~\cref{item:prop_era}.
+The variation of~\cref{eqn:A} is taken with respect to \( \delta R = R \hat \eta \) as
+\begin{align*}
+	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee ,
+%	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
+\end{align*}
+where we used~\cref{eqn:hat1}.
+
+A straightforward application of the chain and product rules of differentiation allows us to show~\cref{item:prop_erb} as
+\begin{align*}
+	\dirDiff{B}{R} &=  \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} ,
+%	-\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta} \right) \right]
+\end{align*}
+where the scalar triple product~\cref{eqn:STP} was used.
+
+%To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
+%The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
+%\begin{align*}
+%	Q = R_d^T R = 
+%	\begin{bmatrix}
+%		q_{11} & q_{12} & q_{13} \\
+%		q_{21} & q_{22} & q_{23} \\
+%		q_{31} & q_{32} & q_{33}
+%	\end{bmatrix} .
+%\end{align*}
+%Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
+%\begin{subequations}
+%\begin{align}
+%	g_3 q_{32} &= g_2 q_{23} , \\
+%	g_1 q_{13} &= g_3 q_{31} , \\
+%	g_2 q_{21} &= g_1 q_{12} .
+%\end{align}
+%\end{subequations}
+%These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
+%Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
+%\begin{subequations}
+%\begin{align}
+%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \\
+%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 , \\
+%	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 .
+%\end{align}
+%\end{subequations}
+%As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
+%Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
+The critical points of \( e_{R_A} \) are derived in~\cite{bullo2004}.
+There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180}.
+The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
+This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \).
+Since we assume the system will not operate in violation of the constraints, the addition of the barrier function does not add additional critical points to the control system.
+The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
+The proof of \( \norm{e_{R_A}} \) given by~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
+\subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
+From the kinematics~\cref{eqn:Rdot} and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
+\begin{gather*}
+	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega .
+\end{gather*}
+Applying this to the time derivative of~\cref{eqn:A} gives
+\begin{gather*}
+	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} .
+\end{gather*}
+Applying~\cref{eqn:hat1} into this shows~\cref{eqn:A_dot}.
+Next, the time derivative of the repulsive error function is given by
+\begin{gather*}
+	\diff{}{t} (B) = \frac{r^T \parenth{\hat{\Omega} R^T} v}{\alpha \parenth{r^T R^T v - \cos \theta}} .
+\end{gather*}
+Using the scalar triple product, given by~\cref{eqn:STP}, one can reduce this to~\cref{eqn:B_dot}.
+The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
+\begin{gather*}
+	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee .
+\end{gather*}
+Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eqn:eRA_dot,eqn:E}.
+
+We take the time derivative of the repulsive attitude error vector, \( e_{R_B} \), as
+\begin{gather*}
+	\diff{}{t}( e_{R_B} )= a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r ,
+\end{gather*}
+with \( a \in \R \) and \( b \in \R\) given by 
+\begin{gather*}
+	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} , \,
+	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} .
+\end{gather*}
+Using the scalar triple product from~\cref{eqn:STP} as \( r \cdot \Omega \times \parenth{R^T v} = \parenth{R^T v} \cdot r \times \Omega \) gives~\cref{eqn:eRB_dot,eqn:F}.
+
+We show the time derivative of the configuration error function as
+\begin{gather*}
+	\diff{}{t} (\Psi) = \dot{A} B + A \dot{B} .
+\end{gather*}
+A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and appplying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
+We show~\cref{eqn:eW_dot} by rearranging~\cref{eqn:Wdot} as 
+\begin{align*}
+	\diff{}{t} e_\Omega = \dot{\Omega} = J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } .
+\end{align*}
+
+\subsection{Proof of~\Cref{prop:att_control}}\label{proof:att_control}
+Consider the following Lyapunov function:
+\begin{gather}
+	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d) . \label{eqn:v_nodist}
+\end{gather}
+From~\cref{item:prop_psi_psd} of~\Cref{prop:config_error}, \(\mathcal{V} \geq 0 \).
+Using~\cref{eqn:eW_dot,eqn:psi_dot} with \( \Delta = 0 \), the time derivative of \( \mathcal{V} \) is given by
+\begin{align}
+	\dot{\mathcal{V}} &= -k_\Omega \norm{e_\Omega}^2 . \label{eqn:vdot_nodist}
+%	e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
+\end{align}
+Since \( \mathcal{V} \) is positive definite and \( \dot{\mathcal{V}} \) is negative semi-definite, the zero equilibrium point \( e_R, e_\Omega \) is stable in the sense of Lyapunov. 
+This also implies \( \lim_{t\to\infty} \norm{e_\Omega} = 0 \) and \( \norm{e_R} \) is uniformly bounded, as the Lyapunov function is non-increasing.
+From \refeqn{eRA_dot} and \refeqn{eRB_dot}, $\lim_{t\to\infty} \dot e_R =0$.
+One can show that \( \norm{\ddot{e}_R} \) is bounded.
+From Barbalat's Lemma, it follows \( \lim_{t\to\infty}\norm{\dot{e}_R} = 0 \)~\cite[Lemma 8.2]{khalil1996}. 
+Therefore, the equilibrium is asymptotically stable.
+
+Furthermore, since \( \dot{\mathcal{V}} \leq 0 \) the Lyapunov function is uniformly bounded which implies 
+\begin{align*}
+	\Psi(R(t)) \leq \mathcal{V}(t) \leq \mathcal{V}(0) .
+\end{align*}
+In addition, the logarithmic term in~\cref{eqn:B} ensures \( \Psi(R) \to \infty \) as \( r^T R^T v \to \cos \theta \).
+Therefore, the inequality constraint is always satisfied given that the desired equilibrium lies in the feasible set.
+
+\subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
+%	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
+%	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
+%	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
+%	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
+%	We know that \( B \to \infty \) as the constraint is neared. 
+%	We assume that \( B > \psi \) which implies that \( A < 1 \).
+%	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
+%	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
+	The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
+	This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
+	Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
+
+	Next, we show~~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
+	The Frobenius norm \( \norm{E}_F \) is given in~\cite{LeeITCST13} as
+	\begin{gather*}
+		\norm{E}_F = \sqrt{\tr{E^T E}} = \frac{1}{2} \sqrt{\tr{G^2} + \tr{R^T R_d G}^2} .
+	\end{gather*}
+	Applying Rodrigues' formula and the Matlab symbolic toolbox, this is simplified to
+	\begin{gather*}
+		\norm{E}^2_F \leq \frac{1}{4} \parenth{\tr{G^2} + \tr{G}^2} \leq \frac{1}{2} \tr{G}^2 ,
+	\end{gather*}
+	which shows~\cref{eqn:E_bound}, since \( \norm{E} \leq \norm{E}_F \).
+
+	To show~\cref{eqn:F_bound}, we apply the Frobenius norm \( \norm{F}_F \):
+	\begin{gather*}
+		\norm{F}_F = \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} - 2 \tr{a^T b} \right. \\
+		\left.+ 2 \tr{a^T c } + \tr{b^T b}  - 2 \tr{b^T c} + \tr{c^T c}\right] .
+	\end{gather*}
+	where the terms \( a, b, \text{ and } c \) are given by
+	\begin{gather*}
+		a = r^T R r I , \quad	b = R^T v r^T , \quad c = \frac{R^T \hat{v} R r v^T R \hat{r}}{r^T R^T v - \cos \theta}.
+	\end{gather*}
+	A straightforward computation of \( a^T a \) shows that
+	\begin{gather*}
+		\tr{a^T a} = \parenth{v^T R r}^2 \tr{I} \leq 3 \beta^2 ,
+	\end{gather*}
+	where we used the fact that \( v^T R r = r^T R^T v < \beta \) from our given domain.
+	Similarly, one can show that \( \tr{a^T b} \) is equivalent to
+	\begin{gather*}
+		\tr{a^T b} = v^T R r \tr{R^T v r^T} = \parenth{v^T R r}^2 \leq \beta^2 ,
+	\end{gather*} 
+	where we used the fact that \( \tr{x y^T} = x^T y \).
+	The product \( \tr{a^T c} \) is given by
+	\begin{gather*}
+		\tr{a^T c} = \frac{v^T R r}{r^T R^T v - \cos \theta} \tr{\parenth{R^T v}^\vee \parenth{r v^T R} \hat{r} } ,
+	\end{gather*}
+	where we used the hat map property~\cref{eqn:RxR}.
+	One can show that \(\mathrm{tr}[a^T c] \leq 0 \) over the range \( -1 \leq v^T R r \leq \cos \theta \). 
+	Next, \( \tr{b^T b}\) is equivalent to
+	\begin{gather*}
+		\tr{b^T b} = \tr{r v^T R R^T v r^T} = 1 ,
+	\end{gather*}
+	since \( r,v \in \Sph^2\).
+	Finally, \( \tr{c^T c} \) is reduced to
+	\begin{gather*}
+		\tr{c^T c} = \tr{\hat{r} R^T v r^T \bracket{-I + R^T v v^T R} r v^T R \hat{r}} ,
+	\end{gather*}
+	where we used the fact that \( \hat{x}^2 = - \norm{x}^2 I + x x^T\).
+	Expanding and collecting like terms gives
+	\begin{gather*}
+		\tr{c^T c } = \frac{1 - 2\parenth{v^T R r}^2 + \parenth{v^T R r}^4}{\parenth{r^T R^T v - \cos \theta}^2} . 
+	\end{gather*}
+	Using the the given domain \( r^T R^T v \leq \beta \) gives the upper bound~\cref{eqn:F_bound}.
+	The bound on \( e_{R_A} \) is given in~\cref{eqn:psi_lower_bound} while \( e_{R_B} \) arises from the definition of the cross product \( \norm{a \times b} = \norm{a} \norm{b} \sin \theta \).
+	Finally, we can find the upper bound~\cref{eqn:eR_dot} as
+	\begin{gather*}
+		\norm{\dot{e}_R} \leq \parenth{\norm{B} \norm{E} + 2 \norm{e_{R_A}} \norm{e_{R_B}} + \norm{A}\norm{F}} \norm{e_\Omega} \, .
+	\end{gather*}
+	Using~\crefrange{eqn:AB_bound}{eqn:eRB_bound} one can define \( H \) in terms of known values.
+\subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}
+	Consider the Lyapunov function \( \mathcal{V} \) given by
+	\begin{gather}
+		\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , \label{eqn:v_adapt}
+	\end{gather}
+	over the domain \( D \) in~\cref{eqn:domain}.
+	From~\Cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
+	\begin{gather}
+		\mathcal{V} \leq z^T W z , \label{eqn:v_upper_bound}
+	\end{gather}
+	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrix \(W \in \R^{3 \times 3}\) is given by
+	\begin{gather*}
+		W = \begin{bmatrix}
+			k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
+			\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
+			0 & 0 & \frac{1}{2 k_\Delta}
+		\end{bmatrix} .
+	\end{gather*}
+	The time derivative of \( \mathcal{V}\) with the control inputs~\cref{eqn:adaptive_control} is given by
+	\begin{align}
+		\dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
+		&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
+	\end{align}
+	where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
+	The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
+	\begin{align*}
+		 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
+	\end{align*}
+	Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
+	\begin{gather*}
+		\dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
+	\end{gather*}
+	where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
+	\begin{gather}
+		M = \begin{bmatrix}
+			k_R c & \frac{k_\Omega c}{2} \\
+			\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
+		\end{bmatrix} .
+	\end{gather}
+	If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
+	This implies that $\dot{\mathcal{V}}$ is negative semidefinite and $\lim_{t\to\infty} \zeta=0$. 
+	As the Lyapunov function is non-increasing $z$ is uniformly bounded. 
+%	
+%	
+%	This implies that the Lyapunov function \( V \) is non-increasing and bounded from below.
+%	Furthermore, since \( V \) is nonincreasing the disturbance error \( e_\Delta\) is bounded.
+%	Since \( \dot{V} \) is uniformly continuous in time this implies that the zero equilibrium \( e_R, e_\Omega\) is stable in the sense of Lyapunov
+%	The domain \( D \) does that include the undesired equilibria and ensures that as \( e_R \to 0 \) the attitude also converges \( R \to R_d \).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2016-02-12 ACC16.2.tex
Remove new when discussing config error function
Add comments from Dr. Lee
Final revision from Dr. Lee - said to upload after completing

--- 2016-02-09 ACC16.2.tex
@@
 In short, the proposed attitude control system in the presence of inequality constraints is computationally efficient and able to handle uncertain disturbances. 
-The effectiveness of this new approach is illustrated via numerical simulation and experimental results.% on a hexrotor aerial vehicle.
+The effectiveness of this approach is illustrated via numerical simulation and experimental results.% on a hexrotor aerial vehicle.
 
@@
 For example, \( r \) may represent the pointing direction of an on-board optical sensor.
-We define \( v \in \Sph^2 \) to be a unit vector from the mass center of the rigid body towards an undesired pointing direction and represented in the inertial reference frame.
+We define \( v \in \Sph^2 \) to be a unit vector from the mass center of the rigid body toward an undesired pointing direction and represented in the inertial reference frame.
 For example, \( v \) may represent the inertial direction of a bright celestial object or the incoming direction of particles or other debris.
@@
 \begin{proof}
-For brevity, the proof is available in~\cite{kulumani2016b}.
+For brevity, the proof is relegated to~\cite{kulumani2016b}.
 \end{proof}
@@
 \begin{proof}
-For brevity the proof is found in~\cite{kulumani2016b}.
+For brevity, the proof is relegated to~\cite{kulumani2016b}.
 \end{proof}
 
-\subsection{Attitude Control without disturbance}
+\subsection{Attitude Control without Disturbance}
 We introduce a nonlinear geometric controller for the attitude stabilization of a rigid body.
@@
 \begin{proof}
-For brevity, the proof is found in~\cite{kulumani2016b}.
+For brevity, the proof is relegated to~\cite{kulumani2016b}.
 \end{proof}
@@
 This proposition only guarantees that the attitude error vector \( e_R \) asymptotically converges to zero.
-However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are three additional critical points of \( \Psi \) where \( e_R = 0 \).
+However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are at most three additional critical points of \( \Psi \) where \( e_R = 0 \) and \( R^T v = \pm r \).
 At an undesired equilibrium \( R = \exp{ \parenth{\pi \hat{e}_i}} R_d \) and \( e_\Omega =0 \).
@@
 We extend the results of the previous section with the addition of a fixed but unknown disturbance \( \Delta \).
-This scenario is typical of many mechanical systems and represents unmodelled dynamics or external moments acting on the system.
+This scenario is typical of many mechanical systems and represents unmodeled dynamics or external moments acting on the system.
 For example, Earth orbiting spacecraft typically experience a torque due to a gravitational gradient.
@@
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{eR_adapt} 
-		\caption{Attitude error vector \(e_R\) } \label{fig:eR_adapt} 
-	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
-	\begin{subfigure}[htbp]{0.5\columnwidth} 
 		\includegraphics[width=\columnwidth]{Psi_adapt} 
 		\caption{Configuration error \( \Psi \)} \label{fig:Psi_adapt} 
+	\end{subfigure}~
+	\begin{subfigure}[htbp]{0.5\columnwidth} 
+		\includegraphics[width=\columnwidth]{constraint_angles} 
+		\caption{Angle to constraints} \label{fig:con_angles} 
 	\end{subfigure}
@@
 The inequality constraints from~\Cref{tab:constraints} are depicted as red cones, where the cone half angle is \( \theta \).
-The control system is able to asymptotically converge to zero attitude error.
+The control system is able to asymptotically converge to zero attitude error while avoiding the constrained regions.
+\Cref{fig:con_angle} shows that the angle \( \arccos(r^T R^T v_i) \) to each constraint in~\cref{tab:constraints} is satisfied for the entire maneuver.
 In addition, the estimate of the disturbance converges to the the true value.
@@
 \section{Experiment on Hexrotor UAV}
-A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory(FDCL) at the George Washington University~\cite{kaufman2014}.
+A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory (FDCL) at the George Washington University~\cite{kaufman2014}.
 The UAV is composed of three pairs of counter-rotating propellers. 
@@
 The experimental results are shown in~\Cref{fig:exp}.
-In order to maneuver the system "close" to the constrained zone we utilize several intermediary set points on either side of the obstacle.
+In order to maneuver the system ``close" to the constrained zone we utilize several intermediary set points on either side of the obstacle.
 From the initial attitude the hexrotor rotates to the first set point, pauses, and then continues around the obstacle to the second set point before continuing toward the desired attitude.

### 2016-02-12 ACC16.2.tex
Add comments to long version from Dr. Lee

--- 2016-02-09 ACC16.2.tex
@@
 The super position of the attractive and repulsive functions is shown in~\cref{fig:combined_error}.
-The control system is defined such that the attitude trajectory follows the negative gradient of \( \Psi \) towards the minimum at \( R = R_d \), while avoiding the constrained region.
+The control system is defined such that the attitude trajectory follows the negative gradient of \( \Psi \) toward the minimum at \( R = R_d \), while avoiding the constrained region.
 \begin{figure} 
@@
 This proposition only guarantees that the attitude error vector \( e_R \) asymptotically converges to zero.
-However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are three additional critical points of \( \Psi \) where \( e_R = 0 \).
+However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are at most three additional critical points of \( \Psi \) where \( e_R = 0 \) and \( R^T v = \pm r\).
 At an undesired equilibrium \( R = \exp{ \parenth{\pi \hat{e}_i}} R_d \) and \( e_\Omega =0 \).
@@
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{eR_adapt} 
-		\caption{Attitude error vector \(e_R\) } \label{fig:eR_adapt} 
+		\includegraphics[width=\columnwidth]{Psi_adapt} 
+		\caption{Configuration error \( \Psi \)} \label{fig:Psi_adapt} 
 	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{Psi_adapt} 
-		\caption{Configuration error \( \Psi \)} \label{fig:Psi_adapt} 
+		\includegraphics[width=\columnwidth]{constraint_angles} 
+		\caption{Angle to constraints} \label{fig:con_angles} 
 	\end{subfigure}
@@
 The control system is able to asymptotically converge to zero attitude error.
+\Cref{fig:con_angles} shows that the angle \( \arccos(r^T R^T v_i) \) to each constraint is satisfied for the entire maneuver.
 In addition, the estimate of the disturbance converges to the the true value.

### 2016-02-13 ACC16.2.tex
Add more corrections to long version

@@
 
-\subsection{Attitude Control without disturbance}
+\subsection{Attitude Control without Disturbance}
 We introduce a nonlinear geometric controller for the attitude stabilization of a rigid body.

### 2016-02-13 ACC16.2.tex
Correct some errors and typos
This version will be uploaded to arxiv for later citation

@@
 
-% MORE DETAIL ON CONTRIBUTIONS 
-% EXPLICITLY STATE - first time for constraints to be incorportated on SO(3) with barrier function
-% Consider adaptive control which allows for stabilization in the presence of uncertain terms
-% Benefits over previous approach -
-% Developed on SO(3) - avoids issues of singularities and ambiguities of quaternion approach
-% Geometric approach - requires a priori calculation of trajectory. not robust to uncertainties or changes in configuraiton
-% Random/Graph approach -computationally expensive. requires a priori calculation of trajectory
-
 % Previous potential function approach - developed using att parameterizations - singularities/ambiguities
@@
 
-%By characterizing the attitude both globally and uniquely \(\SO\), we completely avoid issues associated with local parameterizations of the configuration manifold.
-
 This paper is focused on developing an adaptive attitude control scheme in the presence of attitude inequality constraints on \(\SO\).
@@
 By characterizing the attitude both globally and uniquely on \(\SO\), our approach avoids the issues of attitude parameterizations, such as kinematic singularities and ambiguities, and is geometrically exact.
-A new configuration error function on \(\SO\) with a logarithmic barrier function is proposed to avoid constrained regions. 
+A configuration error function on \(\SO\) with a logarithmic barrier function is proposed to avoid constrained regions. 
 Instead of calculating a priori trajectories, as in the geometric and randomized approaches, our approach results in a closed-loop attitude control system. 
@@
 In short, the proposed attitude control system in the presence of inequality constraints is computationally efficient and able to handle uncertain disturbances. 
-The effectiveness of this new approach is illustrated via numerical simulation and experimental results.% on a hexrotor aerial vehicle.
-
-%Our approach 
-%Finally, a rigorous Lyapunov analysis guarantees the stability of the proposed control system.
-%rather than probablistic convergence properties of the randomized approach.
-
-%We present a
-
-%In this work, we develop a geometric adaptive controller on \(\SO\) to reorient a rigid body in the presence of state inequality constraints.
-
-%Geometric control is concerned with the development of control systems for dynamic systems that evolve on nonlinear manifolds.
+The effectiveness of this approach is illustrated via numerical simulation and experimental results.% on a hexrotor aerial vehicle.
 
@@
 In order to visualize the attitude error function on \( \SO \) we utilize a spherical coordinate representation.
-Recall that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth,and elevation.
-This coordinate system commonly used to define locations on the Earth in terms of a latitude and longitude.
+Recall that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth, and elevation.
+This coordinate system is commonly used to define locations on the Earth in terms of a latitude and longitude.
 Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
@@
 As \( \alpha \) is increased the impact of \( B(R) \) is reduced away from the constraint boundary. 
-The super position of the attractive and repulsive functions is shown in~\cref{fig:combined_error}.
+The superposition of the attractive and repulsive functions is shown in~\cref{fig:combined_error}.
 The control system is defined such that the attitude trajectory follows the negative gradient of \( \Psi \) toward the minimum at \( R = R_d \), while avoiding the constrained region.
@@
 		\diff{}{t} \parenth{\Psi} = e_R \cdot e_\Omega , \label{eqn:psi_dot}\\
-		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B(R) + e_{R_A} \dot{B(R)} + \dot{A(R)}e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
+		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B(R) + e_{R_A} \dot{B}(R) + \dot{A}(R)e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
 		\diff{}{t} \parenth{e_{R_A}} = E(R, R_d) e_\Omega , \label{eqn:eRA_dot} \\
@@
 
-%This results in \( A \) having a value of \( g_1 + g_2, g_2 + g_3 \) or \( g_3 + g_1 \).
-%At any of these undesired equilibria we have \( V = k \). 
-%We define an augmented Lyapunov function as
-%\begin{align*}
-%	W = k - V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \parenth{\frac{k}{k_R}+ \Psi(R,R_d)} .
-%\end{align*}
-%We can choose an attitude \( R \) arbitrarily close to the equilibrium point \( \exp{ \parenth{\pi \hat{e}_i}} R_d \) such that the \( k_R \parenth{\frac{k}{k_R}+\Psi }> 0 \).
-%This is due to the fact that \( \Psi \) is positive definite about \( R = R_d \) as shown in~\cref{item:prop_psi_psd}.
-%If \( e_\Omega \) is sufficiently small this results in \( W > 0 \) and \( \dot{W} = -\dot{V} > 0\) from~\cref{eqn:vdot_nodist}.
-%According to Chateav's theorem, the undesired equilibria are unstable~\cite{khalil1996}.
 \subsection{Adaptive Control}
 We extend the results of the previous section with the addition of a fixed but unknown disturbance \( \Delta \).
-This scenario is typical of many mechanical systems and represents unmodelled dynamics or external moments acting on the system.
+This scenario is typical of many mechanical systems and represents unmodeled dynamics or external moments acting on the system.
 For example, Earth orbiting spacecraft typically experience a torque due to a gravitational gradient.
@@
 The control system is able to asymptotically converge to zero attitude error.
-\Cref{fig:con_angles} shows that the angle \( \arccos(r^T R^T v_i) \) to each constraint is satisfied for the entire maneuver.
-In addition, the estimate of the disturbance converges to the the true value.
+\Cref{fig:con_angles} shows that the angle \( \arccos(r^T R^T v_i) \) between the body fixed sensor and each constraint is satisfied for the entire maneuver.
+In addition, the estimate of the disturbance converges to the the true value as shown in~\cref{fig:delta_adapt}.
 
@@
 There exist several sources of error in the experimental setup.
-The motion capture system uses a series of optical sensor to determine the relative position of several tracking markers. 
+The motion capture system uses a series of optical sensors to determine the relative position of several tracking markers. 
 These markers as well as the cameras must remain fixed to ensure accurate attitude measurement.

### 2016-02-13 ACC16.2.tex
Correct spelling error
Correct spelling mistake

@@
 For example, it is impossible to achieve global attitude stabilization using continuous time-invariant feedback~\cite{bhat2000}.
-
-% topological obstruction - smooth control system can only achieve almost global asymptotic stability
-
-% discuss issues with parameterizations
-
-Attitude control is typically studied using a variety of attitude parameterizations, such as Euler angles or quaternions~\cite{shuster1993}.
-All attitude parameterizations fail to represent the nonlinear configuration space both globally and uniquely~\cite{chaturvedi2011a}.
-For example, minimal attitude representations, such as Euler angle sequences or modified Rodriguez parameters, suffer from singularities.
-These attitude representations are not suitable for large angular slews.
-%In order to avoid singularities, the designer must carefully switch the chosen Euler angle sequence based on the operating region.
-%Another option is to artificially limit the operating region of the rigid body.
-%This ensures the system operates in a region free from singularities but limits the performance capabilities and ability to perform arbitrarily large angular maneuvers.
-Quaternions do not have singularities but they double cover the special orthogonal group.
-As a result, any physical attitude is represented by a pair of antipodal quaternions on the three-sphere.
-%An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
-During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}.
-%, where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.
 
@@
 A conceptually straightforward approach is used in~\cite{hablani1999} to determine feasible attitude trajectories prior to implementation.
-The algorithm determines an intermediate point such that an unconstrained maneuver can be calculated for each subsegment.
-Typically, an optimal or easily implementable on-board control scheme for attitude maneuvers is applied to maneuver the vehicle along these segments.
+The algorithm determines an intermediate point such that an unconstrained maneuver can be calculated for each sub-interval.
 In this manner it is possible to accomplish constraint avoidance by linking several intermediary unconstrained maneuvers.
 While this method is conceptually simple, it is difficult to generalize for an arbitrary number of constraints.
-In addition, this approach is only applicable to problems where the selection of intermediate points are computationally feasible.
 
 The approach in~\cite{frazzoli2001} involves the use of randomized motion planning algorithms to solve the constrained attitude control problem.
-A graph is generated consisting of vertices from an initial attitude to a desired attitude. 
 A random iterative search is conducted to determine a path through a directed graph such that a given cost functional is minimized.
-The random search approach can only stochastically guarantee attitude convergence as it can be shown that as the number of vertices in the graph grow, the probability of nonconvergence goes to zero.
-However, the computational demand grows as the size of the graph is increased. 
-As a result, random search approaches are ill-suited to on-board implementation or in scenarios that require agile maneuvers.
+However, the random search approach can only stochastically guarantee attitude convergence.
+Typically, very large graphs are required which are ill-suited to on-board implementation or in scenarios that require agile maneuvers.
 
 Model predictive control for spacecraft attitude dynamics is studied in~\cite{guiggiani2014,kalabic2014,gupta2015}.
-These methods rely on linear or non-linear state dynamics to repeatedly solve a finite-time optimal control problem.
-As a result, model predictive control methods are also computational expensive and apply direct optimization methods to solve the necessary conditions for optimality.
-Therefore these methods are complicated to implement and not applicable for real-time control applications.
+This approach relies on linear or non-linear state prediction to repeatedly solve a finite time constrained optimal control problem.
+The necessary conditions for optimality are continually computed over a receding finite horizon using a direct method. 
+As a result, these methods are also computationally expensive.
+
+% MORE DETAIL ON CONTRIBUTIONS 
+% EXPLICITLY STATE - first time for constraints to be incorportated on SO(3) with barrier function
+% Consider adaptive control which allows for stabilization in the presence of uncertain terms
+% Benefits over previous approach -
+% Developed on SO(3) - avoids issues of singularities and ambiguities of quaternion approach
+% Geometric approach - requires a priori calculation of trajectory. not robust to uncertainties or changes in configuraiton
+% Random/Graph approach -computationally expensive. requires a priori calculation of trajectory
 
@@
 The goal is the design of attractive and repulsive terms which drive the system toward or away from a certain state, respectively.
-%The goal is the design of an attractive function which drives the system towards the desired state.
-%Similarly, a repulsive function is constructed such that the system is directed away from the constraints. 
-The superposition of the these functions allows one to apply standard feedback control schemes for stabilization and tracking.
 More specifically, artificial potential functions have previously been applied to the spacecraft attitude control problem in~\cite{lee2011b,mcinnes1994}.
-However, both of these approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by the singularities of minimal representations or the ambiguity of quaternions.
+However, both of these approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by singularities or ambiguities.
 
 This paper is focused on developing an adaptive attitude control scheme in the presence of attitude inequality constraints on \(\SO\).
-We apply a potential function based approach developed directly on the nonlinear manifold \(\SO\). 
-By characterizing the attitude both globally and uniquely on \(\SO\), our approach avoids the issues of attitude parameterizations, such as kinematic singularities and ambiguities, and is geometrically exact.
-A configuration error function on \(\SO\) with a logarithmic barrier function is proposed to avoid constrained regions. 
-Instead of calculating a priori trajectories, as in the geometric and randomized approaches, our approach results in a closed-loop attitude control system. 
-This makes it ideal for on-board implementation on UAV or spacecraft systems. 
-In addition, unlike previous approaches our control system can handle an arbitrary number of constrained regions without modification.
-
-Furthermore, we formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances. 
+We apply a potential function based approach directly on the nonlinear manifold \(\SO\). 
+We also formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances.
 The stability of the proposed control systems is verified via mathematically rigorous Lyapunov analysis on $\SO$. 
@@
 \end{equation}
-This form of uncertainty enters the system dynamics through the input channel and as a result is referred to as a matched uncertainty. 
-While this form of uncertainty is easier than the unmatched variety many physically realizable disturbances may be modeled in this manner.
-For example, orbital spacecraft are subject to gravity gradient torques caused by the non-spherical distribution of mass of both the spacecraft and central gravitational body.
-This form of disturbance may be represented as a body fixed torque on the vehicle.
-In addition, for typical scenarios, where the spacecraft is significantly smaller than the orbital radius, the disturbance torque may be assumed constant over short time intervals.
-
-In~\refeqn{Rdot}, the \textit{hat} map $\wedge :\R^{3}\rightarrow\so$ represents the transformation of a vector in $\R^{3}$ to a $3\times 3$ skew-symmetric matrix such that $\hat x y = x\times y$ for any $x,y\in\R^{3}$~\cite{bullo2004}.
-More explicitly, 
-\begin{align*}
-\hat x = \begin{bmatrix} 0 & -x_3 & x_2 \\ x_3 & 0 & -x_1 \\ -x_2 & x_1 & 0\end{bmatrix},
-\end{align*}
-for $x=[x_1,x_2,x_3]^T\in\R^{3}$. 
-The inverse of the hat map is denoted by the \textit{vee} map $\vee:\so\rightarrow\R^{3}$. 
-Several properties of the hat map are summarized as
-\begin{gather}
-%    \hat x y = x\times y = - y\times x = - \hat y x,\\
-    x\cdot \hat y z = y\cdot \hat z x,\quad \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z\label{eqn:STP},\\
-%    \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z,\label{eqn:VTP}\\
-%    C^TC=-C^T\hat e_3^2 C = I_2
-%    \hat x^T \hat x = (x^T x) I - x x^T,\\
-%    \hat x \hat y \hat x=-(y^Tx)\hat x,\\
-%    -\frac{1}{2}\tr{\hat x \hat y} = x^T y,\\
-    \widehat{x\times y} = \hat x \hat y -\hat y \hat x = yx^T-xy^T,\label{eqn:hatxy}\\
-    %\tr{\hat x A}=
-    \tr{A\hat x }=\frac{1}{2}\tr{\hat x (A-A^T)}=-x^T (A-A^T)^\vee,\label{eqn:hat1}\\
-%    \widehat{Ax} = \hat x \parenth{\frac{1}{2}\tr{A}I-A} + \parenth{\frac{1}{2}\tr{A}I-A}^T \hat x,\\
-    \hat x  A+A^T\hat x=(\braces{\tr{A}I_{3\times 3}-A}x)^{\wedge},\label{eqn:xAAx}\\
-R\hat x R^T = (Rx)^\wedge,\quad 
-R(x\times y) = Rx\times Ry\label{eqn:RxR}
-%,\label{eqn:Rxy}
-\end{gather}
-for any $x,y,z\in\R^{3}$, $A\in\R^{3\times 3}$ and $R\in\SO$. 
-Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\R^n$ and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively.
-The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A} \leq \norm{A}_F = \sqrt{\tr{A^T A}} \leq \sqrt{\text{rank}(A)} \norm{A} \).
+This form of uncertainty enters the system dynamics through the input channel and is referred to as a matched uncertainty. 
+Many physically realizable disturbances may be modeled in this manner such as a gravity gradient torque.
 
 \subsection{State Inequality Constraint}
-
 The two-sphere is the manifold of unit-vectors in \( \R^3 \) such that \( \Sph^2 = \{ q \in \R^3 \,  \vert \, \norm{q} = 1 \}\).
@@
 \begin{proof}
-See~\Cref{proof:config_error}.
+For brevity, the proof is relegated to~\cite{kulumani2016b}.
 \end{proof}
@@
 In order to visualize the attitude error function on \( \SO \) we utilize a spherical coordinate representation.
-Recall that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth, and elevation.
-This coordinate system is commonly used to define locations on the Earth in terms of a latitude and longitude.
-Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
-We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
-Using the elementary Euler rotations the rotation matrix is now defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
-We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \).
-Applying this method,~\cref{fig:config_error} allows us to visualize the error function on \( \SO \).
-The attractive error function, given by~\cref{eqn:A}, has been previously used for attitude control on \(\SO\).
-The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum of \( A(R) \).
+We parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
+Using the elementary Euler rotations the rotation matrix is defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
+We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \) as shown in~\cref{fig:config_error}.
+\( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum \(\lambda=\beta=\SI{0}{\degree}\).
 
 To incorporate the state inequality constraints we apply a logarithmic barrier term.
-Barrier functions are typically used in optimal control and motion planning applications.
-A visualization of the configuration error function is presented in~\cref{fig:avoid_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
+A visualization of the barrier function is presented in~\cref{fig:avoid_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
 We use the scale factor~\(\frac{1}{1+\cos \theta} \) to ensure that \( \Psi \) remains positive definite.
@@
 The superposition of the attractive and repulsive functions is shown in~\cref{fig:combined_error}.
-The control system is defined such that the attitude trajectory follows the negative gradient of \( \Psi \) toward the minimum at \( R = R_d \), while avoiding the constrained region.
+The control system allows the attitude trajectory follows the negative gradient of \( \Psi \) towards the minimum at \( R = R_d \), while avoiding the constraints.
 \begin{figure} 
@@
 		\diff{}{t} \parenth{\Psi} = e_R \cdot e_\Omega , \label{eqn:psi_dot}\\
-		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B(R) + e_{R_A} \dot{B}(R) + \dot{A}(R)e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
+		%\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B + e_{R_A} \dot{B} + \dot{A}e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
 		\diff{}{t} \parenth{e_{R_A}} = E(R, R_d) e_\Omega , \label{eqn:eRA_dot} \\
@@
 \begin{proof}
-See~\Cref{proof:error_dyn}.
+For brevity, the proof is relegated to~\cite{kulumani2016b}.
 \end{proof}
@@
 \end{prop}
-
 \begin{proof}
-See~\Cref{proof:att_control}.
+For brevity, the proof is relegated to~\cite{kulumani2016b}.
 \end{proof}
@@
 This proposition only guarantees that the attitude error vector \( e_R \) asymptotically converges to zero.
-However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are at most three additional critical points of \( \Psi \) where \( e_R = 0 \) and \( R^T v = \pm r\).
+However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are at most three additional critical points of \( \Psi \) where \( e_R = 0 \) and \( R^T v = \pm r \).
 At an undesired equilibrium \( R = \exp{ \parenth{\pi \hat{e}_i}} R_d \) and \( e_\Omega =0 \).
@@
 
+%This results in \( A \) having a value of \( g_1 + g_2, g_2 + g_3 \) or \( g_3 + g_1 \).
+%At any of these undesired equilibria we have \( V = k \). 
+%We define an augmented Lyapunov function as
+%\begin{align*}
+%	W = k - V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \parenth{\frac{k}{k_R}+ \Psi(R,R_d)} .
+%\end{align*}
+%We can choose an attitude \( R \) arbitrarily close to the equilibrium point \( \exp{ \parenth{\pi \hat{e}_i}} R_d \) such that the \( k_R \parenth{\frac{k}{k_R}+\Psi }> 0 \).
+%This is due to the fact that \( \Psi \) is positive definite about \( R = R_d \) as shown in~\cref{item:prop_psi_psd}.
+%If \( e_\Omega \) is sufficiently small this results in \( W > 0 \) and \( \dot{W} = -\dot{V} > 0\) from~\cref{eqn:vdot_nodist}.
+%According to Chateav's theorem, the undesired equilibria are unstable~\cite{khalil1996}.
 \subsection{Adaptive Control}
@@
 \begin{proof}
-See~\Cref{proof:eR_dot_bound}.
+For brevity, the proof is relegated to~\cite{kulumani2016b}.
 \end{proof}
@@
 \begin{proof}
-See~\Cref{proof:adaptive_control}.
+For brevity, the proof is relegated to~\cite{kulumani2016b}.
 \end{proof}
@@
 		\caption{Configuration error \( \Psi \)} \label{fig:Psi_adapt} 
-	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+	\end{subfigure}~
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
@@
 The inequality constraints from~\Cref{tab:constraints} are depicted as red cones, where the cone half angle is \( \theta \).
-The control system is able to asymptotically converge to zero attitude error.
-\Cref{fig:con_angles} shows that the angle \( \arccos(r^T R^T v_i) \) between the body fixed sensor and each constraint is satisfied for the entire maneuver.
-In addition, the estimate of the disturbance converges to the the true value as shown in~\cref{fig:delta_adapt}.
+The control system is able to asymptotically converge to zero attitude error while avoiding the constrained regions.
+\Cref{fig:con_angle} shows that the angle \( \arccos(r^T R^T v_i) \) to each constraint in~\cref{tab:constraints} is satisfied for the entire maneuver.
+In addition, the estimate of the disturbance converges to the the true value.
 
@@
 When constrained to the spherical joint the hexrotor is capable of performing responsive attitude changes with high angular velocities.
-In addition, The on-board control and motion capture system operate at a discrete interval of approximately \SI{100}{\hertz}.
-It is possible for the system to violate the constraint between these discrete steps and cause numerical exceptions within the embedded software. 
-As a result, conservative control gains are chosen to ensure the hexrotor operates in a sedate manner and to allow sufficient time for the measurement and control software to operate.
+In addition, the on-board control and motion capture system operate at a discrete interval of approximately \SI{100}{\hertz}.
+It is possible for the system to violate the constraint between these discrete steps and cause numerical instability.
+We choose conservative control gains to  allow sufficient time for the measurement and control software to function correctly.
 
@@
 In addition, the spherical joint is not fixed at the center of mass but is instead offset due to the physical structure of the hexrotor.
-As a result a disturbance moment is induced on the resultant motion.
+As a result a disturbance moment is induced on the system.
 
@@
 This verifies that the proposed control system exhibits the desired performance in the experimental setting as well. 
-A video clip showing the attitude manuever is available \url{https://youtu.be/dsmAbwQram4}.
+A video clip showing the attitude maneuver is available \url{https://youtu.be/dsmAbwQram4}.
 \section{Conclusions}\label{sec:conclusions}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\subsection{Proof of~\Cref{prop:config_error}}\label{proof:config_error}
-To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a positive definite function about \( R = R_d \)~\cite{bullo2004}.
-The constraint angle is assumed \( \ang{0} \leq \theta \leq \ang{90} \) such that \( 0 \leq \cos \theta \).
-The term \( r^T R^T v \) represents the cosine of the angle between the body fixed vector \( r \) and the inertial vector \( v \). 
-It follows that
-\begin{align*}
-	0 \leq  \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta} \leq 1 ,
-\end{align*}
-for all \( R \in \SO \). 
-As a result, its negative logarithm is always positive and from~\cref{eqn:B}, \(1 < B\).
-The error function \( \Psi = A B \) is composed of two positive terms and is therefore also positive definite, and it is minimized at \( R = R_d \).
 
-Next, we consider~\cref{item:prop_era}.
-The variation of~\cref{eqn:A} is taken with respect to \( \delta R = R \hat \eta \) as
-\begin{align*}
-	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee ,
-%	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
-\end{align*}
-where we used~\cref{eqn:hat1}.
-
-A straightforward application of the chain and product rules of differentiation allows us to show~\cref{item:prop_erb} as
-\begin{align*}
-	\dirDiff{B}{R} &=  \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} ,
-%	-\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta} \right) \right]
-\end{align*}
-where the scalar triple product~\cref{eqn:STP} was used.
-
-%To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
-%The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
-%\begin{align*}
-%	Q = R_d^T R = 
-%	\begin{bmatrix}
-%		q_{11} & q_{12} & q_{13} \\
-%		q_{21} & q_{22} & q_{23} \\
-%		q_{31} & q_{32} & q_{33}
-%	\end{bmatrix} .
-%\end{align*}
-%Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
-%\begin{subequations}
-%\begin{align}
-%	g_3 q_{32} &= g_2 q_{23} , \\
-%	g_1 q_{13} &= g_3 q_{31} , \\
-%	g_2 q_{21} &= g_1 q_{12} .
-%\end{align}
-%\end{subequations}
-%These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
-%Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
-%\begin{subequations}
-%\begin{align}
-%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \\
-%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 , \\
-%	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 .
-%\end{align}
-%\end{subequations}
-%As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
-%Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
-The critical points of \( e_{R_A} \) are derived in~\cite{bullo2004}.
-There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180}.
-The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
-This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \).
-Since we assume the system will not operate in violation of the constraints, the addition of the barrier function does not add additional critical points to the control system.
-The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
-The proof of \( \norm{e_{R_A}} \) given by~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
-\subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
-From the kinematics~\cref{eqn:Rdot} and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
-\begin{gather*}
-	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega .
-\end{gather*}
-Applying this to the time derivative of~\cref{eqn:A} gives
-\begin{gather*}
-	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} .
-\end{gather*}
-Applying~\cref{eqn:hat1} into this shows~\cref{eqn:A_dot}.
-Next, the time derivative of the repulsive error function is given by
-\begin{gather*}
-	\diff{}{t} (B) = \frac{r^T \parenth{\hat{\Omega} R^T} v}{\alpha \parenth{r^T R^T v - \cos \theta}} .
-\end{gather*}
-Using the scalar triple product, given by~\cref{eqn:STP}, one can reduce this to~\cref{eqn:B_dot}.
-The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
-\begin{gather*}
-	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee .
-\end{gather*}
-Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eqn:eRA_dot,eqn:E}.
-
-We take the time derivative of the repulsive attitude error vector, \( e_{R_B} \), as
-\begin{gather*}
-	\diff{}{t}( e_{R_B} )= a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r ,
-\end{gather*}
-with \( a \in \R \) and \( b \in \R\) given by 
-\begin{gather*}
-	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} , \,
-	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} .
-\end{gather*}
-Using the scalar triple product from~\cref{eqn:STP} as \( r \cdot \Omega \times \parenth{R^T v} = \parenth{R^T v} \cdot r \times \Omega \) gives~\cref{eqn:eRB_dot,eqn:F}.
-
-We show the time derivative of the configuration error function as
-\begin{gather*}
-	\diff{}{t} (\Psi) = \dot{A} B + A \dot{B} .
-\end{gather*}
-A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and appplying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
-We show~\cref{eqn:eW_dot} by rearranging~\cref{eqn:Wdot} as 
-\begin{align*}
-	\diff{}{t} e_\Omega = \dot{\Omega} = J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } .
-\end{align*}
-
-\subsection{Proof of~\Cref{prop:att_control}}\label{proof:att_control}
-Consider the following Lyapunov function:
-\begin{gather}
-	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d) . \label{eqn:v_nodist}
-\end{gather}
-From~\cref{item:prop_psi_psd} of~\Cref{prop:config_error}, \(\mathcal{V} \geq 0 \).
-Using~\cref{eqn:eW_dot,eqn:psi_dot} with \( \Delta = 0 \), the time derivative of \( \mathcal{V} \) is given by
-\begin{align}
-	\dot{\mathcal{V}} &= -k_\Omega \norm{e_\Omega}^2 . \label{eqn:vdot_nodist}
-%	e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
-\end{align}
-Since \( \mathcal{V} \) is positive definite and \( \dot{\mathcal{V}} \) is negative semi-definite, the zero equilibrium point \( e_R, e_\Omega \) is stable in the sense of Lyapunov. 
-This also implies \( \lim_{t\to\infty} \norm{e_\Omega} = 0 \) and \( \norm{e_R} \) is uniformly bounded, as the Lyapunov function is non-increasing.
-From \refeqn{eRA_dot} and \refeqn{eRB_dot}, $\lim_{t\to\infty} \dot e_R =0$.
-One can show that \( \norm{\ddot{e}_R} \) is bounded.
-From Barbalat's Lemma, it follows \( \lim_{t\to\infty}\norm{\dot{e}_R} = 0 \)~\cite[Lemma 8.2]{khalil1996}. 
-Therefore, the equilibrium is asymptotically stable.
-
-Furthermore, since \( \dot{\mathcal{V}} \leq 0 \) the Lyapunov function is uniformly bounded which implies 
-\begin{align*}
-	\Psi(R(t)) \leq \mathcal{V}(t) \leq \mathcal{V}(0) .
-\end{align*}
-In addition, the logarithmic term in~\cref{eqn:B} ensures \( \Psi(R) \to \infty \) as \( r^T R^T v \to \cos \theta \).
-Therefore, the inequality constraint is always satisfied given that the desired equilibrium lies in the feasible set.
-
-\subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
-%	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
-%	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
-%	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
-%	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
-%	We know that \( B \to \infty \) as the constraint is neared. 
-%	We assume that \( B > \psi \) which implies that \( A < 1 \).
-%	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
-%	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
-	The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
-	This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
-	Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
-
-	Next, we show~~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
-	The Frobenius norm \( \norm{E}_F \) is given in~\cite{LeeITCST13} as
-	\begin{gather*}
-		\norm{E}_F = \sqrt{\tr{E^T E}} = \frac{1}{2} \sqrt{\tr{G^2} + \tr{R^T R_d G}^2} .
-	\end{gather*}
-	Applying Rodrigues' formula and the Matlab symbolic toolbox, this is simplified to
-	\begin{gather*}
-		\norm{E}^2_F \leq \frac{1}{4} \parenth{\tr{G^2} + \tr{G}^2} \leq \frac{1}{2} \tr{G}^2 ,
-	\end{gather*}
-	which shows~\cref{eqn:E_bound}, since \( \norm{E} \leq \norm{E}_F \).
-
-	To show~\cref{eqn:F_bound}, we apply the Frobenius norm \( \norm{F}_F \):
-	\begin{gather*}
-		\norm{F}_F = \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} - 2 \tr{a^T b} \right. \\
-		\left.+ 2 \tr{a^T c } + \tr{b^T b}  - 2 \tr{b^T c} + \tr{c^T c}\right] .
-	\end{gather*}
-	where the terms \( a, b, \text{ and } c \) are given by
-	\begin{gather*}
-		a = r^T R r I , \quad	b = R^T v r^T , \quad c = \frac{R^T \hat{v} R r v^T R \hat{r}}{r^T R^T v - \cos \theta}.
-	\end{gather*}
-	A straightforward computation of \( a^T a \) shows that
-	\begin{gather*}
-		\tr{a^T a} = \parenth{v^T R r}^2 \tr{I} \leq 3 \beta^2 ,
-	\end{gather*}
-	where we used the fact that \( v^T R r = r^T R^T v < \beta \) from our given domain.
-	Similarly, one can show that \( \tr{a^T b} \) is equivalent to
-	\begin{gather*}
-		\tr{a^T b} = v^T R r \tr{R^T v r^T} = \parenth{v^T R r}^2 \leq \beta^2 ,
-	\end{gather*} 
-	where we used the fact that \( \tr{x y^T} = x^T y \).
-	The product \( \tr{a^T c} \) is given by
-	\begin{gather*}
-		\tr{a^T c} = \frac{v^T R r}{r^T R^T v - \cos \theta} \tr{\parenth{R^T v}^\vee \parenth{r v^T R} \hat{r} } ,
-	\end{gather*}
-	where we used the hat map property~\cref{eqn:RxR}.
-	One can show that \(\mathrm{tr}[a^T c] \leq 0 \) over the range \( -1 \leq v^T R r \leq \cos \theta \). 
-	Next, \( \tr{b^T b}\) is equivalent to
-	\begin{gather*}
-		\tr{b^T b} = \tr{r v^T R R^T v r^T} = 1 ,
-	\end{gather*}
-	since \( r,v \in \Sph^2\).
-	Finally, \( \tr{c^T c} \) is reduced to
-	\begin{gather*}
-		\tr{c^T c} = \tr{\hat{r} R^T v r^T \bracket{-I + R^T v v^T R} r v^T R \hat{r}} ,
-	\end{gather*}
-	where we used the fact that \( \hat{x}^2 = - \norm{x}^2 I + x x^T\).
-	Expanding and collecting like terms gives
-	\begin{gather*}
-		\tr{c^T c } = \frac{1 - 2\parenth{v^T R r}^2 + \parenth{v^T R r}^4}{\parenth{r^T R^T v - \cos \theta}^2} . 
-	\end{gather*}
-	Using the the given domain \( r^T R^T v \leq \beta \) gives the upper bound~\cref{eqn:F_bound}.
-	The bound on \( e_{R_A} \) is given in~\cref{eqn:psi_lower_bound} while \( e_{R_B} \) arises from the definition of the cross product \( \norm{a \times b} = \norm{a} \norm{b} \sin \theta \).
-	Finally, we can find the upper bound~\cref{eqn:eR_dot} as
-	\begin{gather*}
-		\norm{\dot{e}_R} \leq \parenth{\norm{B} \norm{E} + 2 \norm{e_{R_A}} \norm{e_{R_B}} + \norm{A}\norm{F}} \norm{e_\Omega} \, .
-	\end{gather*}
-	Using~\crefrange{eqn:AB_bound}{eqn:eRB_bound} one can define \( H \) in terms of known values.
-\subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}
-	Consider the Lyapunov function \( \mathcal{V} \) given by
-	\begin{gather}
-		\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , \label{eqn:v_adapt}
-	\end{gather}
-	over the domain \( D \) in~\cref{eqn:domain}.
-	From~\Cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
-	\begin{gather}
-		\mathcal{V} \leq z^T W z , \label{eqn:v_upper_bound}
-	\end{gather}
-	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrix \(W \in \R^{3 \times 3}\) is given by
-	\begin{gather*}
-		W = \begin{bmatrix}
-			k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
-			\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
-			0 & 0 & \frac{1}{2 k_\Delta}
-		\end{bmatrix} .
-	\end{gather*}
-	The time derivative of \( \mathcal{V}\) with the control inputs~\cref{eqn:adaptive_control} is given by
-	\begin{align}
-		\dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
-		&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
-	\end{align}
-	where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
-	The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
-	\begin{align*}
-		 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
-	\end{align*}
-	Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
-	\begin{gather*}
-		\dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
-	\end{gather*}
-	where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
-	\begin{gather}
-		M = \begin{bmatrix}
-			k_R c & \frac{k_\Omega c}{2} \\
-			\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
-		\end{bmatrix} .
-	\end{gather}
-	If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
-	This implies that $\dot{\mathcal{V}}$ is negative semidefinite and $\lim_{t\to\infty} \zeta=0$. 
-	As the Lyapunov function is non-increasing $z$ is uniformly bounded. 
-%	
-%	
-%	This implies that the Lyapunov function \( V \) is non-increasing and bounded from below.
-%	Furthermore, since \( V \) is nonincreasing the disturbance error \( e_\Delta\) is bounded.
-%	Since \( \dot{V} \) is uniformly continuous in time this implies that the zero equilibrium \( e_R, e_\Omega\) is stable in the sense of Lyapunov
-%	The domain \( D \) does that include the undesired equilibria and ensures that as \( e_R \to 0 \) the attitude also converges \( R \to R_d \).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
+\addtolength{\textheight}{-12cm}
 

### 2016-02-15 ACC16.2.tex
Remove duplicate package call
Correct some typos

@@
 The superposition of the attractive and repulsive functions is shown in~\cref{fig:combined_error}.
-The control system allows the attitude trajectory follows the negative gradient of \( \Psi \) towards the minimum at \( R = R_d \), while avoiding the constraints.
+The control system allows the attitude trajectory follows the negative gradient of \( \Psi \) toward the minimum at \( R = R_d \), while avoiding the constraints.
 \begin{figure} 
@@
 The control system is able to asymptotically converge to zero attitude error while avoiding the constrained regions.
-\Cref{fig:con_angle} shows that the angle \( \arccos(r^T R^T v_i) \) to each constraint in~\cref{tab:constraints} is satisfied for the entire maneuver.
+\Cref{fig:con_angles} shows that the angle \( \arccos(r^T R^T v_i) \) to each constraint in~\Cref{tab:constraints} is satisfied for the entire maneuver.
 In addition, the estimate of the disturbance converges to the the true value.

### 2016-02-16 ACC16.2.tex
Add corrections from Christine and remove useless packages

@@
 \subsection{Attitude Dynamics}\label{sec:att_dyn}
-Consider the attitude dynamics of a rigid body. 
-We define an inertial reference frame and a body frame whose origin is at the center of mass and aligned with the principle directions of the body. 
+Consider the attitude dynamics of a rigid body--we define an inertial reference frame and a body frame whose origin is at the center of mass and aligned with the principle directions of the body. 
 The configuration manifold of the attitude dynamics is the special orthogonal group: \(\SO = \{R\in\R^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\} \).
@@
 
-\begin{prop}[Bound on \( \dot{e}_R \)]\label{prop:eR_dot_bound}
+\begin{prop}[Bound on \( \bm{\dot{e}_R} \)]\label{prop:eR_dot_bound}
 Consider a domain \( D \) about the desired attitude defined as
@@
 In addition, these results show that it is straightforward to incorporate an arbitrary amount of large constraints.
-In spite of this challenging configuration space the proposed control system offers a simple method of avoiding constrained regions.
+In spite of this challenging configuration space, the proposed control system offers a simple method of avoiding constrained regions.
 These closed-loop feedback results are computed in real time and offer a significant advantage over typical open-loop planning methods.
@@
 
-The brushless motors of the hexrotor allow for large control inputs which are critical to enable aggressive maneuvers. 
-When constrained to the spherical joint the hexrotor is capable of performing responsive attitude changes with high angular velocities.
+The brushless motors of the hexrotor allow for large control inputs, which are critical to enable aggressive maneuvers. 
+When constrained to the spherical joint, the hexrotor is capable of performing responsive attitude changes with high angular velocities.
 In addition, the on-board control and motion capture system operate at a discrete interval of approximately \SI{100}{\hertz}.

### 2016-02-16 ACC16.2.tex
Add comments from Christine and remove uneeded packages

@@
 
-\usepackage{ieee_packages,graphicx}
+\usepackage{ieee_packages}
 \newcommand{\squeezeup}{\vspace{-2.5mm}}
@@
 
-Rigid body attitude control is an important problem for aerospace vehicles, ground and underwater vehicles, as well as robotic systems~\cite{hughes2004}.
+Rigid body attitude control is an important problem for aerospace vehicles, ground and underwater vehicles, as well as robotic systems~\cite{hughes2004,wertz1978}.
 One distinctive feature of the attitude dynamics of rigid bodies is that it evolves on a nonlinear manifold.
@@
 For example, it is impossible to achieve global attitude stabilization using continuous time-invariant feedback~\cite{bhat2000}.
+
+% topological obstruction - smooth control system can only achieve almost global asymptotic stability
+
+% discuss issues with parameterizations
+
+Attitude control is typically studied using a variety of attitude parameterizations, such as Euler angles or quaternions~\cite{shuster1993}.
+All attitude parameterizations fail to represent the nonlinear configuration space both globally and uniquely~\cite{chaturvedi2011a}.
+For example, minimal attitude representations, such as Euler angle sequences or modified Rodriguez parameters, suffer from singularities.
+These attitude representations are not suitable for large angular slews.
+%In order to avoid singularities, the designer must carefully switch the chosen Euler angle sequence based on the operating region.
+%Another option is to artificially limit the operating region of the rigid body.
+%This ensures the system operates in a region free from singularities but limits the performance capabilities and ability to perform arbitrarily large angular maneuvers.
+Quaternions do not have singularities but they double cover the special orthogonal group.
+As a result, any physical attitude is represented by a pair of antipodal quaternions on the three-sphere.
+%An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
+During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}.
+%, where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.
 
@@
 A conceptually straightforward approach is used in~\cite{hablani1999} to determine feasible attitude trajectories prior to implementation.
-The algorithm determines an intermediate point such that an unconstrained maneuver can be calculated for each sub-interval.
+The algorithm determines an intermediate point such that an unconstrained maneuver can be calculated for each subsegment.
+Typically, an optimal or easily implementable on-board control scheme for attitude maneuvers is applied to maneuver the vehicle along these segments.
 In this manner it is possible to accomplish constraint avoidance by linking several intermediary unconstrained maneuvers.
 While this method is conceptually simple, it is difficult to generalize for an arbitrary number of constraints.
+In addition, this approach is only applicable to problems where the selection of intermediate points are computationally feasible.
 
 The approach in~\cite{frazzoli2001} involves the use of randomized motion planning algorithms to solve the constrained attitude control problem.
+A graph is generated consisting of vertices from an initial attitude to a desired attitude. 
 A random iterative search is conducted to determine a path through a directed graph such that a given cost functional is minimized.
-However, the random search approach can only stochastically guarantee attitude convergence.
-Typically, very large graphs are required which are ill-suited to on-board implementation or in scenarios that require agile maneuvers.
+The random search approach can only stochastically guarantee attitude convergence as it can be shown that as the number of vertices in the graph grow, the probability of nonconvergence goes to zero.
+However, the computational demand grows as the size of the graph is increased. 
+As a result, random search approaches are ill-suited to on-board implementation or in scenarios that require agile maneuvers.
 
 Model predictive control for spacecraft attitude dynamics is studied in~\cite{guiggiani2014,kalabic2014,gupta2015}.
-This approach relies on linear or non-linear state prediction to repeatedly solve a finite time constrained optimal control problem.
-The necessary conditions for optimality are continually computed over a receding finite horizon using a direct method. 
-As a result, these methods are also computationally expensive.
-
-% MORE DETAIL ON CONTRIBUTIONS 
-% EXPLICITLY STATE - first time for constraints to be incorportated on SO(3) with barrier function
-% Consider adaptive control which allows for stabilization in the presence of uncertain terms
-% Benefits over previous approach -
-% Developed on SO(3) - avoids issues of singularities and ambiguities of quaternion approach
-% Geometric approach - requires a priori calculation of trajectory. not robust to uncertainties or changes in configuraiton
-% Random/Graph approach -computationally expensive. requires a priori calculation of trajectory
+These methods rely on linear or non-linear state dynamics to repeatedly solve a finite-time optimal control problem.
+As a result, model predictive control methods are also computational expensive and apply direct optimization methods to solve the necessary conditions for optimality.
+Therefore these methods are complicated to implement and not applicable for real-time control applications.
 
@@
 The goal is the design of attractive and repulsive terms which drive the system toward or away from a certain state, respectively.
+%The goal is the design of an attractive function which drives the system towards the desired state.
+%Similarly, a repulsive function is constructed such that the system is directed away from the constraints. 
+The superposition of the these functions allows one to apply standard feedback control schemes for stabilization and tracking.
 More specifically, artificial potential functions have previously been applied to the spacecraft attitude control problem in~\cite{lee2011b,mcinnes1994}.
-However, both of these approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by singularities or ambiguities.
+However, both of these approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by the singularities of minimal representations or the ambiguity of quaternions.
 
 This paper is focused on developing an adaptive attitude control scheme in the presence of attitude inequality constraints on \(\SO\).
-We apply a potential function based approach directly on the nonlinear manifold \(\SO\). 
-We also formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances.
+We apply a potential function based approach developed directly on the nonlinear manifold \(\SO\). 
+By characterizing the attitude both globally and uniquely on \(\SO\), our approach avoids the issues of attitude parameterizations, such as kinematic singularities and ambiguities, and is geometrically exact.
+A configuration error function on \(\SO\) with a logarithmic barrier function is proposed to avoid constrained regions. 
+Instead of calculating a priori trajectories, as in the geometric and randomized approaches, our approach results in a closed-loop attitude control system. 
+This makes it ideal for on-board implementation on UAV or spacecraft systems. 
+In addition, unlike previous approaches our control system can handle an arbitrary number of constrained regions without modification.
+
+Furthermore, we formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances. 
 The stability of the proposed control systems is verified via mathematically rigorous Lyapunov analysis on $\SO$.  
@@
 Consider the attitude dynamics of a rigid body--we define an inertial reference frame and a body frame whose origin is at the center of mass and aligned with the principle directions of the body. 
-The configuration manifold of the attitude dynamics is the special orthogonal group: \(\SO = \{R\in\R^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\} \).
-The rotation matrix $R\in\SO$ represents the transformation of the representation of a vector from the body-fixed frame to the inertial reference frame. 
+The configuration manifold of the attitude dynamics is the special orthogonal group:
+\begin{align*}
+	\SO = \{R\in\R^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\} ,
+\end{align*}
+where a rotation matrix $R\in\SO$ represents the transformation of the representation of a vector from the body-fixed frame to the inertial reference frame. 
 The equations of motion are given by
@@
 \end{equation}
-This form of uncertainty enters the system dynamics through the input channel and is referred to as a matched uncertainty. 
-Many physically realizable disturbances may be modeled in this manner such as a gravity gradient torque.
+This form of uncertainty enters the system dynamics through the input channel and as a result is referred to as a matched uncertainty. 
+While this form of uncertainty is easier than the unmatched variety many physically realizable disturbances may be modeled in this manner.
+For example, orbital spacecraft are subject to gravity gradient torques caused by the non-spherical distribution of mass of both the spacecraft and central gravitational body.
+This form of disturbance may be represented as a body fixed torque on the vehicle.
+In addition, for typical scenarios, where the spacecraft is significantly smaller than the orbital radius, the disturbance torque may be assumed constant over short time intervals.
+
+In~\refeqn{Rdot}, the \textit{hat} map $\wedge :\R^{3}\rightarrow\so$ represents the transformation of a vector in $\R^{3}$ to a $3\times 3$ skew-symmetric matrix such that $\hat x y = x\times y$ for any $x,y\in\R^{3}$~\cite{bullo2004}.
+More explicitly, 
+\begin{align*}
+\hat x = \begin{bmatrix} 0 & -x_3 & x_2 \\ x_3 & 0 & -x_1 \\ -x_2 & x_1 & 0\end{bmatrix},
+\end{align*}
+for $x=[x_1,x_2,x_3]^T\in\R^{3}$. 
+The inverse of the hat map is denoted by the \textit{vee} map $\vee:\so\rightarrow\R^{3}$. 
+Several properties of the hat map are summarized as
+\begin{gather}
+%    \hat x y = x\times y = - y\times x = - \hat y x,\\
+    x\cdot \hat y z = y\cdot \hat z x,\quad \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z\label{eqn:STP},\\
+%    \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z,\label{eqn:VTP}\\
+%    C^TC=-C^T\hat e_3^2 C = I_2
+%    \hat x^T \hat x = (x^T x) I - x x^T,\\
+%    \hat x \hat y \hat x=-(y^Tx)\hat x,\\
+%    -\frac{1}{2}\tr{\hat x \hat y} = x^T y,\\
+    \widehat{x\times y} = \hat x \hat y -\hat y \hat x = yx^T-xy^T,\label{eqn:hatxy}\\
+    %\tr{\hat x A}=
+    \tr{A\hat x }=\frac{1}{2}\tr{\hat x (A-A^T)}=-x^T (A-A^T)^\vee,\label{eqn:hat1}\\
+%    \widehat{Ax} = \hat x \parenth{\frac{1}{2}\tr{A}I-A} + \parenth{\frac{1}{2}\tr{A}I-A}^T \hat x,\\
+    \hat x  A+A^T\hat x=(\braces{\tr{A}I_{3\times 3}-A}x)^{\wedge},\label{eqn:xAAx}\\
+R\hat x R^T = (Rx)^\wedge,\quad 
+R(x\times y) = Rx\times Ry\label{eqn:RxR}
+%,\label{eqn:Rxy}
+\end{gather}
+for any $x,y,z\in\R^{3}$, $A\in\R^{3\times 3}$ and $R\in\SO$. 
+Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\R^n$ and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively.
+The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A} \leq \norm{A}_F = \sqrt{\tr{A^T A}} \leq \sqrt{\text{rank}(A)} \norm{A} \).
 
 \subsection{State Inequality Constraint}
+
 The two-sphere is the manifold of unit-vectors in \( \R^3 \) such that \( \Sph^2 = \{ q \in \R^3 \,  \vert \, \norm{q} = 1 \}\).
@@
 A smooth control system is first developed assuming that there is  no disturbance, and then it is extended to include an adaptive update law for stabilization in the presence of unknown disturbances. 
+The proposed attitude configuration error function and several properties are summarized as follows.
 
@@
 \begin{proof}
-For brevity, the proof is relegated to~\cite{kulumani2016b}.
+See~\Cref{proof:config_error}.
 \end{proof}
@@
 In order to visualize the attitude error function on \( \SO \) we utilize a spherical coordinate representation.
-We parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
-Using the elementary Euler rotations the rotation matrix is defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
-We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \) as shown in~\cref{fig:config_error}.
-\( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum \(\lambda=\beta=\SI{0}{\degree}\).
+Recall that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth, and elevation.
+This coordinate system is commonly used to define locations on the Earth in terms of a latitude and longitude.
+Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
+We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
+Using the elementary Euler rotations the rotation matrix is now defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
+We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \).
+Applying this method,~\cref{fig:config_error} allows us to visualize the error function on \( \SO \).
+The attractive error function, given by~\cref{eqn:A}, has been previously used for attitude control on \(\SO\).
+The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum of \( A(R) \).
 
 To incorporate the state inequality constraints we apply a logarithmic barrier term.
-A visualization of the barrier function is presented in~\cref{fig:avoid_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
+Barrier functions are typically used in optimal control and motion planning applications.
+A visualization of the configuration error function is presented in~\cref{fig:avoid_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
 We use the scale factor~\(\frac{1}{1+\cos \theta} \) to ensure that \( \Psi \) remains positive definite.
@@
 The superposition of the attractive and repulsive functions is shown in~\cref{fig:combined_error}.
-The control system allows the attitude trajectory follows the negative gradient of \( \Psi \) toward the minimum at \( R = R_d \), while avoiding the constraints.
+The control system is defined such that the attitude trajectory follows the negative gradient of \( \Psi \) toward the minimum at \( R = R_d \), while avoiding the constrained region.
 \begin{figure} 
@@
 		\diff{}{t} \parenth{\Psi} = e_R \cdot e_\Omega , \label{eqn:psi_dot}\\
-		%\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B + e_{R_A} \dot{B} + \dot{A}e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
+		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B(R) + e_{R_A} \dot{B}(R) + \dot{A}(R)e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
 		\diff{}{t} \parenth{e_{R_A}} = E(R, R_d) e_\Omega , \label{eqn:eRA_dot} \\
@@
 \begin{proof}
-For brevity, the proof is relegated to~\cite{kulumani2016b}.
+See~\Cref{proof:error_dyn}.
 \end{proof}
@@
 \end{prop}
+
 \begin{proof}
-For brevity, the proof is relegated to~\cite{kulumani2016b}.
+See~\Cref{proof:att_control}.
 \end{proof}
@@
 This proposition only guarantees that the attitude error vector \( e_R \) asymptotically converges to zero.
-However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are at most three additional critical points of \( \Psi \) where \( e_R = 0 \) and \( R^T v = \pm r \).
+However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are at most three additional critical points of \( \Psi \) where \( e_R = 0 \) and \( R^T v = \pm r\).
 At an undesired equilibrium \( R = \exp{ \parenth{\pi \hat{e}_i}} R_d \) and \( e_\Omega =0 \).
@@
 
-%This results in \( A \) having a value of \( g_1 + g_2, g_2 + g_3 \) or \( g_3 + g_1 \).
-%At any of these undesired equilibria we have \( V = k \). 
-%We define an augmented Lyapunov function as
-%\begin{align*}
-%	W = k - V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \parenth{\frac{k}{k_R}+ \Psi(R,R_d)} .
-%\end{align*}
-%We can choose an attitude \( R \) arbitrarily close to the equilibrium point \( \exp{ \parenth{\pi \hat{e}_i}} R_d \) such that the \( k_R \parenth{\frac{k}{k_R}+\Psi }> 0 \).
-%This is due to the fact that \( \Psi \) is positive definite about \( R = R_d \) as shown in~\cref{item:prop_psi_psd}.
-%If \( e_\Omega \) is sufficiently small this results in \( W > 0 \) and \( \dot{W} = -\dot{V} > 0\) from~\cref{eqn:vdot_nodist}.
-%According to Chateav's theorem, the undesired equilibria are unstable~\cite{khalil1996}.
 \subsection{Adaptive Control}
@@
 		\norm{E} \leq \frac{1}{\sqrt{2}} \tr{G}  , \label{eqn:E_bound} \\
-		\norm{F} \leq \frac{\parenth{\beta^2 + 1}\parenth{\beta - \cos \theta}^2 + 1 + \beta^4-2 \beta^2}{\alpha^2 \parenth{\beta-\cos \theta}^4} . \label{eqn:F_bound}
+		\norm{F} \leq \frac{\parenth{\beta^2 + 1}\parenth{\beta - \cos \theta}^2 + 1 + \beta^2 \parenth{\beta^2-2}}{\alpha^2 \parenth{\beta-\cos \theta}^4} . \label{eqn:F_bound}
 	\end{gather}
@@
 \begin{proof}
-For brevity, the proof is relegated to~\cite{kulumani2016b}.
+See~\Cref{proof:eR_dot_bound}.
 \end{proof}
@@
 \begin{proof}
-For brevity, the proof is relegated to~\cite{kulumani2016b}.
+See~\Cref{proof:adaptive_control}.
 \end{proof}
@@
 Nonlinear adaptive controllers have been developed for attitude stabilization in terms of modified Rodriguez parameters and quaternions, as well as attitude tracking in terms of Euler angles. 
-The proposed control system is developed on \(\SO\) and avoids the issues inherent in attitude representations, while incorporating state inequality constraints. 
-In addition, the control system handles uncertain disturbances.
+The proposed control system is developed on \(\SO\) and avoids the singularities of Euler angles and Rodriguez parameters while incorporating state inequality constraints. 
+In addition, the unwinding and double coverage ambiguity of quaternions are also completely avoided. 
+The control system handles uncertain disturbances while avoiding constrained regions.
 
 Compared to the previous work on constrained attitude control, we present a geometrically exact control system without parameterizations.
-In addition, we incorporate state inequality constraints on \( \SO \).
+In addition, we incorporate state inequality constraints for the first time on \( \SO \).
 The presented control system is computed in real-time and offers significant computational advantages over previous iterative methods. 
@@
 The desired state is \( R_d = I,\Omega_d = 0\).
-\begin{table}[htbp]
+\begin{table}%[htbp]
 \caption{Constraint Parameters~\label{tab:constraints}}
@@
 		\caption{Configuration error \( \Psi \)} \label{fig:Psi_adapt} 
-	\end{subfigure}~
+	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
 	\begin{subfigure}[htbp]{0.5\columnwidth} 
@@
 Simulation results without the adaptive update law are shown in~\cref{fig:con}.
-Without the update law,~\cref{fig:Psi_con} shows that the configuration error function does not converge to zero and there exist steady state errors.
-\Cref{fig:adapt} shows that the addition of the adaptive update law the system converges to the desired attitude.
+Without the update law, the system does not achieve zero steady state error. 
+\Cref{fig:Psi_con} shows that the configuration error function does not converge to zero and there exist steady state errors.
+\Cref{fig:adapt} shows the results with the addition of the adaptive update law.
+The addition of the adaptive update law allows the system to converge to the desired attitude in the presence of constraints.
 The path of the body fixed sensor in the inertial frame, namely \( R r \), is illustrated in~\cref{fig:cad_adapt}.
@@
 The inequality constraints from~\Cref{tab:constraints} are depicted as red cones, where the cone half angle is \( \theta \).
-The control system is able to asymptotically converge to zero attitude error while avoiding the constrained regions.
-\Cref{fig:con_angles} shows that the angle \( \arccos(r^T R^T v_i) \) to each constraint in~\Cref{tab:constraints} is satisfied for the entire maneuver.
-In addition, the estimate of the disturbance converges to the the true value.
+The control system is able to asymptotically converge to zero attitude error.
+\Cref{fig:con_angles} shows that the angle \( \arccos(r^T R^T v_i) \) between the body fixed sensor and each constraint is satisfied for the entire maneuver.
+In addition, the estimate of the disturbance converges to the the true value as shown in~\cref{fig:delta_adapt}.
 
@@
 	\item BLDC motors with BL-Ctrl-2.0 ESC via I2C.
-	\item Vicon motion capture system.
+	\item Position and attitude over WiFi (TCP) communication from Vicon motion capture system.
+	\item Commands sent over WiFi to  onboard controller. 
 \end{itemize}
@@
 \end{figure}
-
 A sensor pointing direction is defined in the body frame of the hexrotor as \( r = [1,0,0]^T \).
@@
 When constrained to the spherical joint, the hexrotor is capable of performing responsive attitude changes with high angular velocities.
-In addition, the on-board control and motion capture system operate at a discrete interval of approximately \SI{100}{\hertz}.
-It is possible for the system to violate the constraint between these discrete steps and cause numerical instability.
-We choose conservative control gains to  allow sufficient time for the measurement and control software to function correctly.
+In addition, The on-board control and motion capture system operate at a discrete interval of approximately \SI{100}{\hertz}.
+It is possible for the system to violate the constraint between these discrete steps and cause numerical exceptions within the embedded software. 
+As a result, conservative control gains are chosen to ensure the hexrotor operates in a sedate manner and to allow sufficient time for the measurement and control software to operate.
 
@@
 In addition, the spherical joint is not fixed at the center of mass but is instead offset due to the physical structure of the hexrotor.
-As a result a disturbance moment is induced on the system.
+As a result a disturbance moment is induced on the resultant motion.
 
@@
 This will cause an increase in control input until the steady-state error is reduced. 
-Further tuning of the control gains would enable a reduced settling time.
+Further tuning of the control gains would enable a faster response and a reduced settling time.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+\subsection{Proof of~\Cref{prop:config_error}}\label{proof:config_error}
+To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a positive definite function about \( R = R_d \)~\cite{bullo2004}.
+The constraint angle is assumed \( \ang{0} \leq \theta \leq \ang{90} \) such that \( 0 \leq \cos \theta \).
+The term \( r^T R^T v \) represents the cosine of the angle between the body fixed vector \( r \) and the inertial vector \( v \). 
+It follows that
+\begin{align*}
+	0 \leq  \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta} \leq 1 ,
+\end{align*}
+for all \( R \in \SO \). 
+As a result, its negative logarithm is always positive and from~\cref{eqn:B}, \(1 < B\).
+The error function \( \Psi = A B \) is composed of two positive terms and is therefore also positive definite, and it is minimized at \( R = R_d \).
 
-\addtolength{\textheight}{-12cm}
+Next, we consider~\cref{item:prop_era}.
+The variation of~\cref{eqn:A} is taken with respect to \( \delta R = R \hat \eta \) as
+\begin{align*}
+	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee ,
+%	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
+\end{align*}
+where we used~\cref{eqn:hat1}.
+
+A straightforward application of the chain and product rules of differentiation allows us to show~\cref{item:prop_erb} as
+\begin{align*}
+	\dirDiff{B}{R} &=  \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} ,
+%	-\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta} \right) \right]
+\end{align*}
+where the scalar triple product~\cref{eqn:STP} was used.
+
+%To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
+%The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
+%\begin{align*}
+%	Q = R_d^T R = 
+%	\begin{bmatrix}
+%		q_{11} & q_{12} & q_{13} \\
+%		q_{21} & q_{22} & q_{23} \\
+%		q_{31} & q_{32} & q_{33}
+%	\end{bmatrix} .
+%\end{align*}
+%Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
+%\begin{subequations}
+%\begin{align}
+%	g_3 q_{32} &= g_2 q_{23} , \\
+%	g_1 q_{13} &= g_3 q_{31} , \\
+%	g_2 q_{21} &= g_1 q_{12} .
+%\end{align}
+%\end{subequations}
+%These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
+%Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
+%\begin{subequations}
+%\begin{align}
+%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \\
+%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 , \\
+%	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 .
+%\end{align}
+%\end{subequations}
+%As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
+%Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
+The critical points of \( e_{R_A} \) are derived in~\cite{bullo2004}.
+There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180}.
+The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
+This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \).
+Since we assume the system will not operate in violation of the constraints, the addition of the barrier function does not add additional critical points to the control system.
+The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
+The proof of \( \norm{e_{R_A}} \) given by~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
+\subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
+From the kinematics~\cref{eqn:Rdot} and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
+\begin{gather*}
+	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega .
+\end{gather*}
+Applying this to the time derivative of~\cref{eqn:A} gives
+\begin{gather*}
+	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} .
+\end{gather*}
+Applying~\cref{eqn:hat1} into this shows~\cref{eqn:A_dot}.
+Next, the time derivative of the repulsive error function is given by
+\begin{gather*}
+	\diff{}{t} (B) = \frac{r^T \parenth{\hat{\Omega} R^T} v}{\alpha \parenth{r^T R^T v - \cos \theta}} .
+\end{gather*}
+Using the scalar triple product, given by~\cref{eqn:STP}, one can reduce this to~\cref{eqn:B_dot}.
+The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
+\begin{gather*}
+	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee .
+\end{gather*}
+Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eqn:eRA_dot,eqn:E}.
+
+We take the time derivative of the repulsive attitude error vector, \( e_{R_B} \), as
+\begin{gather*}
+	\diff{}{t}( e_{R_B} )= a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r ,
+\end{gather*}
+with \( a \in \R \) and \( b \in \R\) given by 
+\begin{gather*}
+	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} , \,
+	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} .
+\end{gather*}
+Using the scalar triple product from~\cref{eqn:STP} as \( r \cdot \Omega \times \parenth{R^T v} = \parenth{R^T v} \cdot r \times \Omega \) gives~\cref{eqn:eRB_dot,eqn:F}.
+
+We show the time derivative of the configuration error function as
+\begin{gather*}
+	\diff{}{t} (\Psi) = \dot{A} B + A \dot{B} .
+\end{gather*}
+A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and appplying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
+We show~\cref{eqn:eW_dot} by rearranging~\cref{eqn:Wdot} as 
+\begin{align*}
+	\diff{}{t} e_\Omega = \dot{\Omega} = J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } .
+\end{align*}
+
+\subsection{Proof of~\Cref{prop:att_control}}\label{proof:att_control}
+Consider the following Lyapunov function:
+\begin{gather}
+	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d) . \label{eqn:v_nodist}
+\end{gather}
+From~\cref{item:prop_psi_psd} of~\Cref{prop:config_error}, \(\mathcal{V} \geq 0 \).
+Using~\cref{eqn:eW_dot,eqn:psi_dot} with \( \Delta = 0 \), the time derivative of \( \mathcal{V} \) is given by
+\begin{align}
+	\dot{\mathcal{V}} &= -k_\Omega \norm{e_\Omega}^2 . \label{eqn:vdot_nodist}
+%	e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
+\end{align}
+Since \( \mathcal{V} \) is positive definite and \( \dot{\mathcal{V}} \) is negative semi-definite, the zero equilibrium point \( e_R, e_\Omega \) is stable in the sense of Lyapunov. 
+This also implies \( \lim_{t\to\infty} \norm{e_\Omega} = 0 \) and \( \norm{e_R} \) is uniformly bounded, as the Lyapunov function is non-increasing.
+From \refeqn{eRA_dot} and \refeqn{eRB_dot}, $\lim_{t\to\infty} \dot e_R =0$.
+One can show that \( \norm{\ddot{e}_R} \) is bounded.
+From Barbalat's Lemma, it follows \( \lim_{t\to\infty}\norm{\dot{e}_R} = 0 \)~\cite[Lemma 8.2]{khalil1996}. 
+Therefore, the equilibrium is asymptotically stable.
+
+Furthermore, since \( \dot{\mathcal{V}} \leq 0 \) the Lyapunov function is uniformly bounded which implies 
+\begin{align*}
+	\Psi(R(t)) \leq \mathcal{V}(t) \leq \mathcal{V}(0) .
+\end{align*}
+In addition, the logarithmic term in~\cref{eqn:B} ensures \( \Psi(R) \to \infty \) as \( r^T R^T v \to \cos \theta \).
+Therefore, the inequality constraint is always satisfied given that the desired equilibrium lies in the feasible set.
+
+\subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
+%	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
+%	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
+%	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
+%	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
+%	We know that \( B \to \infty \) as the constraint is neared. 
+%	We assume that \( B > \psi \) which implies that \( A < 1 \).
+%	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
+%	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
+	The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
+	This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
+	Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
+
+	Next, we show~~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
+	The Frobenius norm \( \norm{E}_F \) is given in~\cite{LeeITCST13} as
+	\begin{gather*}
+		\norm{E}_F = \sqrt{\tr{E^T E}} = \frac{1}{2} \sqrt{\tr{G^2} + \tr{R^T R_d G}^2} .
+	\end{gather*}
+	Applying Rodrigues' formula and the Matlab symbolic toolbox, this is simplified to
+	\begin{gather*}
+		\norm{E}^2_F \leq \frac{1}{4} \parenth{\tr{G^2} + \tr{G}^2} \leq \frac{1}{2} \tr{G}^2 ,
+	\end{gather*}
+	which shows~\cref{eqn:E_bound}, since \( \norm{E} \leq \norm{E}_F \).
+
+	To show~\cref{eqn:F_bound}, we apply the Frobenius norm \( \norm{F}_F \):
+	\begin{gather*}
+		\norm{F}_F = \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} - 2 \tr{a^T b} \right. \\
+		\left.+ 2 \tr{a^T c } + \tr{b^T b}  - 2 \tr{b^T c} + \tr{c^T c}\right] .
+	\end{gather*}
+	where the terms \( a, b, \text{ and } c \) are given by
+	\begin{gather*}
+		a = r^T R r I , \quad	b = R^T v r^T , \quad c = \frac{R^T \hat{v} R r v^T R \hat{r}}{r^T R^T v - \cos \theta}.
+	\end{gather*}
+	A straightforward computation of \( a^T a \) shows that
+	\begin{gather*}
+		\tr{a^T a} = \parenth{v^T R r}^2 \tr{I} \leq 3 \beta^2 ,
+	\end{gather*}
+	where we used the fact that \( v^T R r = r^T R^T v < \beta \) from our given domain.
+	Similarly, one can show that \( \tr{a^T b} \) is equivalent to
+	\begin{gather*}
+		\tr{a^T b} = v^T R r \tr{R^T v r^T} = \parenth{v^T R r}^2 \leq \beta^2 ,
+	\end{gather*} 
+	where we used the fact that \( \tr{x y^T} = x^T y \).
+	The product \( \tr{a^T c} \) is given by
+	\begin{gather*}
+		\tr{a^T c} = \frac{v^T R r}{r^T R^T v - \cos \theta} \tr{\parenth{R^T v}^\vee \parenth{r v^T R} \hat{r} } ,
+	\end{gather*}
+	where we used the hat map property~\cref{eqn:RxR}.
+	One can show that \(\mathrm{tr}[a^T c] \leq 0 \) over the range \( -1 \leq v^T R r \leq \cos \theta \). 
+	Next, \( \tr{b^T b}\) is equivalent to
+	\begin{gather*}
+		\tr{b^T b} = \tr{r v^T R R^T v r^T} = 1 ,
+	\end{gather*}
+	since \( r,v \in \Sph^2\).
+	Finally, \( \tr{c^T c} \) is reduced to
+	\begin{gather*}
+		\tr{c^T c} = \tr{\hat{r} R^T v r^T \bracket{-I + R^T v v^T R} r v^T R \hat{r}} ,
+	\end{gather*}
+	where we used the fact that \( \hat{x}^2 = - \norm{x}^2 I + x x^T\).
+	Expanding and collecting like terms gives
+	\begin{gather*}
+		\tr{c^T c } = \frac{1 - 2\parenth{v^T R r}^2 + \parenth{v^T R r}^4}{\parenth{r^T R^T v - \cos \theta}^2} . 
+	\end{gather*}
+	Using the the given domain \( r^T R^T v \leq \beta \) gives the upper bound~\cref{eqn:F_bound}.
+	The bound on \( e_{R_A} \) is given in~\cref{eqn:psi_lower_bound} while \( e_{R_B} \) arises from the definition of the cross product \( \norm{a \times b} = \norm{a} \norm{b} \sin \theta \).
+	Finally, we can find the upper bound~\cref{eqn:eR_dot} as
+	\begin{gather*}
+		\norm{\dot{e}_R} \leq \parenth{\norm{B} \norm{E} + 2 \norm{e_{R_A}} \norm{e_{R_B}} + \norm{A}\norm{F}} \norm{e_\Omega} \, .
+	\end{gather*}
+	Using~\crefrange{eqn:AB_bound}{eqn:eRB_bound} one can define \( H \) in terms of known values.
+\subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}
+	Consider the Lyapunov function \( \mathcal{V} \) given by
+	\begin{gather}
+		\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , \label{eqn:v_adapt}
+	\end{gather}
+	over the domain \( D \) in~\cref{eqn:domain}.
+	From~\Cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
+	\begin{gather}
+		\mathcal{V} \leq z^T W z , \label{eqn:v_upper_bound}
+	\end{gather}
+	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrix \(W \in \R^{3 \times 3}\) is given by
+	\begin{gather*}
+		W = \begin{bmatrix}
+			k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
+			\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
+			0 & 0 & \frac{1}{2 k_\Delta}
+		\end{bmatrix} .
+	\end{gather*}
+	The time derivative of \( \mathcal{V}\) with the control inputs~\cref{eqn:adaptive_control} is given by
+	\begin{align}
+		\dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
+		&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
+	\end{align}
+	where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
+	The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
+	\begin{align*}
+		 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
+	\end{align*}
+	Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
+	\begin{gather*}
+		\dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
+	\end{gather*}
+	where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
+	\begin{gather}
+		M = \begin{bmatrix}
+			k_R c & \frac{k_\Omega c}{2} \\
+			\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
+		\end{bmatrix} .
+	\end{gather}
+	If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
+	This implies that $\dot{\mathcal{V}}$ is negative semidefinite and $\lim_{t\to\infty} \zeta=0$. 
+	As the Lyapunov function is non-increasing $z$ is uniformly bounded. 
+%	
+%	
+%	This implies that the Lyapunov function \( V \) is non-increasing and bounded from below.
+%	Furthermore, since \( V \) is nonincreasing the disturbance error \( e_\Delta\) is bounded.
+%	Since \( \dot{V} \) is uniformly continuous in time this implies that the zero equilibrium \( e_R, e_\Omega\) is stable in the sense of Lyapunov
+%	The domain \( D \) does that include the undesired equilibria and ensures that as \( e_R \to 0 \) the attitude also converges \( R \to R_d \).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
+                                  % on the last page of the document manually. It shortens
+                                  % the textheight of the last page by a suitable amount.
+                                  % This command does not take effect until the next page
+                                  % so it should come on the page before the last. Make
+                                  % sure that you do not shorten the textheight too much.
 
